% !TEX root = ../abeliangerbs.tex

\subsection{Extensions to Tuples}
The above proofs technically don't even require that the group $ G$ is abelian. If we want to keep track of the fact our group is abelian, we should extract the elements of $A$ which can do so.
\begin{lemma} \label{lem:constructalphabeta}
	Let $A$ be a $ G$-module, and let 
	\[1\to A\to\mc E\stackrel\pi\to G\to1\]
	be a group extension. Further, fix some $F_1,F_2\in\mc E$ and define $\sigma_i\coloneqq\pi(F_i)$ for $i\in\{1,2\}$, and let $\sigma_i\in G$ have order $n_i$. Then, setting
	\[\alpha_i\coloneqq F_i^{n_i}\qquad\text{and}\qquad\beta\coloneqq F_1F_2F_1^{-1}F_2^{-1},\]
	we have the following.
	\begin{listalph}
		\item $\alpha_i\in A^{\langle\sigma_i\rangle}$ for $i\in\{1,2\}$ and $\beta\in A$.
		\item $N_1(\beta)=\alpha_1/\sigma_2(\alpha_1)$ and $N_2(\beta^{-1})=\alpha_2/\sigma_1(\alpha_2)$, where $N_i\coloneqq\sum_{p=0}^{n_i-1}\sigma_i^p$.
	\end{listalph}
\end{lemma}
\begin{proof}
	These checks are a matter of force. For brevity, we set $A_i\coloneqq A^{\langle\sigma_i\rangle}$ for $i\in\{1,2\}$.
	\begin{listalph}
		\item That $\alpha_i\in A_i$ follows from \autoref{lem:constructalpha}. Lastly, $\beta\in A$ follows from noting
		\[\pi(\beta)=\pi(F_1)\pi(F_2)\pi(F_1)^{-1}\pi(F_2)^{-1}=1,\]
		so $\beta\in\ker\pi=A$.
		\item We will check that $\op N_{L/L_1}(\beta)=\alpha_1/\sigma_2(\alpha_1)$; the other equality follows symmetrically after switching $1$s and $2$s because $\beta^{-1}=F_2F_1F_2^{-1}F_1^{-1}$. Well, we compute
		\begin{align*}
			N_1(\beta) &= \sigma_1^{-1}(\beta)\cdot\sigma_1^{-2}(\beta)\cdot\sigma^{-3}\cdot\ldots\cdot\sigma^{-n_1}(\beta) \\
			&= F_1^{-1}\left(F_1F_2F_1^{-1}F_2^{-1}\right)F_1 \\
			&\phantom{{}={}}\cdot F_1^{-2}\left(F_1F_2F_1^{-1}F_2^{-1}\right)F_1^2 \\
			&\phantom{{}={}}\cdot F_1^{-3}\left(F_1F_2F_1^{-1}F_2^{-1}\right)F_1^3\cdot\ldots \\
			&\phantom{{}={}}\cdot F_1^{-n_1}(F_1F_2F_1^{-1}F_2^{-1})F_1^{n_1} \\
			% &= F_2F_1^{-1}F_2^{-1} \\
			% &\phantom{{}={}}\cdot F_2F_1^{-1}F_2^{-1} \\
			% &\phantom{{}={}}\cdot F_2F_1^{-1}F_2^{-1}\cdot\ldots \\
			% &\phantom{{}={}}\cdot F_2F_1^{-1}F_2^{-1}F_1^{n_1} \\
			&= F_2F_1^{-1} \\
			&\phantom{{}={}}\cdot F_1^{-1} \\
			&\phantom{{}={}}\cdot F_1^{-1}\cdot\ldots \\
			&\phantom{{}={}}\cdot F_1^{-1}F_2^{-1}F_1^{n_1} \\
			&= F_2F_1^{-n_1}F_2^{-1}F_1^{n_1} \\
			&= \alpha_1/\sigma_2(\alpha_1).
		\end{align*}
	\end{listalph}
	The above computations finish the proof.
\end{proof}
The proof of (b) above might appear magical, but in fact it comes from a more general idea.
\begin{lemma} \label{lem:switchtwo}
	Fix everything as in \autoref{lem:constructalphabeta}. Then, for $x,y\ge0$, we have
	\[F_1^xF_2^y=\prod_{k=0}^{x-1}\prod_{\ell=0}^{y-1}\sigma_1^k\sigma_2^\ell(\beta)F_2^yF_1^x.\]
\end{lemma}
\begin{proof}
	We induct. We take a moment to write out the case of $x=1$, for which we induct on $y$. To be explicit, we will prove
	\[F_1F_2^y=\prod_{\ell=0}^{y-1}\sigma_2^\ell(\beta)F_2^yF_1.\]
	For $y=0$, there is nothing to say. So suppose the statement for $y$ (and $x=1$), and we show $y+1$ (and $x=1$). Well, we compute
	\begin{align*}
		F_1F_2^{y+1} &= F_1F_2^y\cdot F_2 \\
		&= \prod_{\ell=0}^{y-1}\sigma_2^\ell(\beta)F_2^yF_1\cdot F_2 \\
		&= \prod_{\ell=0}^{y-1}\sigma_2^\ell(\beta)F_2^y\beta F_2F_1 \\
		&= \prod_{\ell=0}^{y-1}\sigma_2^\ell(\beta)\cdot \sigma_2^y(\beta)F_2^y\cdot F_2F_1 \\
		&= \prod_{\ell=0}^{(y+1)-1}\sigma_2^\ell(\beta)\cdot F_2^{y+1}F_1,
	\end{align*}
	which is what we wanted.
	
	We now move on to the general case. We will induct on $y$. Note that $y=0$ makes the product empty, leaving us with $F_1^x=F_1^x$, for any $x$. So suppose that the statement is true for some $y\ge0$, and we will show $y+1$. For this, we now turn to inducting on $x$. For $x=0$, we note that the product is once again empty, so we are left with showing $F_2^{y+1}=F_2^{y+1}$, which is true.
	
	To finish, we suppose the statement for $x$ and show the statement for $x+1$. Well, we compute
	\begin{align*}
		F_1^{x+1}F_2^{y+1} &= F_1\cdot F_1^xF_2^{y+1} \\
		&= F_1\cdot \prod_{k=0}^{x-1}\prod_{\ell=0}^{(y+1)-1}\sigma_1^k\sigma_2^\ell(\beta)\cdot F_2^{y+1}F_1^x \\
		&= \sigma_1\left(\prod_{k=0}^{x-1}\prod_{\ell=0}^{(y+1)-1}\sigma_1^k\sigma_2^\ell(\beta)\right)\cdot F_1F_2^{y+1}F_1^x \\
		&= \prod_{k=1}^{(x+1)-1}\prod_{\ell=0}^{(y+1)-1}\sigma_1^k\sigma_2^\ell(\beta)\cdot F_1F_2^{y+1}F_1^x \\
		&= \prod_{k=1}^{(x+1)-1}\prod_{\ell=0}^{(y+1)-1}\sigma_1^k\sigma_2^\ell(\beta)\cdot \prod_{\ell=0}^{(y+1)-1}\sigma_2^\ell(\beta)\cdot \sigma_2^y(\beta)\cdot F_2^{y+1}F_1\cdot F_1^x \\
		&= \prod_{k=0}^{(x+1)-1}\prod_{\ell=0}^{(y+1)-1}\sigma_1^k\sigma_2^\ell(\beta)F_2^{y+1}F_1^{x+1},
	\end{align*}
	which is what we wanted.
\end{proof}
\begin{remark} \label{rem:alphabetarelation}
	Setting $x=n_1$ and $y=1$ recovers $\op N_{L/L^{\langle\sigma_1\rangle}}(\beta)=\alpha_1/\sigma_2(\alpha_1)$.
\end{remark}
In particular, \autoref{rem:alphabetarelation} tells us that coherence of the group law in $\mc E$ should give rise to relations between our elements of $A$. Here is a more complex example.
\begin{lemma} \label{lem:betarelations}
	Let $A$ be a $ G$-module, and let 
	\[1\to A\to\mc E\stackrel\pi\to G\to1\]
	be a group extension. Further, fix some $F_1,F_2,F_3\in\mc E$ and define $\sigma_i\coloneqq\pi(F_i)$ for $i\in\{1,2,3\}$, and let $\sigma_i\in G$ have order $n_i$. Then, setting
	\[\beta_{ij}\coloneqq F_iF_jF_i^{-1}F_j^{-1}\]
	for each pair of indices $(i,j)$ with $i>j$. Then
	\[\frac{\sigma_2(\beta_{31})}{\beta_{31}}=\frac{\sigma_1(\beta_{32})}{\beta_{32}}\cdot\frac{\sigma_3(\beta_{21})}{\beta_{21}}.\]
\end{lemma}
\begin{proof}
	The point is to turn $F_3F_2F_1$ into $F_1F_2F_3$ in two different ways. On one hand,
	\begin{align*}
		(F_3F_2)F_1 &= \beta_{32}F_2F_3F_1 \\
		&= \beta_{32}F_2\beta_{31}F_1F_3 \\
		&= \beta_{32}\sigma_2(\beta_{31})(F_2F_1)F_3 \\
		&= \beta_{32}\sigma_2(\beta_{31})\beta_{21}F_1F_2F_3.
	\end{align*}
	On the other hand,
	\begin{align*}
		F_3(F_2F_1) &= F_3\beta_{21}F_1F_2 \\
		&= \sigma_3(\beta_{21})(F_3F_1)F_2 \\
		&= \sigma_3(\beta_{21})\beta_{31}F_1(F_3F_2) \\
		&= \sigma_3(\beta_{21})\beta_{31}F_1\beta_{32}F_2F_3 \\
		&= \sigma_3(\beta_{21})\beta_{31}\sigma_1(\beta_{32})F_1F_2F_3.
	\end{align*}
	Thus,
	\[\beta_{32}\sigma_2(\beta_{31})\beta_{21}=\sigma_3(\beta_{21})\beta_{31}\sigma_1(\beta_{32}),\]
	which rearranges into the desired equation.
\end{proof}
\begin{remark}
	The relation from \autoref{lem:betarelations} may look asymmetric in the $\beta_{ij}$, but this is because the definitions of the $\beta_{ij}$s themselves are asymmetric in $F_i$.
\end{remark}

\subsection{Tuples to Cocycles}
\subsubsection{The Set-Up}
The proceeding lemma is intended to give intuition that the element $\beta$ is helping to specify the group law on $\mc E$.

More concretely, we will take the following set-up for the following results: fix a $ G$-module $A$, and let
\[1\to A\to\mc E\to G\to1\]
be a group extension. Once we choose elements $\{\sigma_i\}_{i=1}^m$ generating $ G$, we know by \autoref{prop:liftsgenerate} that we can generate $\mc E$ by $A$ and some arbitrarily chosen lifts $\{F_i\}_{i=1}^m$ of the $\{\sigma_i\}_{i=1}^m$. Then, letting $n_i$ be the order of $\sigma_i$, we set
\[\alpha_i\coloneqq F_i^{n_i}\]
for each index $i$ and
\[\beta_{ij}\coloneqq F_iF_jF_i^{-1}F_j^{-1}\]
for each index $1\le j<i\le m$. Notably, we will not need more $\beta$s: indeed, $\beta_{ii}=1$ and $\beta_{ij}=\beta_{ji}^{-1}$ for any $i$ and $j$. Setting $A_i\coloneqq A^{\langle\sigma_i\rangle}$ and $N_i\coloneqq\sum_{p=0}^{n_i-1}\sigma_i^p$, the story so far is that
\begin{equation}
	\alpha_i\in A_i\text{ for each }i\qquad\text{and}\qquad\beta_{ij}\in A\text{ for each }i>j \label{eq:tuplefields}
\end{equation}
and
\begin{equation}
	N_i(\beta_{ij})=\alpha_i/\sigma_j(\alpha_i)\qquad\text{and}\qquad N_j(\beta_{ij}^{-1})=\alpha_j/\sigma_i(\alpha_j)\qquad\text{ for each }i>j \label{eq:tuplerelations}
\end{equation}
by \autoref{lem:constructalphabeta}, and
\begin{equation}
	\frac{\sigma_j(\beta_{ik})}{\beta_{ik}}=\frac{\sigma_k(\beta_{ij})}{\beta_{ij}}\cdot\frac{\sigma_i(\beta_{jk})}{\beta_{jk}}\qquad\text{ for each }i>j>k \label{eq:betarelations}
\end{equation}
by \autoref{lem:betarelations}. This data is so important that we will give it a name.
\begin{definition}
	In the above set-up, the data of $(\{\alpha_i\},\{\beta_{ij}\})$ satisfying \autoref{eq:tuplefields} and \autoref{eq:tuplerelations} and \autoref{eq:betarelations} will be called a \textit{$\{\sigma_i\}_{i=1}^m$-tuple}. When understood, the $\{\sigma_i\}_{i=1}^m$ will be abbreviated. Once $G$ and $A$ are fixed, we will denote the set of $\{\sigma_i\}_{i=1}^m$-tuples by $\mathcal T(G,A)$.
\end{definition}
Note that this definition is independent of $\mc E$, but a choice of extension $\mc E$ and lifts $F_i$ give a $\{\sigma_i\}_{i=1}^m$-tuple as described above.
\begin{remark}
	The $\mathcal T(G,A)$ form a group under multiplication in $A$. Indeed, the conditions \autoref{eq:tuplefields} and \autoref{eq:tuplerelations} and \autoref{eq:betarelations} are closed under multiplication and inversion.
\end{remark}
We also know from \autoref{lem:switchtwo} that
\[F_i^xF_j^y=\prod_{k=0}^{x-1}\prod_{\ell=0}^{y-1}\sigma_i^k\sigma_j^\ell(\beta_{ij})F_j^yF_i^x\]
for $i>j$ and $x,y\ge0$. It will be helpful to have some notation for the residue term in $A$, so we define
\[\beta_{ij}^{(xy)}\coloneqq\prod_{k=0}^{x-1}\prod_{\ell=0}^{y-1}\sigma_i^k\sigma_j^\ell(\beta_{ij}).\]
Now, combined with the fact that $F_ix=\sigma_i(x)F_i$ for each $F_i$ and $x\in A$, we have been approximately told how the group operation works in $\mc E$. Namely, we could conceivably write any element of $\mc E$ in the form
\[xF_1^{a_1}\cdots F_m^{a_m}\]
for $x\in A$ and $a_i\in\ZZ/n_i\ZZ$ because we know how to make these elements commute and generate $\mc E$. Further, we can multiply out two terms of the form
\[xF_1^{a_1}\cdots F_m^{a_m}\cdot yF_1^{b_1}\cdots F_m^{b_m}\]
into a term of the form $zF_1^{c_1}\cdots F_m^{c_m}$. In fact, it will be helpful for us to see how to do this.
\begin{proposition} \label{prop:multiplytwoelements}
	Fix everything as in the set-up, except drop the assumption that $\{\sigma_i\}_{i=1}^m$ generate $ G$. Then, choosing $a_i,b_i\in\NN$ for each $i$, we have
	\[\left(\prod_{i=1}^mF_i^{a_i}\right)\left(\prod_{i=1}^mF_i^{b_i}\right)=\left[\prod_{1\le j<i\le m}\Bigg(\prod_{1\le k<j}\sigma_k^{a_k+b_k}\Bigg)\Bigg(\prod_{j\le k<i}\sigma_k^{a_k}\Bigg)\beta_{ij}^{(a_ib_j)}\right]\left(\prod_{i=1}^mF_i^{a_i+b_i}\right).\]
\end{proposition}
\begin{proof}
	The reason that we dropped the assumption on $\{\sigma_i\}_{i=1}^m$ is so that we may induct directly on $m$. We start by showing that
	\[\left(\prod_{i=1}^mF_i^{a_i}\right)F_1^{b_1}=\left[\prod_{1<i\le m}\left(\prod_{1\le k<i}\sigma_k^{a_k}\right)\beta_{i1}^{(a_ib_1)}\right]F_1^{a_1+b_1}\prod_{i=2}^mF_i^{a_i}.\]
	We do this by induction on $m$. When $m=0$ and even for $m=1$, there is nothing to say. For the inductive step, we assume
	\[\left(\prod_{i=1}^mF_i^{a_i}\right)F_1^{b_1}=\left[\prod_{1<i\le m}\left(\prod_{1\le k<i}\sigma_k^{a_k}\right)\beta_{i1}^{(a_ib_1)}\right]F_1^{a_1+b_1}\prod_{i=2}^mF_i^{a_i}\]
	and compute
	\begin{align*}
		\left(\prod_{i=1}^{m+1}F_i^{a_i}\right)F_1^{b_1} &= \left(\prod_{i=1}^{m}F_i^{a_i}\right)F_{m+1}^{a_{m+1}}F_1^{b_1} \\
		&= \left(\prod_{i=1}^{m}F_i^{a_i}\right)\beta_{m+1,1}^{(a_{m+1}b_1)}F_1^{b_1}F_{m+1}^{a_{m+1}} \\
		&= \left[\left(\prod_{k=1}^m\sigma_k^{a_k}\right)\beta_{m+1,1}^{(a_{m+1}b_1)}\right]\left[\prod_{1<i\le m}\left(\prod_{1\le k<i}\sigma_k^{a_k}\right)\beta_{i1}^{(a_ib_1)}\right]F_1^{a_1+b_1}\left(\prod_{i=2}^mF_i^{a_i}\right)F_{m+1}^{a_{m+1}} \\
		&= \left[\prod_{1<i\le m+1}\left(\prod_{1\le k<i}\sigma_k^{a_k}\right)\beta_{i1}^{(a_ib_1)}\right]F_1^{a_1+b_1}\left(\prod_{i=2}^{m+1}F_i^{a_i}\right),
	\end{align*}
	which completes our inductive step.

	We now attack the statement of the proposition directly, again inducting on $m$. For $m=0$ and even for $m=1$, there is again nothing to say. For the inductive step, take $m>1$, and we get to assume that
	\[\left(\prod_{i=2}^mF_i^{a_i}\right)\left(\prod_{i=2}^mF_i^{b_i}\right)=\left[\prod_{2\le j<i\le m}\Bigg(\prod_{2\le k<j}\sigma_k^{a_k+b_k}\Bigg)\Bigg(\prod_{j\le k<i}\sigma_k^{a_k}\Bigg)\beta_{ij}^{(a_ib_j)}\right]\left(\prod_{i=2}^mF_i^{a_i+b_i}\right).\]
	From here, we can compute
	\begin{align*}
		\left(\prod_{i=1}^mF_i^{a_i}\right)\left(\prod_{i=1}^mF_i^{b_i}\right) &= \left(\prod_{i=1}^mF_i^{a_i}\right)F_1^{b_1}\left(\prod_{i=2}^mF_i^{b_i}\right) \\
		&= \left[\prod_{1<i\le m}\Bigg(\prod_{1\le k<i}\sigma_k^{a_k}\Bigg)\beta_{i1}^{(a_ib_1)}\right]F_1^{a_1+b_1}\left(\prod_{i=2}^mF_i^{a_i}\right)\left(\prod_{i=2}^mF_i^{b_i}\right) \\
		&= \left[\prod_{1<i\le m}\Bigg(\prod_{1\le k<i}\sigma_k^{a_k}\Bigg)\beta_{i1}^{(a_ib_1)}\right]F_1^{a_1+b_1}\cdot \\
		&\qquad\qquad\left[\prod_{2\le j<i\le m}\Bigg(\prod_{2\le k<j}\sigma_k^{a_k+b_k}\Bigg)\Bigg(\prod_{j\le k<i}\sigma_k^{a_k}\Bigg)\beta_{ij}^{(a_ib_j)}\right]\left(\prod_{i=2}^mF_i^{a_i+b_i}\right) \\
		&= \left[\prod_{1<i\le m}\Bigg(\prod_{1\le k<i}\sigma_k^{a_k}\Bigg)\beta_{i1}^{(a_ib_1)}\right]\cdot \\
		&\qquad\qquad \sigma_1^{a_1+b_1}\left[\prod_{2\le j<i\le m}\Bigg(\prod_{2\le k<j}\sigma_k^{a_k+b_k}\Bigg)\Bigg(\prod_{j\le k<i}\sigma_k^{a_k}\Bigg)\beta_{ij}^{(a_ib_j)}\right]\left(\prod_{i=2}^mF_i^{a_i+b_i}\right).
	\end{align*}
	From here, a little rearrangement finishes the inductive step.
\end{proof}
The reason we exerted this pain upon ourselves is for the following result.
\begin{prop} \label{prop:writedowncocycle}
	Fix everything as in the set-up. Then, if well-defined, we can represent the cohomology class corresponding to $\mc E$ by the cocycle
	\[c(g,h)\coloneqq\left[\prod_{1\le j<i\le m}\Bigg(\prod_{1\le k<j}\sigma_k^{a_k+b_k}\Bigg)\Bigg(\prod_{j\le k<i}\sigma_k^{a_k}\Bigg)\beta_{ij}^{(a_ib_j)}\right]\left[\prod_{i=1}^m\Bigg(\prod_{1\le k<i}\sigma_k^{a_k+b_k}\Bigg)\alpha_i^{\floor{\frac{a_i+b_i}{n_i}}}\right],\]
	where $g=\prod_i\sigma_i^{a_i}$ and $h=\prod_i\sigma_i^{b_i}$.
\end{prop}
Observe that \autoref{prop:writedowncocycle} has a fairly strong hypothesis that $c$ is well-defined; we will return to this later.
\begin{proof}
	Very quickly, we use the division algorithm to define
	\[a_i+b_i=n_iq_i+r_i\]
	where $q_\in\{0,1\}$ and $0\le r_i<n_i$. In particular,
	\[gh=\prod_{i=1}^mF_i^{r_i}.\]
	Now, because the elements $\sigma_i$ generate $ G$, we see that the lifts $\sigma_i\mapsto F_i$ defines a section $s\colon G\to\mc E$. As such, we can compute a representing cocycle for our cohomology class as
	\begin{align*}
		c(g,h) &= s(g)s(h)s(gh)^{-1} \\
		&= \Bigg(\prod_{i=1}^mF_i^{a_i}\Bigg)\Bigg(\prod_{i=1}^mF_i^{b_i}\Bigg)\Bigg(\prod_{i=1}^mF_i^{r_i}\Bigg)^{-1} \\
		&= \left[\prod_{1\le j<i\le m}\Bigg(\prod_{1\le k<j}\sigma_k^{a_k+b_k}\Bigg)\Bigg(\prod_{j\le k<i}\sigma_k^{a_k}\Bigg)\beta_{ij}^{(a_ib_j)}\right]\left(\prod_{i=1}^mF_i^{a_i+b_i}\right)\Bigg(\prod_{i=1}^mF_{m-i+1}^{-r_{m-i+1}}\Bigg).
	\end{align*}
	It remains to deal with the last products; we claim that it is equal to
	\[\left(\prod_{i=1}^mF_i^{a_i+b_i}\right)\Bigg(\prod_{i=1}^mF_{m-i+1}^{-r_{m-i+1}}\Bigg)=\prod_{i=1}^m\Bigg(\prod_{1\le k<i}\sigma_k^{a_k+b_k}\Bigg)\alpha_i^{q_i},\]
	which will finish the proof. We induct on $m$; for $m=0$ and $m=1$, there is nothing to say. For the inductive step, we assume that
	\[\left(\prod_{i=2}^mF_i^{a_i+b_i}\right)\Bigg(\prod_{i=1}^{m-1}F_{m-i+1}^{-r_{m-i+1}}\Bigg)=\prod_{i=2}^m\Bigg(\prod_{2\le k<i}\sigma_k^{a_k+b_k}\Bigg)\alpha_i^{q_i}\]
	and compute
	\begin{align*}
		\left(\prod_{i=1}^mF_i^{a_i+b_i}\right)\Bigg(\prod_{i=1}^mF_{m-i+1}^{-r_{m-i+1}}\Bigg) &= F_1^{a_1+b_1}\left(\prod_{i=2}^mF_i^{a_i+b_i}\right)\Bigg(\prod_{i=1}^{m-1}F_{m-i+1}^{-r_{m-i+1}}\Bigg)F_1^{-a_1-b_1}F_1^{a_1+b_1-r_1} \\
		&= F_1^{a_1+b_1}\left(\prod_{i=2}^m\Bigg(\prod_{2\le k<i}\sigma_k^{a_k+b_k}\Bigg)\alpha_i^{q_i}\right)F_1^{-a_1-b_1}\alpha_1^{q_1} \\
		&= \left(\prod_{i=2}^m\Bigg(\prod_{1\le k<i}\sigma_k^{a_k+b_k}\Bigg)\alpha_i^{q_i}\right)\alpha_1^{q_1} \\
		&= \prod_{i=1}^m\Bigg(\prod_{1\le k<i}\sigma_k^{a_k+b_k}\Bigg)\alpha_i^{q_i},
	\end{align*}
	finishing.
\end{proof}

\subsubsection{The Modified Set-Up}
A priori we have no reason to expect that the $c$ constructed in \autoref{prop:writedowncocycle} is actually a cocycle, especially if the $\sigma_i$ have nontrivial relations.

To account for this, we modify our set-up slightly. By the classification of finitely generated abelian groups, we may write
\[ G\simeq\bigoplus_{k=1}^m G_k,\]
where $ G_k\subseteq G$ with $ G_k\cong\ZZ/n_k\ZZ$ and $n_k>1$ for each $n_k$. As such, we let $\sigma_k$ be a generating element of $ G_k$ so that we still know that the $\sigma_k$ generate $ G$. In this case, we have the following result.
\begin{theorem} \label{thm:getcocycle}
	Fix everything as in the modified set-up, forgetting about the extension $\mc E$. Then a $\{\sigma_i\}_{i=1}^m$-tuple of $\{\alpha_i\}_{i=1}^m$ and $\{\beta_{ij}\}_{i>j}$ makes
	\[c(g,h)\coloneqq\left[\prod_{1\le j<i\le m}\Bigg(\prod_{1\le k<j}\sigma_k^{a_k+b_k}\Bigg)\Bigg(\prod_{j\le k<i}\sigma_k^{a_k}\Bigg)\beta_{ij}^{(a_ib_j)}\right]\left[\prod_{i=1}^m\Bigg(\prod_{1\le k<i}\sigma_k^{a_k+b_k}\Bigg)\alpha_i^{\floor{\frac{a_i+b_i}{n_i}}}\right],\]
	where $g\coloneqq\prod_i\sigma_i^{a_i}$ with $h\coloneqq\prod_i\sigma_j^{a_j}$ and $0\le a_i,b_i<n_i$, into a cocycle in $Z^2( G,A)$.
\end{theorem}
\begin{proof}
	Note that $c$ is now surely well-defined because the elements $g$ and $h$ have unique representations as described. Anyway, we relegate the direct cocycle check to \autoref{sec:verifycocycle} because it is long, annoying, and unenlightening. We will also present an alternative proof in \autoref{sec:tuplestudy}, using more abstract theory.
\end{proof}
Observe that the above construction has now completely forgotten about $\mc E$! Namely, we have managed to go from tuples straight to cocycles; this is theoretically good because it will allow us to go fully in reverse: we will be able to start with a tuple, build the corresponding cocycle, from which the extension arises. However, equivalence classes of cocycles give the ``same'' extension, so we will also need to give equivalence classes for tuples as well.

\subsection{Building Tuples}
We continue in the modified set-up of the previous section. There is already an established way to get from a cocycle to an extension, which means that it should be possible to go straight from the cocycle to a $\{\sigma_i\}_{i=1}^m$-tuple. Again, it will be beneficial to write this out.
\begin{lemma} \label{lem:explicitalphabeta}
	Fix everything as in the modified set-up, but suppose that $\mc E=\mc E_c$ is the extension generated from a cocycle $c\in Z^2( G,A)$. Then, if $F_i=(x_i,\sigma_i)$ are our lifts, we have
	\[\alpha_i=N_i(x_i)\cdot\prod_{k=0}^{n_i-1}c\left(\sigma_i^k,\sigma_i\right)\qquad\text{and}\qquad\beta_{ij}=\frac{x_i}{\sigma_j(x_i)}\cdot\frac{\sigma_i(x_j)}{x_j}\cdot\frac{c(\sigma_i,\sigma_j)}{c(\sigma_j,\sigma_i)}\]
	for each $\alpha_i$ and $\beta_{ij}$.
\end{lemma}
\begin{proof}
	The equality for the $\alpha_i$ follow from \autoref{lem:explicitalpha}. For the equality about $\beta_{ij}$, we simply compute
	by brute force, writing
    \begin{align*}
        F_iF_j &= (x_i\cdot\sigma_ix_j\cdot c(\sigma_i,\sigma_j),\sigma_i\sigma_j) \\
        F_jF_i &= (x_j\cdot\sigma_jx_i\cdot c(\sigma_j,\sigma_i),\sigma_j\sigma_i) \\
        (F_jF_i)^{-1} &= \left((\sigma_j\sigma_i)^{-1}(x_j\cdot\sigma_jx_i\cdot c(\sigma_j,\sigma_i))^{-1},\sigma_i^{-1}\sigma_j^{-1}\right),
    \end{align*}
    which gives
    \begin{align*}
        \beta_{ij} &= (F_iF_j)(F_jF_i)^{-1} \\
        &= \left(\frac{x_i}{\sigma_jx_i}\cdot\frac{\sigma_ix_j}{x_j}\cdot\frac{c(\sigma_i,\sigma_j)}{c(\sigma_j,\sigma_i)},1\right),
    \end{align*}
	finishing.
\end{proof}
Here is a nice sanity check that we are doing things in the right setting: not only can we build tuples from extensions, but we can find an extension corresponding to any tuple.
\begin{cor} \label{cor:alltuplesfromextens}
	Fix everything as in the modified set-up, forgetting about the extension $\mc E$. For any $\{\sigma_i\}_{i=1}^m$-tuple of $\{\alpha_i\}_{i=1}^m$ and $\{\beta_{ij}\}_{i>j}$, there exists an extension $\mc E$ and lifts $F_i$ of the $\sigma_i$ so that
	\[\alpha_i=F_i^{n_i}\qquad\text{and}\qquad\beta_{ij}=F_iF_jF_i^{-1}F_j^{-1}.\]
\end{cor}
\begin{proof}
	From \autoref{thm:getcocycle}, we may build the cocycle $c\in Z^2( G,A)$ defined by
	\begin{equation}
		c(g,h)\coloneqq\left[\prod_{1\le j<i\le m}\Bigg(\prod_{1\le k<j}\sigma_k^{a_k+b_k}\Bigg)\Bigg(\prod_{j\le k<i}\sigma_k^{a_k}\Bigg)\beta_{ij}^{(a_ib_j)}\right]\left[\prod_{i=1}^m\Bigg(\prod_{1\le k<i}\sigma_k^{a_k+b_k}\Bigg)\alpha_i^{\floor{\frac{a_i+b_i}{n_i}}}\right], \label{eq:uglycocycle}
	\end{equation}
	where $g\coloneqq\prod_iF_i^{a_i}$ and $h\coloneqq\prod_iF_j^{a_j}$ and $0\le a_i,b_i<n_i$. As such, we use $\mc E\coloneqq\mc E_c$ to be the corresponding extension and $F_i\coloneqq(1,\sigma_i)$ as our lifts. We have the following checks.
	\begin{itemize}
		\item To show $\alpha_i=F_i^{n_i}$, we use \autoref{lem:explicitalphabeta} to compute $F_i^{n_i}$, which means we want to compute
		\[\prod_{k=0}^{n_i-1}c\left(\sigma_i^k,\sigma_i\right).\]
		Well, plugging $c\left(\sigma_i^k,\sigma_i\right)$ into \autoref{eq:uglycocycle}, we note that all $\beta_{k\ell}^{(a_kb_\ell)}$ terms vanish (either $a_k=0$ or $b_\ell=0$ for each $k\ne\ell$), so the big left product completely vanishes.
		
		As for the right product, the only term we have to worry about is
		\[\Bigg(\prod_{1\le k<i}\sigma_k^{0+0}\Bigg)\alpha_i^{\floor{\frac{k+1}{n_i}}},\]
		which is equal to $1$ when $k\le n_i-1$ and $\alpha_i$ when $k=n_i-1$. As such, we do indeed have $\alpha_i=F_i^{n_i}$.
		\item To show $\beta_{ij}=F_iF_jF_i^{-1}F_j^{-1}$ for $i>j$, we again use \autoref{lem:explicitalphabeta} to compute $F_iF_jF_i^{-1}F_j^{-1}$, which means we want to compute
		\[\frac{c(\sigma_i,\sigma_j)}{c(\sigma_j,\sigma_i)}.\]
		Plugging into \autoref{eq:uglycocycle} once more, there is no way to make $\floor{(a_k+b_k)/n_k}$ nonzero (recall we set $n_k>1$ for each $k$) in either $c(\sigma_i,\sigma_j)$ or $c(\sigma_j,\sigma_i)$. As such, the right-hand product term disappears.

		As for the left product, we note that it still vanishes for $c(\sigma_j,\sigma_i)$ because $i>j$ implies that either $a_k=0$ or $b_\ell=0$ for each $k>\ell$. However, for $c(\sigma_i,\sigma_j)$, we do have $a_i=1$ and $b_j=1$ only, so we have to deal with exactly the term
		\[\Bigg(\prod_{1\le k<j}\sigma_k^{a_k+b_k}\Bigg)\Bigg(\prod_{j\le k<i}\sigma_k^{a_k}\Bigg)\beta_{ij}.\]
		With $i>j$ and $a_k=b_k=0$ for $k\notin\{i,j\}$, we see that the product of all the $\sigma_k$s will disappear, indeed only leaving us with $\beta_{ij}$.
	\end{itemize}
	The above computations complete the proof.
\end{proof}
And here is our first taste of (partial) classification.
\begin{cor} \label{cor:cocycletuplesection}
	Fix everything as in the modified set-up, forgetting about the extension $\mc E$. Then the formula of \autoref{thm:getcocycle} and the formulae of \autoref{lem:explicitalphabeta} (setting $x_i=1$ for each $i$) are homomorphisms of abelian groups between tuples in $\mathcal T(G,A)$ and cocycles in $Z^2( G,A)$. In fact, the formula of \autoref{thm:getcocycle} is a section of the formulae of \autoref{lem:explicitalphabeta}.
\end{cor}
\begin{proof}
	The formulae in \autoref{thm:getcocycle} and \autoref{lem:explicitalphabeta} are both large products in their inputs, so they are multiplicative (i.e., homomorphisms). It remains to check that we have a section. Well, starting with a $\{\sigma_i\}_{i=1}^m$-tuple and building the corresponding cocycle $c$ by \autoref{thm:getcocycle}, the proof of \autoref{cor:alltuplesfromextens} shows that the formulae of \autoref{lem:explicitalphabeta} recovers the correct $\{\sigma_i\}_{i=1}^m$-tuple.
\end{proof}

\subsection{Equivalence Classes of Tuples}
We continue in the modified set-up. We would like to make \autoref{cor:cocycletuplesection} into a proper isomorphism of abelian groups, but this is not feasible; for example, the cocycle $c$ generated by \autoref{thm:getcocycle} will always have $c(\sigma_j,\sigma_i)=1$ for $i>j$, which is not true of all cocycles in $Z^2( G,A)$.

However, we did have a notion that the data of a $\{\sigma_i\}_{i=1}^m$ should be enough to specify the group law of the extension that the tuple comes from, so we do expect to be able to define all extensions---and hence achieve all cohomology classes---from a specially chosen $\{\sigma_i\}_{i=1}^m$-tuple.

To make this precise, we want to define an equivalence relation on tuples which go to the same cohomology class and then show that the map \autoref{thm:getcocycle} is surjective on these equivalence classes. The correct equivalence relation is taken from \autoref{lem:explicitalphabeta}.
\begin{definition}
	Fix everything as in the modified set-up. We say that two $\{\sigma_i\}_{i=1}^m$-tuples $(\{\alpha_i\},\{\beta_{ij}\})$ and $(\{\alpha_i'\},\{\beta_{ij}'\})$ are \textit{equivalent} if and only if there exist elements $x_1,\ldots,x_m\in A$ such that
	\[\alpha_i=N_i(x_i)\cdot\alpha_i'\qquad\text{and}\qquad\beta_{ij}=\frac{x_i}{\sigma_j(x_i)}\cdot\frac{\sigma_i(x_j)}{x_j}\cdot\beta_{ij}'\]
	for each $\alpha_i$ and $\beta_{ij}$. We may notate this by $(\{\alpha_i\},\{\beta_{ij}\})\sim(\{\alpha_i'\},\{\beta_{ij}'\})$.
\end{definition}
\begin{remark}
	It is not too hard to see directly from the definition that this is in fact an equivalence relation. In fact, the set of tuples equivalent to the ``trivial'' tuple of all $1$s is closed under multiplication (and inversion) and hence forms a subgroup of $\mathcal T(G,A)$. As such, the set of equivalence classes forms a quotient group of $\mathcal T(G,A)$. We will denote this quotient group by $\overline{\mathcal T}(G,A)$.
\end{remark}
This notion of equivalence can be seen to be the correct one in the sense that it correctly generalizes \autoref{prop:findallalpha}.
\begin{proposition} \label{prop:extenmakesaclass}
	Fix everything as in the modified set-up with an extension $\mc E$. As the lifts $F_i$ change, the corresponding values of
	\[\alpha_i\coloneqq F_i^{n_i}\qquad\text{and}\qquad\beta_{ij}\coloneqq F_iF_jF_i^{-1}F_j^{-1}\]
	go through a full equivalence class of $\{\sigma_i\}_{i=1}^m$-tuples.
\end{proposition}
\begin{proof}
	We proceed as in \autoref{prop:findallalpha}. Given an extension $\mc E'$, let $S_{\mc E'}$ be the set of $\{\sigma_i\}_{i=1}^m$-tuples generated as the lifts $F_i$ change. We start by showing that an isomorphism $\varphi\colon\mc E\simeq\mc E'$ of extensions implies that $S_{\mc E}=S_{\mc E'}$; by symmetry, it will be enough for $S_{\mc E}\subseteq S_{\mc E'}$. The isomorphism induces the following diagram.
	% https://q.uiver.app/?q=WzAsMTAsWzAsMCwiMSJdLFsxLDAsIkxeXFx0aW1lcyJdLFsyLDAsIlxcbWMgRSJdLFszLDAsIlxcR2FtbWEiXSxbNCwwLCIxIl0sWzAsMSwiMSJdLFsxLDEsIkxeXFx0aW1lcyJdLFsyLDEsIlxcbWMgRSciXSxbMywxLCJcXEdhbW1hIl0sWzQsMSwiMSJdLFswLDFdLFsxLDJdLFsyLDMsIlxccGkiXSxbMyw0XSxbNSw2XSxbNiw3XSxbNyw4LCJcXHBpJyJdLFs4LDldLFsyLDcsIlxcdmFycGhpIl0sWzEsNiwiIiwxLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMyw4LCIiLDEseyJsZXZlbCI6Miwic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		1 & {A} & {\mc E} &  G & 1 \\
		1 & {A} & {\mc E'} &  G & 1
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-2, to=1-3]
		\arrow["\pi", from=1-3, to=1-4]
		\arrow[from=1-4, to=1-5]
		\arrow[from=2-1, to=2-2]
		\arrow[from=2-2, to=2-3]
		\arrow["{\pi'}", from=2-3, to=2-4]
		\arrow[from=2-4, to=2-5]
		\arrow["\varphi", from=1-3, to=2-3]
		\arrow[Rightarrow, no head, from=1-2, to=2-2]
		\arrow[Rightarrow, no head, from=1-4, to=2-4]
	\end{tikzcd}\]
	To show that $S_{\mc E}\subseteq S_{\mc E'}$, pick up some $\{\sigma_i\}_{i=1}^m$-tuple $(\{\alpha_i\},\{\beta_{ij}\})$ generated from lifts $F_i\in\mc E$ (i.e., $\pi(F_i)=\sigma_i$), where
	\[\alpha_i\coloneqq F_i^{n_i}\qquad\text{and}\qquad\beta_{ij}\coloneqq F_iF_jF_i^{-1}F_j^{-1}.\]
	Now, we note that $F_i'\coloneqq\varphi(F_i)$ will have
	\[\pi(F_i')=\pi(\varphi(F_i))=\varphi(\pi(F_i))=\sigma_i\]
	by the commutativity of the diagram, so the $F_i'$ are lifts of the $\sigma_i$. Further, we see that
	\[(F_i')^{n_i}=\varphi(F_i)^{n_i}=\varphi\left(F_i^{n_i}\right)=\varphi(\alpha_i)=\alpha_i\]
	for each $i$, and
	\[F_i'F_j'(F_i')^{-1}(F_j')^{-1}=\varphi\left(F_iF_jF_i^{-1}F_j^{-1}\right)=\varphi(\beta_{ij})=\beta_{ij}\]
	for each $i>j$. Thus, $(\{\alpha_i\},\{\beta_{ij}\})$ is a $\{\sigma_i\}_{i=1}^m$-tuple generated by lifts from $\mc E'$, implying that $(\{\alpha_i\},\{\beta_{ij}\})\in S_{\mc E'}$.

	It now suffices to show the statement in the proposition for a specific extension isomorphic to $\mc E$. Well, the isomorphism class of $\mc E$ corresponds to some cohomology class in $H^2( G,A)$, for which we let $c$ be a representative; then $\mc E\simeq\mc E_c$, so we may show the statement for $\mc E\coloneqq\mc E_c$. Indeed, as the lifts $F_i=(x_i,\sigma_i)$ change, we know by \autoref{lem:explicitalphabeta} that
	\[\alpha_i=N_i(x_i)\cdot\prod_{k=0}^{n_i-1}c\left(\sigma_i^k,\sigma_i\right)\qquad\text{and}\qquad\beta_{ij}=\frac{x_i}{\sigma_j(x_i)}\cdot\frac{\sigma_i(x_j)}{x_j}\cdot\frac{c(\sigma_i,\sigma_j)}{c(\sigma_j,\sigma_i)}\]
	for each $\alpha_i$ and $\beta_{ij}$. All of these live in the same equivalence class by definition of the equivalence, and as the $x_i$ are allowed to vary over all of $A$, they will fill up that equivalence class fully. This finishes.
\end{proof}
We are now ready to upgrade our section.
\begin{cor} \label{cor:cohomologymakesaclass}
	Fix everything as in the modified set-up, forgetting about the extension $\mc E$. Fixing a cohomology class $[c]\in H^2( G,A)$, the set of $\{\sigma_i\}_{i=1}^m$-tuples which correspond to $[c]$ (via \autoref{thm:getcocycle}) forms exactly one equivalence class.
\end{cor}
\begin{proof}
	We show that two tuples are equivalent if and only if their corresponding cocycles (via \autoref{thm:getcocycle}) to the same cohomology class, which will be enough.
	
	In one direction, suppose $(\{\alpha_i\},\{\beta_{ij}\})\sim(\{\alpha_i'\},\{\beta_{ij}'\})$. By \autoref{cor:alltuplesfromextens}, we can find an extension $\mc E$ which gives $(\{\alpha_i\},\{\beta_{ij}\})$ by choosing an appropriate set of lifts. By \autoref{prop:extenmakesaclass}, we see that $(\{\alpha_i'\},\{\beta_{ij}'\})$ must also come from choosing an appropriate set of lifts in $\mc E$. However, the cocycles in $Z^2( G,A)$ generated by \autoref{thm:getcocycle} from our two tuples now both represent the isomorphism class of $\mc E$ by \autoref{prop:writedowncocycle}, so these cocycles belong to the same cohomology class.

	In the other direction, name the cocycles corresponding to $(\{\alpha_i\},\{\beta_{ij}\})$ and $(\{\alpha_i'\},\{\beta_{ij}'\})$ by $c$ and $c'$ respectively, and suppose $[c]=[c']$. Then $\mc E_c\simeq\mc E_{c'}$ as extensions, but we know by the proof of \autoref{cor:alltuplesfromextens} that $(\{\alpha_i\},\{\beta_{ij}\})$ comes from choosing lifts of $\mc E_c$ and similar for $(\{\alpha_i'\},\{\beta_{ij}'\})$. In particular, because $\mc E_c\simeq\mc E_{c'}$, we know that $(\{\alpha_i'\},\{\beta_{ij}'\})$ will also come from choosing some lifts in $\mc E_c$ (recall the proof of \autoref{prop:extenmakesaclass}), so $(\{\alpha_i\},\{\beta_{ij}\})\sim(\{\alpha_i'\},\{\beta_{ij}'\})$ follows.
\end{proof}
\begin{theorem} \label{thm:classisomorphism}
	The maps described in \autoref{cor:cocycletuplesection} descend to an isomorphism of abelian groups between the equivalence classes in $\overline{\mathcal T}(G,A)$ and cohomology classes in $H^2( G,A)$.
\end{theorem}
\begin{proof}
	The fact that the maps are well-defined (in both directions) and hence injective is \autoref{cor:cohomologymakesaclass}. The fact that we had a section from tuples to cocycles implies that the map from cocycles to tuples was also surjective. Thus, we have a bona fide isomorphism.
\end{proof}

\subsection{Classification of Extensions}
We remark that we are now able to classify all extensions up to isomorphism, in some sense. At a high level, an isomorphism class of extensions corresponds to a particular cohomology class in $H^2( G,A)$, so choosing a $\{\sigma_i\}_{i=1}^m$-tuple $(\{\alpha_i\},\{\beta_{ij}\})$ corresponding to this class, we can write out a representative of this cocycle by \autoref{thm:getcocycle}, properly corresponding to the original extension by \autoref{prop:writedowncocycle}.

In fact, the cocycle in \autoref{prop:writedowncocycle} is generated by the description of the group law in \autoref{prop:multiplytwoelements}, and the entire computation only needed to use the following relations, for the appropriate choice of lifts $F_i$.
\begin{listalph}
	\item $F_ix=\sigma_i(x)F_i$ for each $i$ and $x\in A$.
	\item $F_i^{n_i}=\alpha_i$ for each $i$.
	\item $F_iF_jF_i^{-1}F_j^{-1}=\beta_{ij}$ for each $i>j$; i.e., $F_iF_j=\beta_{ij}F_jF_i$.
\end{listalph}
As such, the above relations fully describe the extension because they also specify the cocycle, and we know that this cocycle is well-defined. We summarize this discussion into the following theorem.
\begin{theorem}
	Fix everything as in the modified set-up, forgetting about the extension $\mc E$. Given a $\{\sigma_i\}_{i=1}^m$-tuple $(\{\alpha_i\},\{\beta_{ij}\})$, define the group $\mc E(\{\alpha_i\},\{\beta_{ij}\})$ as being generated by $A$ and elements $\{F_i\}_{i=1}^n$ having the following relations.
	\begin{listalph}
		\item $F_ix=\sigma_i(x)F_i$ for each $i$ and $x\in A$.
		\item $F_i^{n_i}=\alpha_i$ for each $i$.
		\item $F_iF_j=\beta_{ij}F_jF_i$ for each $i>j$.
	\end{listalph}
	Then the natural embedding $A\into\mc E(\{\alpha_i\},\{\beta_{ij}\})$ and projection $\pi\colon\mc E(\{\alpha_i\},\{\beta_{ij}\})\onto G$ by $F_i\mapsto\sigma_i$ makes $\mc E(\{\alpha_i\},\{\beta_{ij}\})$ into an extension. In fact, all extensions are isomorphic to some $\mc E(\{\alpha_i\},\{\beta_{ij}\})$.
\end{theorem}
\begin{proof}
	This follows from the preceding discussion, though we will provide a few more words in this proof. The exactness of
	\[1\to A\to\mc E(\{\alpha_i\},\{\beta_{ij}\})\stackrel\pi\to G\to1\]
	follows quickly. Further, the action of conjugation of $\mc E$ on $A$ corresponds correctly to the $ G$-action by (a). So we do indeed have an extension.

	It remains to show that all extensions are isomorphic to one of this type. Well, note that \autoref{prop:multiplytwoelements} and \autoref{prop:writedowncocycle} use only the above relations to write down a cocycle representing the isomorphism class of $\mc E(\{\alpha_i\},\{\beta_{ij}\})$, and it is the cocycle corresponding to the $\{\sigma_i\}_{i=1}^m$-tuple $(\{\alpha_i\},\{\beta_{ij}\})$ itself as described in \autoref{thm:getcocycle}.

	However, we know that as the equivalence class of $(\{\alpha_i\},\{\beta_{ij}\})$ changes, we will hit all cohomology classes in $H^2( G,A)$ by \autoref{thm:classisomorphism}. Thus, because every extension is represented by some cohomology class, every extension will be isomorphic to some $\mc E(\{\alpha_i\},\{\beta_{ij}\})$. This completes the proof.
\end{proof}

\subsection{Change of Group}
We continue in the modified set-up, but we will no longer need access to an extension $\mc E$. In this subsection, we are interested in what happens to tuples when the cocycle operations of $\op{Inf}\colon H^2\left(G/H,A^H\right)\to H^2(G,A)$ and $\op{Res}\colon H^2(G,A)\to H^2(H,A)$ are applied, where $H\subseteq G$ is some subgroup.

In general, this is difficult because the structure of a subgroup $H\subseteq G$ might not be particularly amenable to forming a tuple from a tuple in $G$. More concretely, $H$ might have generators which look very different from those of $G$. However, it will be enough for our purposes to restrict our attention to the subgroups of the form
\[H=\langle\sigma_1^{t_1},\ldots,\sigma_m^{t_m}\rangle,\]
where the $\{t_i\}_{i=1}^m$ are some positive integers. With that said, here are our computations. We begin with inflation.
\begin{lemma} \label{lem:tupleinflation}
	Fix everything as in the modified set-up, forgetting about the extension $\mc E$. Further, let $H\coloneqq\langle\sigma_1^{t_1},\ldots,\sigma_m^{t_m}\rangle$ be a subgroup with $t_\bullet\mid n_\bullet$, and let $\overline\sigma_i$ be the image of $\sigma_i$ in $G/H$. Consider the inflation map $\op{Inf}\colon H^2\left(G/H,A^H\right)\to H^2(G,A)$.
	
	If the cocycle $\overline c\in Z^2\left(G/H,A^H\right)$ gives the $\left\{\overline\sigma_i\right\}_{i=1}^m$-tuple $(\{\overline\alpha_i\},\{\overline\beta_{ij}\})$ (by \autoref{cor:cocycletuplesection}), then the cocycle $\op{Inf}\overline c\in Z^2(G,A)$ gives the $\{\sigma_i\}_{i=1}^m$-tuple
	\[\op{Inf}(\{\overline\alpha_i\},\{\overline\beta_{ij}\})\coloneqq(\{\alpha_i\},\{\beta_{ij}\})=\left(\left\{\overline\alpha_i^{n_i/\gcd(t_i,n_i)}\right\},\{\overline\beta_{ij}\}\right).\]
	Notably, $\gcd(t_i,n_i)$ is the order of $\overline\sigma_i\in G/H$.
\end{lemma}
\begin{proof}
	The point is to use the explicit formulae for the $\alpha_i$ and $\beta_{ij}$ of \autoref{lem:explicitalphabeta}.
	
	More explicitly, the map of \autoref{cor:cocycletuplesection} tells us that we can compute the tuple for $\op{Inf}\overline c$ by using our explicit formulae for $\alpha_i$ and $\beta_{ij}$ on the $2$-cocycle $\op{Inf}\overline c\in Z^2(G,A)$. For some $\alpha_i$, the computation is
	\begin{align*}
		\alpha_i &= \prod_{k=0}^{n_i-1}(\op{Inf}c)\left(\sigma_i^k,\sigma_i\right) \\
		&= \prod_{k=0}^{n_i-1}\overline c\left(\overline\sigma_i^k,\overline\sigma_i\right) \\
		&= \Bigg(\prod_{k=0}^{\gcd(n_i,t_i)-1}\overline c\left(\overline\sigma_i^k,\overline\sigma_i\right)\Bigg)^{n_i/\gcd(n_i,t_i)}
	\end{align*}
	where the last equality is because $\overline\sigma_i^{\gcd(n_i,t_i)}=1$ in $G/H$. In fact, $\gcd(n_i,t_i)$ is the order of $\overline\sigma_i$, so the product is just $\overline\alpha_i$ by \autoref{lem:explicitalphabeta} and how we defined $\overline\alpha_i$. It follows
	\[\alpha_i=\overline\alpha_i^{n_i/\gcd(n_i,t_i)}.\]
	Continuing, for some $\beta_{ij}$, we have
	\begin{align*}
		\beta_{ij} &= \frac{(\op{Inf}\overline c)(\sigma_i,\sigma_j)}{(\op{Inf}\overline c)(\sigma_j,\sigma_i)} \\
		&= \frac{\overline c(\overline\sigma_i,\overline\sigma_j)}{\overline c(\overline\sigma_j,\overline\sigma_i)} \\
		&= \overline\beta_{ij},
	\end{align*}
	where the last equality is by how we defined $\overline\beta_{ij}$. These computations complete the proof.
\end{proof}
\begin{remark} \label{rem:tupleinflationcommutativediagram}
	We can also the statement of \autoref{lem:tupleinflation} as asserting that the diagram
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXG1hdGhjYWwgVFxcbGVmdChHL0gsQV5IXFxyaWdodCkiXSxbMSwwLCJcXG1hdGhjYWwgVChHLEEpIl0sWzAsMSwiWl4yXFxsZWZ0KEcvSCxBXkhcXHJpZ2h0KSJdLFsxLDEsIlpeMihHLEEpIl0sWzAsMSwiXFxvcHtJbmZ9Il0sWzAsMiwiIiwyLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzEsMywiIiwwLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzIsMywiXFxvcHtJbmZ9IiwyXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{Z^2\left(G/H,A^H\right)} & {Z^2(G,A)} \\
		{\mathcal T\left(G/H,A^H\right)} & {\mathcal T(G,A)}
		\arrow["{\op{Inf}}", from=1-1, to=1-2]
		\arrow[two heads, from=1-1, to=2-1]
		\arrow[two heads, from=1-2, to=2-2]
		\arrow["{\op{Inf}}", from=2-1, to=2-2]
	\end{tikzcd}\]
	commutes, where the vertical morphisms are from \autoref{cor:cocycletuplesection}.
\end{remark}
\begin{remark} \label{rem:inflationclasses}
	In light of the fact that the cohomology class of some $\op{Inf}\overline c\in Z^2(G,A)$ is only defined up to the cohomology class of $\overline c\in Z^2\left(G/H,A^H\right)$, changing an input tuple $(\{\overline\alpha_i\},\{\overline\beta_{ij}\})\in\mathcal T\left(G/H,A^H\right)$ up to equivalence will not change the cohomology class of the associated cocycle in $\overline c\in Z^2\left(G/H,A^H\right)$ and hence will not change the cohomology class of $\op{Inf}\overline c$ nor the equivalence class of $\op{Inf}(\{\overline\alpha_i\},\{\overline\beta_{ij}\})\in\mathcal T\left(G,A\right)$. All this is to say that we have a well-defined map
	\[\op{Inf}\colon\overline{\mathcal T}\left(G/H,A^H\right)\to\overline{\mathcal T}(G,A)\]
	and commutative diagram
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXG92ZXJsaW5le1xcbWF0aGNhbCBUfVxcbGVmdChHL0gsQV5IXFxyaWdodCkiXSxbMSwwLCJcXG92ZXJsaW5le1xcbWF0aGNhbCBUfShHLEEpIl0sWzAsMSwiSF4yXFxsZWZ0KEcvSCxBXkhcXHJpZ2h0KSJdLFsxLDEsIkheMihHLEEpIl0sWzAsMSwiXFxvcHtJbmZ9Il0sWzAsMiwiIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJ0b3AifSwiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzEsMywiIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJ0b3AifSwiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzIsMywiXFxvcHtJbmZ9IiwyXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\overline{\mathcal T}\left(G/H,A^H\right)} & {\overline{\mathcal T}(G,A)} \\
		{H^2\left(G/H,A^H\right)} & {H^2(G,A)}
		\arrow["{\op{Inf}}", from=1-1, to=1-2]
		\arrow[hook, two heads, from=1-1, to=2-1]
		\arrow[hook, two heads, from=1-2, to=2-2]
		\arrow["{\op{Inf}}", from=2-1, to=2-2]
	\end{tikzcd}\]
	induced by modding out from \autoref{rem:tupleinflationcommutativediagram}.
\end{remark}
Restriction is similar.
\begin{lemma} \label{lem:restricttuple}
	Fix everything as in the modified set-up, forgetting about the extension $\mc E$. Further, let $H\coloneqq\langle\sigma_1^{t_1},\ldots,\sigma_m^{t_m}\rangle$ be a subgroup with $t_\bullet\mid n_\bullet$. Consider the inflation map $\op{Res}\colon H^2\left(G,A\right)\to H^2(H,A)$.
	
	If the cohomology class $[c]\in H^2\left(G,A\right)$ is represented by the $\left\{\sigma_i\right\}_{i=1}^m$-tuple $(\{\alpha_i\},\{\beta_{ij}\})$, then the cohomology class $[\op{Res}\overline c]$ is represented by the $\{\sigma_i\}_{i=1}^m$-tuple
	\[(\{\overline\alpha_i\},\{\overline\beta_{ij}\})=\left(\left\{\alpha_i^{1_{n_i\mid t_i}}\right\},\left\{\beta_{ij}^{(\gcd(t_i,n_i)1_{n_i\mid t_i},\,\gcd(t_j,n_j)1_{n_i\mid t_i})}\right\}\right).\]
\end{lemma}
\begin{proof}
	By replacing $t_i$ with $\gcd(t_i,n_i)$ (which does not affect $\langle\sigma_i^{t_i}\rangle$ and hence does not affect $H$), we may assume that $t_i=\gcd(t_i,n_i)$. As in the previous proof, we will simply define $c$ by \autoref{thm:getcocycle}, and we will use the formulae of \autoref{lem:explicitalphabeta} to retrieve the $\left\{\sigma_i^{t_i}\right\}$-tuple for $\op{Res}c$. Indeed, we compute
	\begin{align*}
		\overline\alpha_i &= \prod_{k=0}^{n_i/t_i-1}(\op{Res}c)\left(\sigma_i^{t_ik},\sigma_i^{t_i}\right) \\
		&= \prod_{k=0}^{n_i/t_i-1}c\left(\sigma_i^{t_ik},\sigma_i^{t_i}\right) \\
		&= \prod_{k=0}^{n_i/t_i-1}\alpha_i^{\floor{t_i(k+1)/n_i}},
	\end{align*}
	where in the last equality we have used the construction of $c$. Now, if $n_i\mid t_i$, then $n_i=t_i$, and the product is empty, and we get $1$; otherwise, the last term of the product $k=n_i/t_i-1$ is the only term which does not return $1$, and it returns $\alpha_i$. So this matches the claimed $\alpha_i^{1_{n_i\mid t_i}}$.

	Continuing, we compute
	\begin{align*}
		\overline\beta_{ij} &= \frac{(\op{Res}c)\left(\sigma_i^{t_i},\sigma_j^{t_j}\right)}{(\op{Res}c)\left(\sigma_j^{t_j},\sigma_i^{t_i}\right)} \\
		&= \frac{c\left(\sigma_i^{t_i},\sigma_j^{t_j}\right)}{c\left(\sigma_j^{t_j},\sigma_i^{t_i}\right)} \\
		&= c\left(\sigma_i^{t_i},\sigma_j^{t_j}\right),
	\end{align*}
	where in the last step we have used the construction of $c$. Now, if $n_i\mid t_i$ or $n_i\mid t_j$, then we are computing $c\left(1,\sigma_j^{t_j}\right)$ or $c\left(\sigma_i^{t_i},1\right)$, which are both $1$, as needed. Otherwise, $t_i<n_i$ and $t_j<n_j$, so
	\[\overline\beta_{ij}=\beta_{ij}^{(t_it_j)},\]
	which again is as claimed.
\end{proof}
Thankfully, we will really only care about inflation in the following discussion, but we will say that there are analogues of \autoref{rem:tupleinflationcommutativediagram} and \autoref{rem:inflationclasses}.

\subsection{Profinite Groups}
In this subsection, we will use our results on change of group to extend our results a little to allow profinite groups. As such, we will want to slightly modify our set-up; we will call the following set-up the ``profinite set-up.''

Let $\mathcal I$ be a poset category such that any pair of elements has an upper bound (i.e., a directed set), and let the functor $G_\bullet\colon\mathcal I\opp\to\op{FinAbGrp}$ be an inverse system of finite abelian groups. These will create a profinite group
\[G\coloneqq\limit_{i\in\mathcal I}G_i.\]
In order to be able to apply our theory, we will assume that $G$ is a finite direct sum of procyclic groups as
\[G\simeq\bigoplus_{k=1}^m\overline{\langle\sigma_k\rangle}\]
for some elements $\{\sigma_k\}_{k=1}^m\subseteq G$. Further, we will require that the kernel $N_i$ of the map $G\onto G_i$ to take the form
\[N_i\coloneqq\overline{\left\langle\sigma_1^{t_{i,1}},\ldots,\sigma_m^{t_{i,m}}\right\rangle}.\]
In short, our restriction on the $N_i$ will allow our inflation maps to be computable in the sense of \autoref{lem:tupleinflation}. We quickly remark that, because the topology on $G$ is the coarsest one making the projections $G\onto G_i$ continuous, the subsets $\{N_i\}_{i\in\mathcal I}$ give a fundamental system of open neighborhoods around the identity.
\begin{remark}
	Of course, one could also start with $G$ being a finite direct sum of procyclic groups and then define the $N_i$ and $G_i$ accordingly. We have chosen the above approach because in application one might only have access to select $G_i$s, and it is not obvious how to choose these from such a ``top-down'' approach.
\end{remark}
\begin{example}
	To show that we are still allowing interesting groups, we can set 
	\[G_{m,\nu}\coloneqq\op{Gal}\left(\QQ_p(\zeta_{p^m-1})\QQ_p(\zeta_{p^\nu})/\QQ_p\right)\simeq\op{Gal}\left(\QQ_p(\zeta_{p^m-1})/\QQ_p\right)\oplus\op{Gal}\left(\QQ_p(\zeta_{p^\nu})/\QQ_p\right),\]
	which becomes $G=\op{Gal}\left(\QQ_p^{\op{ab}}/\QQ_p\right)\simeq\widehat\ZZ\oplus\ZZ_p^\times$ upon taking the inverse limit. It is not very hard to check that the kernels are generated correctly; for example, when $p$ is odd, we have $\ZZ_p^\times\cong\ZZ/(p-1)\ZZ\oplus\ZZ_p$, and under our isomorphisms, we will have
	\[\op{Gal}\left(\QQ(\zeta_{p^\nu})/\QQ_p\right)\simeq\ZZ/(p-1)\ZZ\oplus\ZZ_p/p^{\nu-1}\ZZ_p,\]
	so the kernel of $G\onto G_{m,\nu}$ is $m\widehat\ZZ\oplus(\ZZ/(p-1)\ZZ)^{1_{\nu=0}}\oplus p^{\nu-1}\ZZ_p$.
	% let $K$ be a local field with $\op{char}K=0$, and set $G_{\pi,n,m}\coloneqq\op{Gal}(K_{\pi,n}K_m/K)$, where $\{K_{\pi,n}\}$ is an ascending chain of Lubin--Tate extension and $K_m$ is the unramified extension of degree $m$. Then
	% \begin{align*}
	% 	\colimit_{n,m}\op{Gal}(K_{\pi,n}K_m/K) &\cong \op{Gal}(K^{\mathrm{ab}}/K) \\
	% 	&\cong \op{Gal}(K^{\op{unr}}/K)\oplus\op{Gal}(K_\pi) \\
	% 	&\cong \overline{\langle\op{Frob}_K\rangle}\oplus\mathcal O_K^\times \\
	% 	&\cong \widehat\ZZ\oplus\FF_\mf p^\times\oplus(1+\mf p) \\
	% 	&\cong \widehat\ZZ\oplus\FF_\mf p^\times\oplus\ZZ/p^a\ZZ\oplus\ZZ_p^{[K:\QQ_p]}
	% \end{align*}
	% for some sufficiently large $a\in\NN$; here the last isomorphism is by the logarithm map, which exists because $\op{char}K=0$. (For details, see \cite{neukirch-alg-nt}, Proposition II.5.7.)
\end{example}
\begin{remark}
	I'm not sure if such an explicit construction can be extended to other local fields $K$ (say, via Lubin--Tate theory). Because $K^\times$ is not topologically finitely generated when $K$ is in positive characteristic (see for example \cite{neukirch-alg-nt}, Proposition~II.5.7) such a construction must do something subtle.
\end{remark}
Let $A$ be a discrete $G$-module. The main goal of this subsection is to be able to provide a notion of a ``compatible system'' of tuples from each individual $H^2(G_i,A)$ to be able to exactly describe an element of $H^2(G,A)$. To effect this, we have the following somewhat annoying checks.
% \begin{lemma}
% 	Fix everything as in the profinite set-up, and let $N\subseteq G$ be an open normal subgroup. If $\sigma\in G$ is such that $[\sigma]_N\in G/N$ has finite order $n_\sigma$, then there exists some $i\in\mathcal I$ such that the order of $[\sigma]_{N_i}\in G/N_i=G_i$ has order divisible by $n_\sigma$.
% \end{lemma}
% \begin{proof}
% 	We proceed in steps. Let $1$ denote the identity of $G$.
% 	\begin{enumerate}
% 		\item Suppose that $p\coloneqq n_\sigma$ is prime. We proceed by contraposition. Namely, suppose there is no $N_i$ such that $\sigma^p\in N_i$, and we will show that $[\sigma]_N\in G/N$ cannot have order $p$. We may assume that $\sigma^p\in N$, which means that we are actually interested in showing $\sigma\in N$.

% 		Well, we claim that $\sigma$ is a limit point of $\langle\sigma^p\rangle$. To see this, we need to show that any open neighborhood $U$ around $\sigma$ has nontrivial intersection with $\langle\sigma^p\rangle$. Indeed, $\sigma^{-1}U$ is an open set containing the identity, but because the $\{N_i\}_{i\in\mathcal I}$ form a fundamental system of open neighborhoods around the identity, we have $N_i\subseteq\sigma^{-1}U$ for some $i\in\mathcal I$. Thus, it suffices to show that 
% 		\[\sigma N_i\cap\langle\sigma^p\rangle\ne\emp.\]
% 		Now, the order of $\sigma N_i$ is not divisible by $p$, so $\langle\sigma^pN_i\rangle=\langle\sigma N_i\rangle$ and in particular $\langle\sigma^pN_i\rangle$ contains $\sigma N_i$. Concretely, let's say $\sigma^{pk}N_i=\sigma N_i$; then $\sigma^{pk}\in\sigma N_i\cap\langle\sigma^p\rangle$, finishing.

% 		In total, because $N$ is an open subgroup and hence closed, we see that $\sigma^p\in N$ must also contain $\langle\sigma^p\rangle$ and hence must contain the limit point $\sigma$. This finishes.

% 		\item Next suppose that $n_\sigma=p^\nu$ is a power of a prime. We proceed by induction on $\nu$. When $\nu=0$, there is nothing to say because the order of a group element is always divisible by $1$; when $\nu=1$, this is the previous step. Otherwise, when $\nu>1$, we note that $\left[\sigma^p\right]_N=[\sigma]_N^p$ has order $p^{\nu-1}$: certainly $[\sigma]_N^{p\cdot p^{\nu-1}}$ vanishes, so the order divides $p^{\nu-1}$, but no smaller of $p$ will do because this would make the order of $[\sigma]_N$ too small.

% 		Thus, by the inductive hypothesis, there exists some $i\in\mathcal I$ such that the order of $[\sigma^p]_{N_i}$ has order divisible by $p^{\nu-1}$. We claim $[\sigma]_{N_i}$ has order divisible by $p^\nu$. Indeed, if not, then there exists some $k$ with $p\nmid k$ such that
% 		\[[\sigma]_{N_i}^{p^{\nu-1}k}=[1]_{N_i},\]
% 		from which we conclude that the order of $[\sigma^p]$ divides $p^{\nu-2}k$, which is not divisible by $p^{\nu-1}$.

% 		\item To finish, we show a version of multiplicativity: if the order of $[\sigma]_{N_p}$ is divisible by $n_p$, and the order of $[\sigma]_{N_q}$ is divisible by $n_q$ with $\gcd(n_p,n_q)=1$, then there exists $r\in\mathcal I$ such that the order of $[\sigma]_{N_r}$ is divisible by $n_pn_q$.

% 		Indeed, because $\mathcal I$ is a directed set, there exists some $r\in\mathcal I$ with morphisms $i\to r$ and $j\to r$. These correspond to having morphisms $G_r\to G_i$ and $G_r\to G_j$, and the fact that these morphisms are well-defined requires $N_r\subseteq N_i,N_j$.

% 		Now, let's say that the order of $[\sigma]_{N_r}$ is $n_r$; we want to show $n_pn_q\mid n_r$. Because $\gcd(n_p,n_q)=1$, it suffices (by symmetry) to show $n_p\mid n_r$. Well, $\sigma^{n_r}\in N_r\subseteq N_p$, so
% 		\[[\sigma]_{N_p}^{n_r}=[1]_{N_p},\]
% 		so the order of $[\sigma]_{N_p}$ divides $n_r$. In particular, $n_p\mid n_r$.
% 	\end{enumerate}
% 	We now note that, for the general case of $n\in\NN$, we can prime-factor $n$ into coprime factors, use step 2 to create a list of $N_i$, one for each prime factor, and then use step 3 to glue them all together. This completes the proof.
% \end{proof}
% \begin{lemma}
% 	Fix everything as in the profinite set-up. Then, for any open normal subgroup $N\subseteq G$, there exists $i\in\mathcal I$ so that $N$ contains $N_i$.
% \end{lemma}
% \begin{proof}
% 	This follows directly from the fact that the collection $\{N_i\}_{i\in\mathcal I}$ is a fundamental system of open neighborhoods around the identity of $G$. In particular, $N$ contains the identity and is open.
% 	% Because $G$ is compact (it's profinite), we have $[G:N]<\infty$. In particular, for any $\sigma\in G$, we must have $\sigma^{[G:N]}\in N$.
% 	% Thus, it will roughly speaking be enough to show that, for any $\sigma_k$ and $t\in\NN$, we have $\sigma_k^t\in N_i$ for some $i\in\mathcal I$. We have two cases.
% 	% \begin{itemize}
% 	% 	\item Suppose that $\sigma_k\in G$ has infinite order. 
% 	% \end{itemize}
% \end{proof}
\begin{lemma} \label{lem:colimitfiltered}
	Suppose that $\mathcal P$ is a directed set, and let $\mathcal P'\subseteq\mathcal P$ be a subcategory such that any $x\in\mathcal P$ has some $x'\in\mathcal P'$ such that $x\le x'$. Then, given a functor $F\colon\mathcal P\to\mathcal C$, we have
	\[\colimit_\mathcal PF\simeq\colimit_{\mathcal P'}F,\]
	provided that both colimits exist.
\end{lemma}
\begin{proof}
	For concreteness, if $x\le y$ in $\mathcal P$, we will let $f_{yx}\colon x\to y$ be the corresponding morphism; in particular, $x\le y\le z$ has $f_{zx}=f_{zy}f_{yx}$. Now, for brevity, set
	\[X\coloneqq\colimit_\mathcal PF\qquad\text{and}\qquad X'\coloneqq\colimit_{\mathcal P'}F.\]
	By the Yoneda lemma, it suffices to fix some object $Y\in\mathcal C$ and show that $\op{Mor}_\mathcal C(X,Y)\simeq\op{Mor}_\mathcal C(X',Y)$. Well, morphsims $X\to Y$ are in (natural) bijection with cones under $F$ with nadir $Y$, and morphisms $X'\to Y$ are in (natural) bijection with cones under $F'\coloneqq F|_{\mathcal P'}$ with nadir $Y$.

	Thus, it suffices to give a natural bijection between cones under $F$ with nadir $Y$ and cones under $F'$ with nadir $Y$. Well, given a cone under $F$ with nadir $Y$, we can simply restrict it to $\mathcal P'$ to get a cone under $F'$. In the other direction, given a cone under $F'$ with nadir $Y$, we can build a cone under $F$ with nadir $Y$ as follows; let $\varphi_{x'}\colon F(x')\to Y$ for $x'\in\mathcal P'$ be the corresponding morphisms in our cone.
	
	For any $x\in\mathcal P$, find $x'\in\mathcal P'$ such that $x\le x'$. Then set
	\[\varphi_x\coloneqq\varphi_{x'}\circ f_{x'x}\]
	Note that $\varphi_x$ is in fact independent of our choice of $x'$: if $x\le x_1'$ and $x\le x_2'$, then because $\mathcal P$ is a directed set, we can find $y\in\mathcal P$ such that $x_1',x_2'\le y$ and then $y'\in\mathcal P'$ with $y\le y'$. Then
	\begin{align*}
		\varphi_{x_\bullet'}\circ f_{x_\bullet'x} &= \varphi_{y'}\circ f_{y'x_\bullet'}\circ f_{x_\bullet'x} \\
		&= \varphi_{y'}\circ f_{y'x}
	\end{align*}
	for $x_\bullet'\in\{x_1',x_2'\}$. Anyway, we can check that the morphisms $\varphi$ do assemble to a cone under $F'$: if $x\le y$ in $\mathcal P$, then find $y'\in\mathcal P$ with $x\le y\le y'$, and we compute
	\begin{align*}
		\varphi_y\circ f_{yx} &= \varphi_{y'}\circ f_{y'y}\circ f_{yx} \\
		&= \varphi_{y'}\circ f_{y'x} \\
		&= \varphi_x.
	\end{align*}
	Thus, we do have a natural, well-defined map sending cones under $F'$ with nadir $Y$ to cones under $F$ with nadir $Y$. It is not too hard to see that these maps are inverse to each other (for example, the cone under $F'$, extended to $F$, does indeed restrict back to $F'$ properly), which completes the proof.
\end{proof}
\begin{remark}
	One can remove the hypothesis that the colimits exist and use essentially the same proof.
\end{remark}
\begin{proposition} \label{prop:bettercohomlimit}
	Fix everything as in the profinite set-up. Then, given a discrete $G$-module $A$,
	\[H^2(G,A)\simeq\colimit_{i\in\mathcal I}H^2\left(G_i,A^{N_i}\right).\]
	Here, the morphisms between the collection of $H^2\left(G_i,A^{N_i}\right)$ are induced by inflation: if $i\to j$ in $\mathcal I$, then $G_j\to G_i$ in $\mathrm{FinAbGrp}$, giving an inflation map $\op{Inf}\colon H^2\left(G_i,A^{N_i}\right)\to H^2\left(G_j,A^{N_j}\right)$.
\end{proposition}
\begin{proof}
	Let $\mathcal N$ be the poset category of open normal subgroups of $G$, reverse ordered under inclusion; i.e., $N_1\subseteq N_2$ in $G$ induces a map $N_2\to N_1$. Then it is already known that
	\[H^2(G,A)\simeq\colimit_{N\in\mathcal N}H^2\left(G/N,A^N\right).\]
	On the other hand, observe that $i\le j$ in $\mathcal I$ induces $G_j\to G_i$, so $N_j\subseteq N_i$. In other words, $i\mapsto N_i$ will define a functor $\mathcal I\to\mathcal N$; functoriality follows because $\mathcal I$ and $\mathcal N$ are poset categories. Letting $\mathcal N'$ denote the image of $\mathcal I$ in $\mathcal N$, we see
	\[\colimit_{i\in\mathcal I}H^2\left(G_i,A^{N_i}\right)\simeq\colimit_{N\in\mathcal N'}H^2\left(G/N,A^N\right).\]
	Notably, the inflation maps $\op{Inf}\colon H^2\left(G_i,A^{N_i}\right)\to H^2\left(G_j,A^{N_j}\right)$ when $i\le j$ become the inflation maps $\op{Inf}\colon H^2\left(G/N,A^N\right)\to H^2\left(G/N',A^{N'}\right)$ when $N'\subseteq N$. So if we let $F\colon\mathcal N\to\op{AbGrp}$ be the functor taking $N$ to $H^2\left(G/N,A^N\right)$ (and $N\subseteq N'$ to the inflation map), we are trying to show
	\[\colimit_{\mathcal N}F=\colimit_{\mathcal N'}F.\]
	For this, we use \autoref{lem:colimitfiltered}. Indeed, for a given open normal subgroup $N\in\mathcal N$, we need to find some $N'\in\mathcal N'$ such that $N\le N'$, which means $N'\subseteq N$.
	
	However, the elements of $\mathcal N'$ are the collection $\{N_i\}_{i\in\mathcal I}$, which form a fundamental system of open neighborhoods around the identity. Thus, the fact that $N$ is an open set containing the identity implies there is some $N_i\in\mathcal N'$ such that $N_i\subseteq N$. This finishes the proof.
\end{proof}
Observe that the above proofs did not use the extra hypotheses on $G$ nor $N_i$ to be products of procyclic groups. We use these hypotheses now.
% \begin{definition}
% 	Fix everything as in the profinite set-up, and let $A$ be a discrete $G$-module. Then a \textit{compatible system of $\{\sigma_p\}_{p=1}^m$-tuples} is an indexed set
% 	\[\left(\{\alpha_{i,p}\},\{\beta_{i,pq}\}\right)_{i\in\mathcal I}\]
% 	such that $\left(\{\alpha_{i,p}\},\{\beta_{i,pq}\}\right)$ is a $\{\sigma_pN_i\}_{p=1}^m$-tuple (corresponding to a class in $H^2\left(G_i,A^{N_i}\right)$) and
% 	\[\op{Inf}\left(\{\alpha_{i,p}\},\{\beta_{i,pq}\}\right)\sim\left(\{\alpha_{j,p}\},\{\beta_{j,pq}\}\right)\]
% 	as tuples corresponding to $H^2\left(G_j,A^{N_j}\right)$, whenever $i\le j$ in $\mathcal I$. We also define the relation $\sim$ of equivalence between compatible systems if and only if they are pointwise equivalent.
% \end{definition}
% The precise definition above is one of technical convenience, as we will shortly see.
To work more concretely, we note that any $i\in\mathcal I$ has
\[G_i\simeq\frac G{N_i}\simeq\bigoplus_{p=1}^m\overline{\langle\sigma_p\rangle}/\overline{\langle\sigma_p^{t_{i,p}}\rangle}\simeq\bigoplus_{p=1}^m\langle\sigma_p\rangle/\langle\sigma_p^{t_{i,p}}\rangle\subseteq\bigoplus_{p=1}^m\ZZ/t_{i,p}\ZZ\]
is a finite abelian group generated by the elements $\sigma_pN_i$. As a warning, the order of $\sigma_pN_i$ might not be $t_{i,p}$, for example if $\sigma_p$ itself has some small finite order which $t_{i,p}$ is not properly capitalizing on. More concretely, $\ZZ_5/3\ZZ_5=0$.

Regardless, the main point is that, given a discrete $G$-module $A$, we can consider the $\{\sigma_pN_i\}_{p=1}^m$-tuples $\mathcal T\left(G_i,A^{N_i}\right)$. Now, as discussed above, $i\le j$ in $\mathcal I$ induces a quotient map $G_j\simeq G/N_j\onto G_i/N_i$. From this, we have the following coherence check.
\begin{lemma} \label{lem:tupleinflationcommutes}
	Fix everything as in the profinite set-up, and let $A$ be a discrete $G$-module. Then, given $i\le j\le k$ in $\mathcal I$, the diagram
	% https://q.uiver.app/?q=WzAsMyxbMCwwLCJcXG1hdGhjYWwgVFxcbGVmdChHX2ksQV9pXntOX2l9XFxyaWdodCkiXSxbMSwwLCJcXG1hdGhjYWwgVFxcbGVmdChHX2osQV9qXntOX2p9XFxyaWdodCkiXSxbMSwxLCJcXG1hdGhjYWwgVFxcbGVmdChHX2ssQV9rXntOX2t9XFxyaWdodCkiXSxbMCwxLCJcXG9we0luZn0iXSxbMSwyLCJcXG9we0luZn0iXSxbMCwyLCJcXG9we0luZn0iLDJdXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\mathcal T\left(G_i,A^{N_i}\right)} & {\mathcal T\left(G_j,A^{N_j}\right)} \\
		& {\mathcal T\left(G_k,A^{N_k}\right)}
		\arrow["{\op{Inf}}", from=1-1, to=1-2]
		\arrow["{\op{Inf}}", from=1-2, to=2-2]
		\arrow["{\op{Inf}}"', from=1-1, to=2-2]
	\end{tikzcd}\]
	commutes. Here, the $\op{Inf}$ maps are defined as in \autoref{lem:tupleinflation}.
\end{lemma}
\begin{proof}
	For each $i\in\mathcal I$, we let $n_{i,p}$ denote the order of $\sigma_pN_i\in G_i$. Using the definition of $\op{Inf}$ from \autoref{lem:tupleinflation}, we just pick up some $\{\sigma_pN_p\}_{p=1}^m$-tuple $(\{\alpha_p\},\{\beta_{pq}\})$-tuple in $\mathcal T\left(G_i,A^{N_i}\right)$ and track through the diagram as follows.
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCIoXFx7XFxhbHBoYV9wXFx9LFxce1xcYmV0YV97cHF9XFx9KSJdLFsxLDAsIlxcbGVmdChcXGJpZ1xce1xcYWxwaGFfcF57bl97aixwfS9uX3tpLHB9fVxcYmlnXFx9LFxce1xcYmV0YV97cHF9XFx9XFxyaWdodCkiXSxbMSwxLCJcXGxlZnQoXFxiaWdcXHtcXGFscGhhX3BeeyhuX3tqLHB9L25fe2kscH0pKG5fe2sscH0vbl97aixwfSl9XFxiaWdcXH0sXFx7XFxiZXRhX3twcX1cXH1cXHJpZ2h0KSJdLFswLDEsIlxcbGVmdChcXGJpZ1xce1xcYWxwaGFfcF57bl97ayxwfS9uX3tpLHB9fVxcYmlnXFx9LFxce1xcYmV0YV97cHF9XFx9XFxyaWdodCkiXSxbMCwxLCJcXG9we0luZn0iXSxbMSwyLCJcXG9we0luZn0iXSxbMCwzLCJcXG9we0luZn0iLDJdLFszLDIsIiIsMix7ImxldmVsIjoyLCJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJub25lIn19fV1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{(\{\alpha_p\},\{\beta_{pq}\})} & {\left(\big\{\alpha_p^{n_{j,p}/n_{i,p}}\big\},\{\beta_{pq}\}\right)} \\
		{\left(\big\{\alpha_p^{n_{k,p}/n_{i,p}}\big\},\{\beta_{pq}\}\right)} & {\left(\big\{\alpha_p^{(n_{j,p}/n_{i,p})(n_{k,p}/n_{j,p})}\big\},\{\beta_{pq}\}\right)}
		\arrow["{\op{Inf}}", from=1-1, to=1-2]
		\arrow["{\op{Inf}}", from=1-2, to=2-2]
		\arrow["{\op{Inf}}"', from=1-1, to=2-1]
		\arrow[Rightarrow, no head, from=2-1, to=2-2]
	\end{tikzcd}\]
	This completes the proof.
\end{proof}
% Now, if we let $n_{i,p}$ denote the actual order of $\sigma_{i,p}N_i\in G_i$, then we may compute the inflation map $\op{Inf}\colon H^2\left(G_i,A^{N_i}\right)\to H^2\left(G_j,A^{N_j}\right)$ by
% \[\op{Inf}\left(\{\alpha_{i,p}\},\{\beta_{i,pq}\}\right)=\left(\{\alpha_{i,p}^{n_{j,p}}\},\{\beta_{i,pq}\}\right),\]
% so we are asking for
% \[\left(\{\alpha_{i,p}^{n_{j,p}}\},\{\beta_{i,pq}\}\right)\sim\left(\{\alpha_{j,p}\},\{\beta_{j,pq}\}\right)\]
% in the coherence condition for a compatible tuple.
% \begin{remark}
% 	From the above description, we can see why we ``have'' to allow the equivalence relation into our notion of compatibility. For example, if one of the $G_i$ is the trivial group, and $A^G$ is trivial, then we would be requiring all the $\beta_{i,pq}$ elements to be trivial for all $i\in\mathcal I$. This is not good.
% \end{remark}
And here is the result.
\begin{theorem}
	Fix everything as in the profinite set-up, and let $A$ be a discrete $G$-module. Then the isomorphisms of \autoref{thm:classisomorphism} upgrade into an isomorphism
	\[H^2(G,A)\simeq\colimit_{i\in\mathcal I}\overline{\mathcal T}\left(G_i,A^{N_i}\right).\]
	Here the morphisms between the $\overline{\mathcal T}\left(G_i,A^{N_i}\right)$ are inflation maps of \autoref{lem:tupleinflation}.
\end{theorem}
\begin{proof}
	Note that the objects $\overline{\mathcal T}\left(G_i,A^{N_i}\right)$ do make a directed system over $\mathcal I$ because of the commutativity of \autoref{lem:tupleinflationcommutes}. Namely, the lemma checks that $\mathcal I\to\op{AbGrp}$ by $i\mapsto\overline{\mathcal T}\left(G_i,A^{N_i}\right)$ is actually functorial; technically we must also check that the maps $\overline{\mathcal T}\left(G_i,A^{N_i}\right)\to\overline{\mathcal T}\left(G_i,A^{N_i}\right)$ are the identity, but this follows from the definition.

	Now, by \autoref{prop:bettercohomlimit}, we have
	\[H^2(G,A)\simeq\colimit_{i\in\mathcal I}H^2\left(G_i,A^{N_i}\right),\]
	but now the natural isomorphism induced by \autoref{rem:inflationclasses} induces an isomorphism of direct limits
	\[\colimit_{i\in\mathcal I}H^2\left(G_i,A^{N_i}\right)\simeq\colimit_{i\in\mathcal I}\overline{\mathcal T}\left(G_i,A^{N_i}\right)\]
	given by the isomorphism of \autoref{thm:classisomorphism} acting pointwise. This completes the proof.
\end{proof}
Because there are reasonably explicit descriptions of direct limits of abelian groups, and we already have an explicit description of each $\overline{\mathcal T}\left(G_i,A^{N_i}\right)$ term in addition to a description of the inflation maps between them, we will be content with our sufficiently explicit description of $H^2(G,A)$. So we call it done here.