% !TEX root = ../abeliangerbs.tex

The goal of this section is to separate out what we can, a priori, expect from ``encoding'' modules from what is a special property of the specific encoding module we study in the rest of the paper. As such, we should begin by motivating encoding modules.

Throughout this section, let $G$ be a finite group. When $G=\langle\sigma\rangle$ is a cyclic group of order $n$, it is an amazing feature that there is some $\chi\in\widehat H^2(G,\ZZ)$ granting isomorphisms
\begin{equation}
	(\chi\cup-)\colon\widehat H^0(G,M)\to\widehat H^2(G,M) \label{eq:motivatingcycliccohom}
\end{equation}
for any $G$-module $M$. In fact, it is not too hard to write down $\chi$ as being represented by the ``carrying'' $2$-cocycle
\[\left(\sigma^i,\sigma^j\right)\mapsto\floor{\frac{i+j}n},\]
so \autoref{eq:motivatingcycliccohom} is telling us that we can represent each cohomology class of $\widehat H^2(G,M)$ by a $2$-cocycle of the form
\[\left(\sigma^i,\sigma^j\right)\mapsto\floor{\frac{i+j}n}\alpha\]
for some $\alpha\in M^G$. This ``classification'' of $2$-cocycles in $\widehat H^2(G,M)$ is incredibly useful and makes cyclic groups very easy to work with computationally.

From one perspective, this classification of $2$-cocycles for cyclic groups says that we can retrieve all $2$-cocycles by keeping track of the single element $\alpha\in M^G=H^0(G,M)$, modulo some equivalence relation coming from Tate cohomology. The algebraic way to choose a single element of $M^G$ is by elements in
\[\op{Hom}_\ZZ\left(\ZZ,M^G\right)=\op{Hom}_{\ZZ[G]}(\ZZ,M).\]
As such, one can phrase \autoref{eq:motivatingcycliccohom} as providing a natural isomorphism
\[\widehat H^0(G,\op{Hom}_\ZZ(\ZZ,-))\Rightarrow\widehat H^2(G,-).\]
Here, the choice of $G$-module $\ZZ$ in some sense ``encodes'' $2$-cocycles from $\widehat H^2(G,M)$ into a single morphism from $\ZZ$ to $M$, modulo some equivalence relations.

More generally, permit $G$ to be non-cyclic, and suppose we have a $G$-module $\ZZ[G]^m/I$ for some $m\ge0$ and $G$-submodule $I$ with isomorphisms
\[\widehat H^0\left(G,\op{Hom}_\ZZ(\ZZ[G]^m/I,M)\right)\to\widehat H^2(G,M),\]
for any $G$-module $M$. In this case, we see we are still encoding $2$-cocycles into morphisms, where these morphisms look like
\[\widehat H^0\left(G,\op{Hom}_\ZZ(\ZZ[G]^m/I,M)\right)=\frac{\op{Hom}_{\ZZ[G]}\left(\ZZ[G]^m/I,M\right)}{N_G\op{Hom}_\ZZ(\ZZ[G]^m/I,M)}.\]
To see the encoding here, view the numerator as choosing out an $m$-tuple of elements of $M$ in the same way that we would choose morphisms $\op{Hom}_{\ZZ[G]}\left(\ZZ[G]^m,M\right)$, but we can't just choose any $m$ elements because they must saitsfy some relations dictated by $I$. Then the denominator provides an equivalence relation of the $m$-tuples which determines if two tuples live in the same ``class.''

The above discussion is intended to motivate the following definition.
\begin{definition}
	Let $G$ be a finite group and $r\in\ZZ$ be an index. Then a $G$-module $X$ is an \textit{$r$-encoding $G$-module} if and only if there is a natural isomorphism
	\[\Phi_\bullet\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(G,-)\]
	for some $i\in\ZZ$.
\end{definition}
We will abbreviate the $G$ from ``$r$-encoding $G$-module'' whenever confusion is unlikely to arise.

It will turn out that the index $i\in\ZZ$ is more or less irrelevant. Indeed, we will be able to show the following equivalences.
\begin{theorem}
	Let $G$ be a finite group. Given a $G$-module $X$ and index $r\in\ZZ$, the following are equivalent.
	\begin{enumerate}[label=(\alph*)]
		\item $X$ is an $r$-encoding module.
		\item If $r\ge0$, then $X$ is cohomologically equivalent to $I_G^{\otimes r}$; if $r<0$, then $X$ is cohomologically equivalent to $\op{Hom}_\ZZ(I_G^{\otimes r},\ZZ)$.
		\item There is $x\in\widehat H^r(G,X)$ granting a natural isomorphism
		\[(x\cup-)\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(G,-)\]
		for any $i\in\ZZ$.
		\item There are $x\in\widehat H^r(G,X)$ and $x^\lor\in\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))$ such that
		\[x\cup x^\lor=[1]\in\widehat H^0(G,\ZZ)\qquad\text{and}\qquad x^\lor\cup x=[{\id_X}]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X)).\]
		\item We can find $x\in\widehat H^r(G,X)$ yielding natural isomorphisms
		\[(-\cup x)\colon\widehat H^i(G,-)\Rightarrow\widehat H^{i+r}(G,-\otimes_\ZZ X)\]
		for all $i\in\ZZ$.
	\end{enumerate}
	If $X$ is also $\ZZ$-free, these are equivalent to
	\begin{enumerate}[label=(\alph*),resume]
		\item $\widehat H^r(G,X)\cong\ZZ/\#G\ZZ$ and $\widehat H^0(G,\op{Hom}_\ZZ(X,X))$ is cyclic.
	\end{enumerate}
\end{theorem}
\begin{proof}
	The equivalence of (a) and (b) follow from combining \autoref{prop:encodingmodules} with \autoref{ex:igisencoding} and \autoref{ex:allencoderesexist}. The equivalence of (c) follows from \autoref{prop:encodingsarecups}. Continuing, the equivalence of (d) follows from \autoref{prop:intdualelement}. The equivalence of (e) follows from \autoref{thm:tensorencode} and the discussion in \autoref{rem:bighandwave}. Lastly, the equivalence of (f) follows from \autoref{prop:finitecohomcheck}.
\end{proof}

% Throughout this section, $G$ will be a finite group. To motivate where we are going, we will go ahead and say that a $p$-encoding $G$-module $X$ is a $G$-module equipped with a natural isomorphism
% \[\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+p}(G,-).\]
% The idea is that, in the case of $i=0$ for a specific $G$-modulee $A$, we are taking cohomology of $\widehat H^p(G,A)$ and encoding this data as
% \[\widehat H^0(G,\op{Hom}_\ZZ(X,A))=\frac{\op{Hom}_{\ZZ[G]}(X,A)}{N_G\op{Hom}_\ZZ(X,A)}.\]
% If $X$ is finitely generated, we can write $X=\ZZ[G]^m/M$ for some $m\ge0$ and $G$-module $M$, so this object essentially picks out $m$ elements of $A$ and encodes some relations among them. In other words, an $m$-tuple of elements in $A$ (satisfying some special relations) is able to encode cohomology.

When we may take $X=\ZZ$ (e.g., when $G$ is cyclic), we are essentially studying groups with periodic cohomology, so many results in this section will mimic these results. However, periodic cohomology requires somewhat stringent conditions on the group itself, and allowing this ``free parameter'' $X$ will permit general groups at the cost of a perhaps more complex $X$. For example, when $r\ge0$, we can take $X=I_G^{\otimes r}$ for any finite group $G$, though this $G$-module is quite rough to handle.

In general, it can be an interesting question what specified abelian groups $X$ can be turned into encoding modules or dually what the encoding modules for a given group $G$ look like. Many of the results in this section are motivated by a desire to provide partial answers or intuition towards answers to these questions.

\subsection{Shiftable Functors}
The main point of this section is to set up some theory around what we call shiftable functors, whose main application will be in the proofs of \autoref{cor:cupup} and \autoref{cor:cupdown}.
\begin{definition}
	Let $G$ be a finite group. Then a functor $F\colon\op{Mod}_G\to\op{Mod}_G$ is a \textit{shiftable functor} if and only if $F$ is both additive and sends induced modules to induced modules.
\end{definition}
The main point to shiftable functors $F$ is that the dimension-shifting short exact sequences
\[\arraycolsep=1.4pt\begin{array}{ccccccccc}
	0 &\to& I_G\otimes_\ZZ A &\to& \ZZ[G]\otimes_\ZZ A &\to& A &\to& 0 \\
	0 &\to& A &\to& \op{Hom}_\ZZ(\ZZ[G],A) &\to& \op{Hom}_\ZZ(I_G,A) &\to& 0
\end{array}\]
will remain exact upon applying $F$ (because $F$ is additive, and these short exact sequences are $\ZZ$-split), and the middle term will remain induced.

Here are our key examples of shiftable functors.
\begin{lemma} \label{lem:contravariantshiftable}
	Let $G$ be a finite group and $X$ a $G$-module. Then $\op{Hom}_\ZZ(-,X)$ is a (contravariant) shiftable functor.
\end{lemma}
\begin{proof}
	We already know that $\op{Hom}_\ZZ(-,X)$ is additive, so the main check is that we send induced modules to induced modules. Well, without loss of generality, let $M\coloneqq\ZZ[G]\otimes_\ZZ A$ be our induced module. Then the tensor--hom adjunction gives
	\[\op{Hom}_\ZZ(M,X)=\op{Hom}_\ZZ(\ZZ[G]\otimes_\ZZ A,X)\simeq\op{Hom}_\ZZ(\ZZ[G],\op{Hom}_\ZZ(A,X)),\]
	which is also a $G$-module isomorphism. This finishes.
\end{proof}
\begin{lemma} \label{lem:hompreservesinduced}
	Let $G$ be a finite group and $X$ a $G$-module. Then $\op{Hom}_\ZZ(X,-)$ is a shiftable functor.
\end{lemma}
\begin{proof}
	It is known that $\op{Hom}_\ZZ(X,-)$ is an additive functor, so we just need to check that it sends induced modules to induced modules. Well, pick up some induced module $M\coloneqq\op{Hom}_\ZZ(\ZZ[G],A)$ for some $G$-module $A$. Then we see
	\[\op{Hom}_\ZZ(X,M) = \op{Hom}_\ZZ(X,\op{Hom}_\ZZ(\ZZ[G],A)) \simeq \op{Hom}_\ZZ(X\otimes_\ZZ\ZZ[G],A),\]
	which is induced by noting $X\otimes_\ZZ\ZZ[G]$ is induced and using \autoref{lem:contravariantshiftable}.
	% Now, we claim that
	% \[\arraycolsep=1.4pt\begin{array}{cccc}
	% 	\varphi\colon& \op{Hom}_\ZZ(X,\op{Hom}_\ZZ(\ZZ[G],A)) &\simeq& \op{Hom}_\ZZ(\ZZ[G],\op{Hom}_\ZZ(X,A)) \\
	% 	\varphi\colon& f &\mapsto& \big(z\mapsto(x\mapsto f(x)(z))\big)
	% \end{array}\]
	% is an isomorphism of $G$-modules. This will finish because the right-hand $G$-module is induced.
	%
	% Now, $\varphi$ s a homomorphism of abelian groups because
	% \[\varphi(f+f')(z)(x)=(f+g)(x)(z)=\varphi(f)(z)(x)+\varphi(f')(z)(x)\]
	% for any $x$ and $z$ and $f,f'\in\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(\ZZ[G],A))$. This is a $G$-module homomorphism because any $g\in G$ and $f\in\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(\ZZ[G],A))$ has
	% \begin{align*}
	% 	\varphi(gf)(z)(x) &= \big(g\cdot\varphi(f)(g^{-1}z)\big)(x) \\
	% 	&= g\cdot\varphi(f)(g^{-1}z)(g^{-1}x) \\
	% 	&= g\cdot f(g^{-1}x)(g^{-1}z) \\
	% 	&= \big(g\cdot f(g^{-1}x)\big)(z) \\
	% 	&= (gf)(x)(z) \\
	% 	&= \varphi(gf)(x)(z)
	% \end{align*}
	% for each $x$ and $z$.
	%
	% Now, we define
	% \[\arraycolsep=1.4pt\begin{array}{cccc}
	% 	\psi\colon& \op{Hom}_\ZZ(\ZZ[G],\op{Hom}_\ZZ(X,A)) &\simeq& \op{Hom}_\ZZ(X,\op{Hom}_\ZZ(\ZZ[G],A)) \\
	% 	\psi\colon& f &\mapsto& \big(x\mapsto(z\mapsto f(z)(x))\big)
	% \end{array}\]
	% to be the inverse morphism. The exact same checks show that this is a $G$-module homomorphism, and it is not hard to see that
	% \[\varphi\psi(f)(z)(x)=\psi(f)(z)(x)=f(x)(z),\]
	% so $\varphi\circ\psi$ is the identity; similarly, $\psi\circ\varphi$ is the identity.
\end{proof}
\begin{lemma}
	Let $G$ be a finite group and $X$ a $G$-module. Then $X\otimes_\ZZ-$ is a shiftable functor.
\end{lemma}
\begin{proof}
	Again, $X\otimes_\ZZ-$ is additive, so we just need to check that it sends induced modules to induced modules. Well, suppose $M\coloneqq\ZZ[G]\otimes_\ZZ A$ is an induced module. Then we note the isomorphisms
	\[X\otimes_\ZZ M=X\otimes_\ZZ\ZZ[G]\otimes_\ZZ A\simeq\ZZ[G]\otimes_\ZZ(X\otimes_\ZZ A)\]
	are all also isomorphisms of $G$-modules. Because $\ZZ[G]\otimes_\ZZ(X\otimes_\ZZ A)$ is induced, we are done.
\end{proof}
Of course, we can create some crazier examples of shiftable functors by melding them together.
\begin{lemma}
	Let $G$ be a finite group. If $F$ and $F'$ are shiftable functors, then $F\circ F'$ is a shiftable functor.
\end{lemma}
\begin{proof}
	This follows directly from the definition.
\end{proof}
\begin{example}
	The functor
	\[A\mapsto\op{Hom}_\ZZ\big(A\otimes_\ZZ\op{Hom}_\ZZ(I_G,I_G\otimes_\ZZ A),I_G\big)\]
	is a shiftable functor.
\end{example}

\subsection{Shifting by Cup Products}
A key property of shiftable functors is how we will be able to relate them to each other via cup products. With this in mind, we have the following definition.
\begin{definition}
	Let $G$ be a finite group. Then we define a \textit{shifting pair} $(F,F',X,\eta)$ to be a pair of shiftable functors $F$ and $F'$ equipped with a natural transformation
	\[\eta_\bullet\colon X\otimes_\ZZ F\Rightarrow F'.\]
\end{definition}
The following will be our key example.
\begin{example} \label{ex:shiftingpair}
	Given $G$-modules $X$ and $X'$, there is a canonical composition map
	\[\arraycolsep=1.4pt\begin{array}{crllcc}
		\eta_\bullet\colon&\op{Hom}_\ZZ(X',X)&\otimes_\ZZ&\op{Hom}_\ZZ(X,-)&\Rightarrow&\op{Hom}_\ZZ(X',-) \\
		& \varphi &\otimes& f &\mapsto& f\circ\varphi
	\end{array}\]
	so $(\op{Hom}_\ZZ(X,-),\op{Hom}_\ZZ(X',-),\op{Hom}_\ZZ(X',X),\eta_\bullet)$ is a shifting pair.
\end{example}
In particular, cup products assemble into natural transformations.
\begin{lemma} \label{lem:cuppingisnatural}
	Let $G$ be a finite group, and let $(F,F',X,\eta)$ be a shifting pair. Then, given indices $r,s\in\ZZ$ and $c\in\widehat H^r(G,X)$, the cup-product maps
	\[(c\cup-)\colon\widehat H^s(G,F-)\Rightarrow\widehat H^{r+s}(G,F'-)\]
	make a natural transformation of cohomology functors.
\end{lemma}
\begin{proof}
	Given a $G$-module $A$, we note that our cup-product map is defined by
	\[\widehat H^s(G,FA)\stackrel{c\cup-}\to\widehat H^{r+s}(G,X\otimes_\ZZ FA)\stackrel{\eta_A}\to\widehat H^{r+s}(G,F'A).\]
	So, to check naturality, we pick up a $G$-module homomorphism $\varphi\colon A\to B$ and draw the following diagram.
	% https://q.uiver.app/?q=WzAsNixbMCwwLCJcXHdpZGVoYXQgSF5xKEcsRkEpIl0sWzEsMCwiXFx3aWRlaGF0IEhee3ArcX0oRyxYXFxvdGltZXNfXFxaWiBGQSkiXSxbMiwwLCJcXHdpZGVoYXQgSF57cCtxfShHLEYnQSkiXSxbMCwxLCJcXHdpZGVoYXQgSF5xKEcsRkIpIl0sWzEsMSwiXFx3aWRlaGF0IEhee3ArcX0oRyxYXFxvdGltZXNfXFxaWiBGQikiXSxbMiwxLCJcXHdpZGVoYXQgSF57cCtxfShHLEYnQikiXSxbMCwxLCJjXFxjdXAtIl0sWzEsMiwiXFxldGFfQSJdLFs0LDUsIlxcZXRhX0IiXSxbMSw0LCJmIiwyXSxbMiw1LCJmIiwyXSxbMCwzLCJmIiwyXSxbMyw0LCJjXFxjdXAtIl1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\widehat H^s(G,FA)} & {\widehat H^{r+s}(G,X\otimes_\ZZ FA)} & {\widehat H^{r+s}(G,F'A)} \\
		{\widehat H^s(G,FB)} & {\widehat H^{r+s}(G,X\otimes_\ZZ FB)} & {\widehat H^{r+s}(G,F'B)}
		\arrow["{c\cup-}", from=1-1, to=1-2]
		\arrow["{\eta_A}", from=1-2, to=1-3]
		\arrow["{\eta_B}", from=2-2, to=2-3]
		\arrow["f"', from=1-2, to=2-2]
		\arrow["f"', from=1-3, to=2-3]
		\arrow["f"', from=1-1, to=2-1]
		\arrow["{c\cup-}", from=2-1, to=2-2]
	\end{tikzcd}\]
	The left square commutes by functoriality of cup products (see \cite{bonn-lectures}, Proposition~I.5.3), and the right square commutes by the naturality of $\eta$ and functoriality of $\widehat H^{r+s}(G,-)$.
\end{proof}
It will turn out occasionally that we have multiple evaluation maps flying around, so we pick up the following lemma for reassurance.
\begin{lemma} \label{lem:cupassoc}
	Let $G$ be a finite group, and let $A$, $B$, $C$ be $G$-modules equipped with maps
	\begin{align*}
		\varphi_{AB}\colon& A\otimes_\ZZ B\to X \\
		\varphi_{XC}\colon& X\otimes_\ZZ C\to Z \\
		\varphi_{BC}\colon& B\otimes_\ZZ C\to Y \\
		\varphi_{AY}\colon& A\otimes_\ZZ Y\to Z
	\end{align*}
	making the diagram
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJBXFxvdGltZXNfXFxaWiBCXFxvdGltZXNfXFxaWiBDIl0sWzEsMCwiWFxcb3RpbWVzX1xcWlogQyJdLFswLDEsIkFcXG90aW1lc19cXFpaIFkiXSxbMSwxLCJaIl0sWzAsMiwiXFx2YXJwaGlfe0JDfSIsMl0sWzIsMywiXFx2YXJwaGlfe0FZfSJdLFswLDEsIlxcdmFycGhpX3tBQn0iXSxbMSwzLCJcXHZhcnBoaV97WEN9Il1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{A\otimes_\ZZ B\otimes_\ZZ C} & {X\otimes_\ZZ C} \\
		{A\otimes_\ZZ Y} & Z
		\arrow["{\varphi_{BC}}"', from=1-1, to=2-1]
		\arrow["{\varphi_{AY}}", from=2-1, to=2-2]
		\arrow["{\varphi_{AB}}", from=1-1, to=1-2]
		\arrow["{\varphi_{XC}}", from=1-2, to=2-2]
	\end{tikzcd}\]
	commute. Then, for any $a\in\widehat H^r(G,A)$ and $b\in\widehat H^s(G,B)$ and $c\in\widehat H^t(G,C)$, we have
	\[(a\cup b)\cup c=a\cup(b\cup c)\in\widehat H^{r+s+t}(G,Z).\]
\end{lemma}
\begin{proof}
	The point is to track $b\in\widehat H^s(G,B)$ through the following very large commutative diagram.
	% https://q.uiver.app/?q=WzAsOSxbMSwxLCJcXHdpZGVoYXQgSF57citzK3R9KEcsQVxcb3RpbWVzX1xcWlogQlxcb3RpbWVzX1xcWlogQykiXSxbMiwxLCJcXHdpZGVoYXQgSF57citzK3R9KEcsWFxcb3RpbWVzX1xcWlogQykiXSxbMSwyLCJcXHdpZGVoYXQgSF57citzK3R9KEcsQVxcb3RpbWVzX1xcWlogWSkiXSxbMiwyLCJcXHdpZGVoYXQgSF57citzK3R9KEcsWikiXSxbMCwwLCJcXHdpZGVoYXQgSF5zKEcsQikiXSxbMSwwLCJcXHdpZGVoYXQgSF57citzfShHLEFcXG90aW1lc19cXFpaIEIpIl0sWzIsMCwiXFx3aWRlaGF0IEhee3Irc30oRyxYKSJdLFswLDEsIlxcd2lkZWhhdCBIXntzK3R9KEcsQlxcb3RpbWVzX1xcWlogQykiXSxbMCwyLCJcXHdpZGVoYXQgSF57cyt0fShHLFkpIl0sWzAsMiwiXFx2YXJwaGlfe0JDfSIsMl0sWzIsMywiXFx2YXJwaGlfe0FZfSJdLFswLDEsIlxcdmFycGhpX3tBQn0iXSxbMSwzLCJcXHZhcnBoaV97WEN9IiwyXSxbNCw1LCJhXFxjdXAtIl0sWzUsNiwiXFx2YXJwaGlfe0FCfSJdLFs1LDAsImNcXGN1cC0iLDJdLFs2LDEsImNcXGN1cC0iLDJdLFs0LDcsImNcXGN1cC0iLDJdLFs3LDAsImFcXGN1cC0iXSxbNyw4LCJcXHZhcnBoaV97QkN9IiwyXSxbOCwyLCJhXFxjdXAtIl0sWzE3LDE1LCIoMSkiLDEseyJzaG9ydGVuIjp7InNvdXJjZSI6MjAsInRhcmdldCI6MjB9LCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJub25lIn0sImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMTUsMTYsIigyKSIsMSx7InNob3J0ZW4iOnsic291cmNlIjoyMCwidGFyZ2V0IjoyMH0sInN0eWxlIjp7ImJvZHkiOnsibmFtZSI6Im5vbmUifSwiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFsxOSw5LCIoMykiLDEseyJzaG9ydGVuIjp7InNvdXJjZSI6MjAsInRhcmdldCI6MjB9LCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJub25lIn0sImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbOSwxMiwiKDQpIiwxLHsic2hvcnRlbiI6eyJzb3VyY2UiOjIwLCJ0YXJnZXQiOjIwfSwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoibm9uZSJ9LCJoZWFkIjp7Im5hbWUiOiJub25lIn19fV1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\widehat H^s(G,B)} & {\widehat H^{r+s}(G,A\otimes_\ZZ B)} & {\widehat H^{r+s}(G,X)} \\
		{\widehat H^{s+t}(G,B\otimes_\ZZ C)} & {\widehat H^{r+s+t}(G,A\otimes_\ZZ B\otimes_\ZZ C)} & {\widehat H^{r+s+t}(G,X\otimes_\ZZ C)} \\
		{\widehat H^{s+t}(G,Y)} & {\widehat H^{r+s+t}(G,A\otimes_\ZZ Y)} & {\widehat H^{r+s+t}(G,Z)}
		\arrow[""{name=0, anchor=center, inner sep=0}, "{\varphi_{BC}}"', from=2-2, to=3-2]
		\arrow["{\varphi_{AY}}", from=3-2, to=3-3]
		\arrow["{\varphi_{AB}}", from=2-2, to=2-3]
		\arrow[""{name=1, anchor=center, inner sep=0}, "{\varphi_{XC}}"', from=2-3, to=3-3]
		\arrow["{a\cup-}", from=1-1, to=1-2]
		\arrow["{\varphi_{AB}}", from=1-2, to=1-3]
		\arrow[""{name=2, anchor=center, inner sep=0}, "{c\cup-}"', from=1-2, to=2-2]
		\arrow[""{name=3, anchor=center, inner sep=0}, "{c\cup-}"', from=1-3, to=2-3]
		\arrow[""{name=4, anchor=center, inner sep=0}, "{c\cup-}"', from=1-1, to=2-1]
		\arrow["{a\cup-}", from=2-1, to=2-2]
		\arrow[""{name=5, anchor=center, inner sep=0}, "{\varphi_{BC}}"', from=2-1, to=3-1]
		\arrow["{a\cup-}", from=3-1, to=3-2]
		\arrow["{(1)}"{description}, Rightarrow, draw=none, from=4, to=2]
		\arrow["{(2)}"{description}, Rightarrow, draw=none, from=2, to=3]
		\arrow["{(3)}"{description}, Rightarrow, draw=none, from=5, to=0]
		\arrow["{(4)}"{description}, Rightarrow, draw=none, from=0, to=1]
	\end{tikzcd}\]
	Namely, $(a\cup b)\cup c$ corresponds to following the top and then right legs of the diagram, and $a\cup(b\cup c)$ corresponds to following the left and then bottom legs of the diagram.
	
	Thus, it suffices to show that the entire diagram square commutes. Well, $(1)$ commutes by associativity of the cup product, $(2)$ and $(3)$ commute by naturality of the cup product, and $(4)$ commutes by the hypothesized square and functoriality of $\widehat H^{r+s+t}(G,-)$. This finishes.
\end{proof}
Let's start with a key result on shiftable functors, which gives a taste for why our hypotheses are so specially chosen.
\begin{proposition} \label{prop:dimshiftcupisos}
	Let $G$ be a finite group, and let $(F,F',X,\eta)$ be a shifting pair. If we have indices $r,s\in\ZZ$ and $c\in H^r(G,X)$ such that the cup-product map
	\[(c\cup-)\colon\widehat H^s(G,F-)\Rightarrow\widehat H^{r+s}(G,F'-)\]
	is a natural isomorphism, then the cup-product map
	\[(c\cup-)\colon\widehat H^j(G,F-)\Rightarrow\widehat H^{r+j}(G,F'-)\]
	is a natural isomorphism for all indices $j\in\ZZ$.
\end{proposition}
\begin{proof}
	This proof is by dimension-shifting on $j$. Note that it suffices by \autoref{lem:cuppingisnatural} to only worry about the component morphisms being isomorphisms.
	
	To shift downwards, we suppose that the cup-product map is always an isomorphism for $j$, and we show that it is always an isomorphism $j-1$. Namely, fix a $G$-module $A$, and we are interested in showing that the cup-product map
	\[(c\cup-)\colon\widehat H^{j-1}(G,FA)\to\widehat H^{r+j-1}(G,F'A)\]
	is an isomorphism. To do so, we note the short exact sequence
	\begin{equation}
		0\to I_G\to\ZZ[G]\to\ZZ\to0 \label{eq:shiftingses}
	\end{equation}
	which splits over $\ZZ$ and thus gives us the short exact sequences
	% https://q.uiver.app/?q=WzAsMTUsWzAsMCwiMCJdLFsxLDAsIlxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBBKSJdLFsyLDAsIlxcb3B7SG9tfV9cXFpaKFgsXFxaWltHXVxcb3RpbWVzX1xcWlogQSkiXSxbMywwLCJcXG9we0hvbX1fXFxaWihYLEEpIl0sWzQsMCwiMCJdLFswLDEsIjAiXSxbNCwxLCIwIl0sWzEsMSwiWFxcb3RpbWVzX1xcWlpcXG9we0hvbX1fXFxaWihYLElfR1xcb3RpbWVzX1xcWlogQSkiXSxbMiwxLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsXFxaWltHXVxcb3RpbWVzX1xcWlogQSkiXSxbMywxLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMCwyLCIwIl0sWzEsMiwiSV9HXFxvdGltZXNfXFxaWiBBIl0sWzIsMiwiXFxaWltHXVxcb3RpbWVzX1xcWlogQSJdLFszLDIsIkEiXSxbNCwyLCIwIl0sWzAsMV0sWzEsMl0sWzIsM10sWzMsNF0sWzUsN10sWzcsOF0sWzgsOV0sWzksNl0sWzEwLDExXSxbMTEsMTJdLFsxMiwxM10sWzEzLDE0XSxbNywxMSwiXFxldGFfe0lfR30iLDJdLFs4LDEyLCJcXGV0YV97XFxaWltHXX0iLDJdLFs5LDEzLCJcXGV0YV9BIiwyXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		0 & {F(I_G\otimes_\ZZ A)} & {F(\ZZ[G]\otimes_\ZZ A)} & {FA} & 0 \\
		0 & {X\otimes_\ZZ F(I_G\otimes_\ZZ A)} & {X\otimes_\ZZ F(\ZZ[G]\otimes_\ZZ A)} & {X\otimes_\ZZ FA} & 0 \\
		0 & {F'(I_G\otimes_\ZZ A)} & {F'(\ZZ[G]\otimes_\ZZ A)} & {F'A} & 0
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-2, to=1-3]
		\arrow[from=1-3, to=1-4]
		\arrow[from=1-4, to=1-5]
		\arrow[from=2-1, to=2-2]
		\arrow[from=2-2, to=2-3]
		\arrow[from=2-3, to=2-4]
		\arrow[from=2-4, to=2-5]
		\arrow[from=3-1, to=3-2]
		\arrow[from=3-2, to=3-3]
		\arrow[from=3-3, to=3-4]
		\arrow[from=3-4, to=3-5]
		\arrow["{\eta_{I_G}}"', from=2-2, to=3-2]
		\arrow["{\eta_{\ZZ[G]}}"', from=2-3, to=3-3]
		\arrow["{\eta_A}"', from=2-4, to=3-4]
	\end{tikzcd}\]
	where the bottom two rows commute by definition of $\eta$ and thus give a morphism of short exact sequences. These short exact sequences give us boundary morphisms
	\[\arraycolsep=1.4pt\begin{array}{rccc}
		\delta\colon& \widehat H^{r+j-1}(G,F'A) &\to& \widehat H^{r+j}(G,F'(I_G\otimes_\ZZ A)) \\
		\delta_h\colon& \widehat H^{j-1}(G,FA) &\to& \widehat H^j(G,F(I_G\otimes_\ZZ A)) \\
		\delta_t\colon& \widehat H^{r+j-1}(G,X\otimes_\ZZ FA) &\to& \widehat H^{r+j}(G,X\otimes_\ZZ F(I_G\otimes_\ZZ A)).
	\end{array}\]
	Notably, all these $\delta$ morphisms because their short exact sequences have induced middle terms: all of $F$ and $X\otimes_\ZZ F$ and $F'$ are shiftable functors.
	
	Now, the key to this dimension-shifting is claiming that the diagram
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF57ai0xfShHLFxcb3B7SG9tfV9cXFpaKFgsQSkpIl0sWzEsMCwiXFx3aWRlaGF0IEhee3Arai0xfShHLEEpIl0sWzAsMSwiXFx3aWRlaGF0IEhee2p9KEcsXFxvcHtIb219X1xcWlooWCxJX0dcXG90aW1lc19cXFpaIEEpKSJdLFsxLDEsIlxcd2lkZWhhdCBIXntwK2p9KEcsSV9HXFxvdGltZXNfXFxaWiBBKSJdLFswLDEsImNcXGN1cC0iXSxbMiwzLCJjXFxjdXAtIl0sWzAsMiwiXFxkZWx0YV9oIiwyXSxbMSwzLCJcXGRlbHRhIiwyXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\widehat H^{j-1}(G,FA)} & {\widehat H^{r+j-1}(G,F'A)} \\
		{\widehat H^{j}(G,F(I_G\otimes_\ZZ A))} & {\widehat H^{r+j}(G,F'(I_G\otimes_\ZZ A))}
		\arrow["{c\cup-}", from=1-1, to=1-2]
		\arrow["{c\cup-}", from=2-1, to=2-2]
		\arrow["{\delta_h}"', from=1-1, to=2-1]
		\arrow["(-1)^r\delta"', from=1-2, to=2-2]
	\end{tikzcd}\]
	commutes. Indeed, this will be enough because the bottom row is an isomorphism by the inductive hypothesis, and the left and morphisms are isomorphisms as discussed above, which makes the top row into an isomorphism. Well, to see that the diagram commutes, we expand the diagram as follows.
	% https://q.uiver.app/?q=WzAsNixbMCwwLCJcXHdpZGVoYXQgSF57ai0xfShHLFxcb3B7SG9tfV9cXFpaKFgsQSkpIl0sWzEsMCwiXFx3aWRlaGF0IEhee3Aran0oRyxYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKEEpKSJdLFswLDEsIlxcd2lkZWhhdCBIXntqfShHLFxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBBKSkiXSxbMSwxLCJcXHdpZGVoYXQgSF57cCtqfShHLFhcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooSV9HXFxvdGltZXNfXFxaWiBBKSkiXSxbMiwwLCJcXHdpZGVoYXQgSF57cCtqLTF9KEcsQSkiXSxbMiwxLCJcXHdpZGVoYXQgSF57cCtqfShHLElfR1xcb3RpbWVzX1xcWlogQSkiXSxbMCwxLCJjXFxjdXAtIl0sWzIsMywiY1xcY3VwLSJdLFswLDIsIlxcZGVsdGFfaCIsMl0sWzEsMywiXFxkZWx0YV90IiwyXSxbMSw0LCJcXGV0YV9BIl0sWzMsNSwiXFxldGFfe0lfR30iXSxbNCw1LCJcXGRlbHRhIiwyXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\widehat H^{j-1}(G,FA)} & {\widehat H^{r+j-1}(G,X\otimes_\ZZ FA)} & {\widehat H^{r+j-1}(G,F'A)} \\
		{\widehat H^{j}(G,F(I_G\otimes_\ZZ A))} & {\widehat H^{r+j}(G,X\otimes_\ZZ F(I_G\otimes_\ZZ A))} & {\widehat H^{r+j}(G,F'(I_G\otimes_\ZZ A))}
		\arrow["{c\cup-}", from=1-1, to=1-2]
		\arrow["{c\cup-}", from=2-1, to=2-2]
		\arrow["{\delta_h}"', from=1-1, to=2-1]
		\arrow["{(-1)^r\delta_t}"', from=1-2, to=2-2]
		\arrow["{\eta_A}", from=1-2, to=1-3]
		\arrow["{\eta_{I_G}}", from=2-2, to=2-3]
		\arrow["(-1)^r\delta"', from=1-3, to=2-3]
	\end{tikzcd}\]
	The left square commutes because cup products commute with boundary morphisms; the right square commutes by functoriality of boundary morphisms.

	Shifting upwards is similar. Suppose that the cup-product in question is always an isomorphism for $j$, and we show that it is always an isomorphism for $j+1$. Namely, fix a $G$-module $A$, and we are interested in showing that the cup-product map
	\[(c\cup-)\colon\widehat H^{j+1}(G,FA)\to\widehat H^{r+j+1}(G,F'A)\]
	is an isomorphism. As before, we use \autoref{eq:shiftingses} to induce the short exact sequences
	% https://q.uiver.app/?q=WzAsMTUsWzAsMCwiMCJdLFsxLDAsIlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMiwwLCJcXG9we0hvbX1fXFxaWihYLFxcb3B7SG9tfV9cXFpaKFxcWlpbR10sQSkpIl0sWzMsMCwiXFxvcHtIb219X1xcWlooWCxcXG9we0hvbX1fXFxaWihJX0csQSkpIl0sWzQsMCwiMCJdLFswLDEsIjAiXSxbNCwxLCIwIl0sWzEsMSwiWFxcb3RpbWVzX1xcWlpcXG9we0hvbX1fXFxaWihYLEEpIl0sWzIsMSwiWFxcb3RpbWVzX1xcWlpcXG9we0hvbX1fXFxaWihYLFxcb3B7SG9tfV9cXFpaKFxcWlpbR10sQSkpIl0sWzMsMSwiWFxcb3RpbWVzX1xcWlpcXG9we0hvbX1fXFxaWihYLFxcb3B7SG9tfV9cXFpaKElfRyxBKSkiXSxbMCwyLCIwIl0sWzEsMiwiQSJdLFsyLDIsIlxcb3B7SG9tfV9cXFpaKFxcWlpbR10sQSkiXSxbMywyLCJcXG9we0hvbX1fXFxaWihJX0csQSkiXSxbNCwyLCIwIl0sWzAsMV0sWzEsMl0sWzIsM10sWzMsNF0sWzUsN10sWzcsOF0sWzgsOV0sWzksNl0sWzEwLDExXSxbMTEsMTJdLFsxMiwxM10sWzEzLDE0XSxbNywxMSwiXFxldGFfQSIsMl0sWzgsMTIsIlxcZXRhX3tcXFpaW0ddfSIsMl0sWzksMTMsIlxcZXRhX3tJX0d9IiwyXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		0 & {FA} & {F(\op{Hom}_\ZZ(\ZZ[G],A))} & {F(\op{Hom}_\ZZ(I_G,A))} & 0 \\
		0 & {X\otimes_\ZZ FA} & {X\otimes_\ZZ F(\op{Hom}_\ZZ(\ZZ[G],A))} & {X\otimes_\ZZ F(\op{Hom}_\ZZ(I_G,A))} & 0 \\
		0 & F'A & {F'(\op{Hom}_\ZZ(\ZZ[G],A))} & {F'(\op{Hom}_\ZZ(I_G,A))} & 0
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-2, to=1-3]
		\arrow[from=1-3, to=1-4]
		\arrow[from=1-4, to=1-5]
		\arrow[from=2-1, to=2-2]
		\arrow[from=2-2, to=2-3]
		\arrow[from=2-3, to=2-4]
		\arrow[from=2-4, to=2-5]
		\arrow[from=3-1, to=3-2]
		\arrow[from=3-2, to=3-3]
		\arrow[from=3-3, to=3-4]
		\arrow[from=3-4, to=3-5]
		\arrow["{\eta_A}"', from=2-2, to=3-2]
		\arrow["{\eta_{\ZZ[G]}}"', from=2-3, to=3-3]
		\arrow["{\eta_{I_G}}"', from=2-4, to=3-4]
	\end{tikzcd}\]
	where again the bottom rows commute by definition of $\eta$. As before, we have the boundary morphisms
	\[\arraycolsep=1.4pt\begin{array}{rccc}
		\delta\colon& \widehat H^{r+j}(G,F'(\op{Hom}_\ZZ(I_G,A))) &\to& \widehat H^{r+j+1}(G,F'A) \\
		\delta_h\colon& \widehat H^{j}(G,F(\op{Hom}_\ZZ(I_G,A))) &\to& \widehat H^{j+1}(G,FA) \\
		\delta_t\colon& \widehat H^{r+j}(G,X\otimes_\ZZ F(\op{Hom}_\ZZ(I_G,A))) &\to& \widehat H^{r+j+1}(G,X\otimes_\ZZ FA).
	\end{array}\]
	We again note that all $\delta$ are isomorphisms because the middle terms of our short exact sequences are induced: all of $F$ and $X\otimes_\ZZ F$ and $F'$ are shiftable functors.

	Once more, the key to the dimension-shifting will be the claim that the diagram
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF57an0oRyxcXG9we0hvbX1fXFxaWihYLFxcb3B7SG9tfV9cXFpaKElfRyxBKSkpIl0sWzAsMSwiXFx3aWRlaGF0IEhee2orMX0oRyxcXG9we0hvbX1fXFxaWihYLEEpKSJdLFsxLDAsIlxcd2lkZWhhdCBIXntwK2p9KEcsXFxvcHtIb219X1xcWlooSV9HLEEpKSJdLFsxLDEsIlxcd2lkZWhhdCBIXntwK2orMX0oRyxBKSJdLFswLDEsIlxcZGVsdGFfaCIsMl0sWzIsMywiXFxkZWx0YSIsMl0sWzAsMiwiY1xcY3VwLSJdLFsxLDMsImNcXGN1cC0iXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\widehat H^{j}(G, F(\op{Hom}_\ZZ(I_G,A)))} & {\widehat H^{r+j}(G,F'(\op{Hom}_\ZZ(I_G,A)))} \\
		{\widehat H^{j+1}(G,FA)} & {\widehat H^{r+j+1}(G,F'A)}
		\arrow["{\delta_h}"', from=1-1, to=2-1]
		\arrow["(-1)^r\delta"', from=1-2, to=2-2]
		\arrow["{c\cup-}", from=1-1, to=1-2]
		\arrow["{c\cup-}", from=2-1, to=2-2]
	\end{tikzcd}\]
	commutes. This will be enough because the top arrow is an isomorphism by the inductive hypothesis, and the left and right arrows are isomorphisms as discussed above, thus making the bottom arrow also an isomorphism. Now, to see that the diagram commutes, we expand out our cup products as follows.
	% https://q.uiver.app/?q=WzAsNixbMCwwLCJcXHdpZGVoYXQgSF57an0oRyxcXG9we0hvbX1fXFxaWihYLFxcb3B7SG9tfV9cXFpaKElfRyxBKSkpIl0sWzAsMSwiXFx3aWRlaGF0IEhee2orMX0oRyxcXG9we0hvbX1fXFxaWihYLEEpKSJdLFsxLDAsIlxcd2lkZWhhdCBIXntwK2p9KEcsWFxcb3RpbWVzX1xcWlpcXG9we0hvbX1fXFxaWihJX0csQSkpIl0sWzEsMSwiXFx3aWRlaGF0IEhee3AraisxfShHLFhcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooWCxBKSkiXSxbMiwxLCJcXHdpZGVoYXQgSF57cCtqKzF9KEcsQSkiXSxbMiwwLCJcXHdpZGVoYXQgSF57cCtqfShHLFxcb3B7SG9tfV9cXFpaKElfRyxBKSkiXSxbMCwxLCJcXGRlbHRhX2giLDJdLFsyLDMsIigtMSlecFxcZGVsdGFfdCIsMl0sWzAsMiwiY1xcY3VwLSJdLFsxLDMsImNcXGN1cC0iXSxbMiw1LCJcXGV0YV97SV9HfSJdLFszLDQsIlxcZXRhX0EiXSxbNSw0LCIoLTEpXnBcXGRlbHRhIiwyXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\widehat H^{j}(G,F(\op{Hom}_\ZZ(I_G,A)))} & {\widehat H^{r+j}(G,X\otimes_\ZZ F(\op{Hom}_\ZZ(I_G,A)))} & {\widehat H^{r+j}(G,F'(\op{Hom}_\ZZ(I_G,A)))} \\
		{\widehat H^{j+1}(G,FA)} & {\widehat H^{r+j+1}(G,X\otimes_\ZZ FA)} & {\widehat H^{r+j+1}(G,F'A)}
		\arrow["{\delta_h}"', from=1-1, to=2-1]
		\arrow["{(-1)^r\delta_t}"', from=1-2, to=2-2]
		\arrow["{c\cup-}", from=1-1, to=1-2]
		\arrow["{c\cup-}", from=2-1, to=2-2]
		\arrow["{\eta_{I_G}}", from=1-2, to=1-3]
		\arrow["{\eta_A}", from=2-2, to=2-3]
		\arrow["{(-1)^r\delta}"', from=1-3, to=2-3]
	\end{tikzcd}\]
	The left square commutes because cup products commute with boundary morphisms, and the right square commutes by functoriality of boundary morphisms. This finishes.
\end{proof}
Here are some applications.
\begin{cor} \label{cor:cupup}
	Let $G$ be a finite group. There exists $c\in\widehat H^1(G,I_G)$ such that, for any $G$-module $X$,
	\[(c\cup-)\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+1}(G,\op{Hom}_\ZZ(X,I_G\otimes_\ZZ-))\]
	is a natural isomorphism for any $i\in\ZZ$.
\end{cor}
\begin{proof}
	Here, we are using the shifting pair $(\op{Hom}_\ZZ(X,-),\op{Hom}_\ZZ(X,I_G\otimes_\ZZ-),I_G,\eta)$, where
	\[\eta_A\colon I_G\otimes_\ZZ\op{Hom}_\ZZ(X,A)\to\op{Hom}_\ZZ(X,I_G\otimes_\ZZ A)\]
	is the canonical map sending $z\otimes f$ to $x\mapsto z\otimes f(x)$.

	Now, in light of \autoref{prop:dimshiftcupisos}, we merely have to find $c\in\widehat H^1(G,I_G)$ and show that we have a natural isomorphism at $i=0$. Because we already have a natural transformation by \autoref{lem:cuppingisnatural}, we are only worried about making the component morphisms
	\[\widehat H^0(G,\op{Hom}_\ZZ(X,A))\to\widehat H^1(G,\op{Hom}_\ZZ(X,I_G\otimes_\ZZ A))\]
	isomorphisms for all $G$-modules $A$. Well, we note that we have the $\ZZ$-split short exact sequence
	\[0\to\op{Hom}_\ZZ(X,I_G\otimes_\ZZ A)\to\op{Hom}_\ZZ(X,\ZZ[G]\otimes_\ZZ A)\to\op{Hom}_\ZZ(X,I_G\otimes_\ZZ A)\to0\]
	which will induce a $\delta$ morphism between the correct modules. In fact, because $\op{Hom}_\ZZ(X,-)$ is a shiftable functor, the middle term here is induced, so the $\delta$ morphism
	\[\delta\colon\widehat H^0(G,\op{Hom}_\ZZ(X,A))\to\widehat H^1(G,\op{Hom}_\ZZ(X,I_G\otimes_\ZZ A))\]
	is an isomorphism.

	To finish, we claim that this $\delta$ morphism arises as a cup product. We simply show this by hand by tracking through the $\delta$ morphism. Given $[f]\in\widehat H^0(G,\op{Hom}_\ZZ(X,A))$ where $f\colon X\to A$ is a $G$-module homomorphism, we can pull this back to the $0$-chain $\widetilde f\colon X\to\ZZ[G]\otimes_\ZZ A$ defined by
	\[\widetilde f\colon x\mapsto 1\otimes f(x).\]
	Applying the differential, we get the $1$-cocycle $d\widetilde f\in B^1(G,\op{Hom}_\ZZ(X,\ZZ[G]\otimes_\ZZ A))$ defined by
	\begin{align*}
		(d\widetilde f)(g)(x) &= (g\widetilde f)(x)-\widetilde f(x) \\
		&= g\cdot\widetilde f\left(g^{-1}x\right)-\widetilde f(x) \\
		&= g\left(1\otimes f(g^{-1}x)\right)-(1\otimes f(x)) \\
		&= (g-1)\otimes f(x),
	\end{align*}
	which we know must be a $1$-cocycle representing $\delta([f])\in H^1(G,\op{Hom}_\ZZ(X,I_G\otimes_\ZZ A))$.

	Thus, we see that we should set $c\in\widehat H^1(G,I_G)$ to be represented by $g\mapsto(g-1)$. This will work as long as $g\mapsto(g-1)$ is actually $1$-cocycle in $\widehat H^1(G,I_G)$. Well, take $X=A=\ZZ$ and $f=\id_\ZZ$ in the above argument so that $\delta(f)$ is exactly $g\mapsto(x\mapsto(g-1)\otimes x)$, which is $g\mapsto(g-1)$ after applying $\op{Hom}_\ZZ(\ZZ,I_G)\simeq I_G$.
\end{proof}
\begin{cor} \label{cor:cupdown}
	Let $G$ be a finite group. There exists $c\in\widehat H^1(G,I_G)$ such that, for any $G$-module $X$,
	\[(c\cup-)\colon\widehat H^i(G,\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,-)))\Rightarrow\widehat H^{i+1}(G,\op{Hom}_\ZZ(X,-))\]
	is a natural isomorphism for any $i\in\ZZ$.
\end{cor}
\begin{proof}
	Similar to before, we are using the shifting pair $(\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,-)),\op{Hom}_\ZZ(X,-),I_G,\eta)$, where
	\[\eta_A\colon I_G\otimes_\ZZ\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A))\Rightarrow\op{Hom}_\ZZ(X,-)\]
	is the canonical map sending $z\otimes f$ to $x\mapsto f(x)(z)$.

	Using \autoref{prop:dimshiftcupisos} and \autoref{lem:cuppingisnatural} again, it will suffice to find $c\in\widehat H^1(G,I_G)$ such that we have isomorphisms
	\[(c\cup-)\colon\widehat H^0(G,\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A)))\to\widehat H^1(G,\op{Hom}_\ZZ(X,A))\]
	for all $G$-modules $A$. This time around we use the $\ZZ$-split short exact sequence
	\[0\to\op{Hom}_\ZZ(X,A)\to\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(\ZZ[G],A))\to\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A))\to0\]
	which will induce a boundary morphism
	\[\delta\colon\widehat H^0(G,\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A)))\to\widehat H^1(G,\op{Hom}_\ZZ(X,A)).\]
	In fact, $\delta$ is an isomorphism because our middle term $\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(\ZZ[G],A))$ is induced.

	We now show that $\delta$ is a cup product by hand. Pick up some $[f]\in\widehat H^0(G,\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A)))$ where $f\colon X\to\op{Hom}_\ZZ(I_G,A)$ is a $G$-module homomorphism. This pulls back to the $0$-cochain
	\[\widetilde f\colon x\mapsto\big(z\mapsto f(x)(z-\varepsilon(z))\big).\]
	Applying the differential, we compute
	\begin{align*}
		(d\widetilde f)(g)(x)(z) &= (g\widetilde f-\widetilde f)(x)(z) \\
		&= (g\widetilde f)(x)(z)-\widetilde f(x)(z) \\
		&= \left(g\cdot\widetilde f\left(g^{-1}x\right)\right)(z)-\widetilde f(x)(z) \\
		&= g\cdot\widetilde f\left(g^{-1}x\right)\left(g^{-1}z\right)-\widetilde f(x)(z) \\
		&= g\cdot f\left(g^{-1}x\right)\left(g^{-1}z-\varepsilon(z)\right)-f(x)(z-\varepsilon(z)) \\
		&= g\cdot \left(g^{-1}f\left(x\right)\right)\left(g^{-1}z-\varepsilon(z)\right)-f(x)(z-\varepsilon(z)) \\
		&= f(x)\left(z-g\varepsilon(z)\right)-f(x)(z-\varepsilon(z)) \\
		&= \varepsilon(z)f(x)\left(1-g\right).
	\end{align*}
	Thus, this pulls back to the $1$-cocycle $g\mapsto(x\mapsto f(x)(1-g))$ in $\widehat H^1(G,\op{Hom}_\ZZ(X,A))$.
	
	In particular, we see that we should take $c$ represented by $g\mapsto(1-g)$, which will work as soon as we know that $g\mapsto(1-g)$ is a $1$-cocycle. Well, this is the negation of the $1$-cocycle $g\mapsto(g-1)$ found in \autoref{cor:cupup}. We close by remarking that we can actually take $c$ represented by $g\mapsto(g-1)$ because negating $c$ does not change the fact that the cup product gives an isomorphism.
\end{proof}
\begin{remark}
	Essentially the same proofs for \autoref{cor:cupup} and \autoref{cor:cupdown} will work when $\op{Hom}_\ZZ(X,-)$ is replaced by $X\otimes_\ZZ-$, or any composite of these. There isn't an analogue for arbitrary shiftable functors because, for example, there is no way obvious way to construct $\eta$ in general. Regardless, we will not need to work in these levels of generality.
\end{remark}
The point of \autoref{cor:cupup} and \autoref{cor:cupdown} is that have a somewhat general version of dimension-shifting granted by cup products. In fact, we see that we can use the same $c\in\widehat H^1(G,I_G)$ represented by $g\mapsto(g-1)$ for both shifting isomorphisms.

\subsection{Shifting Natural Transformations}
Observe that a natural transformation $F\Rightarrow F'$ of shiftable functors will induce natural transformations in cohomology
\[\widehat H^i(G,F-)\Rightarrow\widehat H^i(G,F'-)\]
It will turn out that, when $F=\op{Hom}_\ZZ(X,-)$ and $F'=\op{Hom}_\ZZ(X',-)$, we will be able to force all natural transformations in cohomology will come from natural transformations $F\Rightarrow F'$.

To begin, we show this result for $i=0$.
\begin{lemma} \label{lem:naturaltransiscupping}
	Let $G$ be a finite group, and let $X$ and $X'$ be $G$-modules. Suppose that, for given index $r\in\ZZ$, there is a natural transformation
	\[\Phi_\bullet\colon\widehat H^0(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^r(G,\op{Hom}_\ZZ(X',-)).\]
	Then there exists $[x]\in\widehat H^r(G,\op{Hom}_\ZZ(X',X))$ such that $\Phi_\bullet=([x]\cup-)$, where the cup product is induced by the shifting pair of \autoref{ex:shiftingpair}.
	% Then there exists a $G$-module homomorphism $\varphi\colon X'\to X$ such that $\Phi_A([f])=(-\circ\varphi)([f])$ for any $f\in\op{Hom}_{\ZZ[G]}(X,A)$.
\end{lemma}
\begin{proof}
	This is essentially the Yoneda lemma. As such, set $[x]\coloneqq\Phi_X([\id_X])$. The point is to fix some $G$-module $A$ and $[\overline f]\in\widehat H^0(G,\op{Hom}_\ZZ(X,A))$ in order to track through the commutativity of the following diagram.
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF4wKEcsXFxvcHtIb219X1xcWlooWCxYKSkiXSxbMSwwLCJcXHdpZGVoYXQgSF4wKEcsXFxvcHtIb219X1xcWlooWCcsWCkpIl0sWzAsMSwiXFx3aWRlaGF0IEheMChHLFxcb3B7SG9tfV9cXFpaKFgsQSkpIl0sWzEsMSwiXFx3aWRlaGF0IEheMChHLFxcb3B7SG9tfV9cXFpaKFgnLEEpKSJdLFswLDEsIlxcUGhpX1giXSxbMCwyLCJmIiwyXSxbMSwzLCJmIiwyXSxbMiwzLCJcXFBoaV9BIl1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\begin{equation}
		\begin{tikzcd}
			{\widehat H^0(G,\op{Hom}_\ZZ(X,X))} & {\widehat H^r(G,\op{Hom}_\ZZ(X',X))} \\
			{\widehat H^0(G,\op{Hom}_\ZZ(X,A))} & {\widehat H^r(G,\op{Hom}_\ZZ(X',A))}
			\arrow["{\Phi_X}", from=1-1, to=1-2]
			\arrow["\overline f"', from=1-1, to=2-1]
			\arrow["\overline f"', from=1-2, to=2-2]
			\arrow["{\Phi_A}", from=2-1, to=2-2]
		\end{tikzcd} \label{eq:cohomologicalyoneda}
	\end{equation}
	Because we will need to deal with the cup products with negative indices, we will use the standard resolution of \cite{atiyah-wall}. For example, we interpret $f\in[\overline f]\in\widehat H^0(G,\op{Hom}_\ZZ(X,A))$ as a constant function $f\in\op{Hom}_{\ZZ[G]}(\ZZ[G],\op{Hom}_\ZZ(X,A))$ outputting $\overline f\in\op{Hom}_{\ZZ[G]}(X,A)$, which means that $f(z)$ is the same $G$-module homomorphism for each $z\in\ZZ[G]$.

	As such, we can track the left arrow of \autoref{eq:cohomologicalyoneda} as
	\[\arraycolsep=1.4pt\begin{array}{cccc}
		\overline f\colon& \widehat H^0(G,\op{Hom}_\ZZ(X,X)) &\to& \widehat H^0(G,\op{Hom}_\ZZ(X,A)) \\
		& {[z\mapsto\id_X]} &\mapsto& {[z\mapsto f(z)\circ\id_X]=[\overline f]}.
	\end{array}\]
	So, along the bottom of \autoref{eq:cohomologicalyoneda}, we are evaluating $\Phi_A([\overline f])$.

	Along the top of \autoref{eq:cohomologicalyoneda}, we immediately send $[z\mapsto\id_X]$ to $\Phi_X([z\mapsto\id_X])=[x]$, so to finish the proof, we need to show that
	\[\overline f([x])\stackrel?=[x]\cup[\overline f],\]
	which will be enough by the commutativity of \autoref{eq:cohomologicalyoneda}. We have two similar cases to appropriately deal with the cup product.
	\begin{itemize}
		\item Suppose that $r\ge0$ so that we can interpret $x$ as an element of $\op{Hom}_{\ZZ[G]}\left(\ZZ[G^{r+1}],X\right)$, using the standard resolution. As such, we compute
		\[(x\cup f)(g_0,\ldots,g_p) = x(g_0,\ldots,g_p) \otimes f(g_r),\]
		where our output is in $\op{Hom}_\ZZ(X',X)\otimes_\ZZ\op{Hom}_\ZZ(X,A)$. Applying evaluation, the cup product is outputting
		\[(g_0,\ldots,g_r)\mapsto\overline f\circ x(g_0,\ldots,g_r)\]
		as our element of $\op{Hom}_{\ZZ[G]}(\ZZ[G^{r+1}],\op{Hom}_\ZZ(X',A))$. Indeed, this morphism represents $\overline f([x])$.
		\item Analogously, suppose that $r<0$ so that we interpret $x$ as an element of $\op{Hom}_{\ZZ[G]}\left(\op{Hom}_\ZZ(\ZZ[G]^r,\ZZ),X\right)$. To decrease headaches, we let $g^*\colon\ZZ[G]\to\ZZ$ denote the $G$-module homomorphism sending $g\mapsto1$ and other group elements to $0$. Then $r$-tuples $(g_1^*,\ldots,g_r^*)$ form a $\ZZ$-basis of $\op{Hom}_\ZZ(\ZZ[G]^r,\ZZ)$, so it's enough to specify
		\[(x\cup f)(g_1^*,\ldots,g_r^*) = x(g_1^*,\ldots,g_r^*)\otimes f(g_r),\]
		where the output is in $\op{Hom}_\ZZ(X',X)\otimes_\ZZ\op{Hom}_\ZZ(X,A)$. Applying evaluation, the cup product is outputting
		\[(g_1^*,\ldots,g_r^*)\mapsto\overline f\circ x(g_1^*,\ldots,g_r^*)\]
		as an element of $\op{Hom}_{\ZZ[G]}\left(\op{Hom}_\ZZ(\ZZ[G]^r,\ZZ),\op{Hom}_\ZZ(X',A)\right)$. Indeed, this represents $\overline f([x])$.
	\end{itemize}
	The above cases finish tracking through \autoref{eq:cohomologicalyoneda} and hence finish the proof.
	% This is essentially the Yoneda lemma. Choose $\varphi\colon X'\to X$ to represent $[\varphi]=\Phi_X([\id_X])$. Then tracking through the commutativity of
	% % https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF4wKEcsXFxvcHtIb219X1xcWlooWCxYKSkiXSxbMSwwLCJcXHdpZGVoYXQgSF4wKEcsXFxvcHtIb219X1xcWlooWCcsWCkpIl0sWzAsMSwiXFx3aWRlaGF0IEheMChHLFxcb3B7SG9tfV9cXFpaKFgsQSkpIl0sWzEsMSwiXFx3aWRlaGF0IEheMChHLFxcb3B7SG9tfV9cXFpaKFgnLEEpKSJdLFswLDEsIlxcUGhpX1giXSxbMCwyLCJmIiwyXSxbMSwzLCJmIiwyXSxbMiwzLCJcXFBoaV9BIl1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% \[\begin{tikzcd}
	% 	{\widehat H^0(G,\op{Hom}_\ZZ(X,X))} & {\widehat H^0(G,\op{Hom}_\ZZ(X',X))} \\
	% 	{\widehat H^0(G,\op{Hom}_\ZZ(X,A))} & {\widehat H^0(G,\op{Hom}_\ZZ(X',A))}
	% 	\arrow["{\Phi_X}", from=1-1, to=1-2]
	% 	\arrow["f"', from=1-1, to=2-1]
	% 	\arrow["f"', from=1-2, to=2-2]
	% 	\arrow["{\Phi_A}", from=2-1, to=2-2]
	% \end{tikzcd}\]
	% reveals that
	% % https://q.uiver.app/?q=WzAsNCxbMCwwLCJbXFxpZF9YXSJdLFsxLDAsIltcXHZhcnBoaV0iXSxbMCwxLCJbZl0iXSxbMSwxLCJcXFBoaV9BKFtmXSk9W2ZcXGNpcmNcXHZhcnBoaV0iXSxbMCwxLCJcXFBoaV9YIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFswLDIsImYiLDIseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzEsMywiZiIsMix7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbMiwzLCJcXFBoaV9BIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% \[\begin{tikzcd}
	% 	{[\id_X]} & {[\varphi]} \\
	% 	{[f]} & {\Phi_A([f])=[f\circ\varphi]}
	% 	\arrow["{\Phi_X}", maps to, from=1-1, to=1-2]
	% 	\arrow["f"', maps to, from=1-1, to=2-1]
	% 	\arrow["f"', maps to, from=1-2, to=2-2]
	% 	\arrow["{\Phi_A}", maps to, from=2-1, to=2-2]
	% \end{tikzcd}\]
	% after plugging in. To finish, we note that $\varphi([f])=[f\circ\varphi]$ under the induced map $\varphi\colon\op{Hom}_\ZZ(X,A)\to\op{Hom}_\ZZ(X',A)$. This finishes.
\end{proof}
The case of $r=0$ will be particularly interesting to us, so we note that we have the following more concrete description.
\begin{lemma} \label{lem:cupiscomp}
	Let $G$ be a finite group, and let $X$ and $X'$ be $G$-modules. Then, given a $G$-module morphism $\varphi\colon X'\to X$, the maps $(-\circ\varphi)$ and $([\varphi]\cup-)$ on
	\[\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^i(G,\op{Hom}_\ZZ(X',-))\]
	assemble into the same natural transformation for any $i\in\ZZ$.
\end{lemma}
\begin{proof}
	This follows from unpacking the definitions.
	
	We already know that $([\varphi]\cup-)$ is a natural transformation by \autoref{lem:cuppingisnatural}, so it suffices to show that the two maps agree on components. (Namely, naturality of $(-\circ\varphi)$ will immediately follow.) To see this, we fix a $G$-module $A$ to evaluate the morphism
	\[\widehat H^i(G,\op{Hom}_\ZZ(X,A))\to\widehat H^i(G,\op{Hom}_\ZZ(X',A)),\]
	for which we use the standard resolution of \cite{atiyah-wall}. For this, we represent $[\varphi]$ by the morphism $\widetilde\varphi\in\op{Hom}_{\ZZ[G]}(\ZZ[G],\op{Hom}_{\ZZ}(X,A))$ which constantly outputs $\varphi$.
	
	Now, pick up $[x]\in\widehat H^i(G,\op{Hom}_\ZZ(X,A))$. We have two cases.
	\begin{itemize}
		\item If $i\ge0$, we can interpret $x$ as an element of $\op{Hom}_{\ZZ[G]}\left(\ZZ[G]^{i+1},\op{Hom}_\ZZ(X,A)\right)$. Then our cup product is
		\[(\widetilde\varphi\cup x)(g_0,\ldots,g_i)=\widetilde\varphi(x_0)\otimes x(g_0,\ldots,g_i),\]
		which evaluates to
		\[(g_0,\ldots,g_i)\mapsto x(g_0,\ldots,g_i)\circ\varphi,\]
		which represents the desired class $(-\circ\varphi)([x])$.
		\item If $i<0$, we can interpret $x$ as an element of $\op{Hom}_{\ZZ[G]}\left(\op{Hom}_\ZZ(\ZZ[G]^i,\ZZ),\op{Hom}_\ZZ(X,A)\right)$. Our cup product is
		\[(\widetilde\varphi\cup x)(g_1^*,\ldots,g_i^*)=\widetilde\varphi(g_1)\otimes x(g_1^*,\ldots,g_i^*),\]
		which evaluates to
		\[(g_1^*,\ldots,g_i^*)\mapsto x(g_1^*,\ldots,g_i^*)\circ\varphi,\]
		which represents the desired class $(-\circ\varphi)([x])$.
	\end{itemize}
	The above cases finish the proof.
\end{proof}
We now get the main result by dimension-shifting.
\begin{prop} \label{prop:allnaturaltransarecups}
	Let $G$ be a finite group, and let $X$ and $X'$ be $G$-modules. Then, given indices $r,s\in\ZZ$, any natural transformation
	\[\Phi_\bullet^{(s)}\colon\widehat H^s(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{r+s}(G,\op{Hom}_\ZZ(X',-)),\]
	is $\Phi_\bullet^{(s)}=(x\cup-)$ for some $x\in\widehat H^r(G,\op{Hom}_\ZZ(X',X))$.
	% are natural transformations (respectively, isomorphisms)
	% \[\Phi_\bullet^{(i)}\colon\widehat H^i(G,F-)\Rightarrow\widehat H^i(G,F'-),\]
	% for all $i\in\ZZ$.
\end{prop}
% \begin{proof}
% 	This argument is by dimension-shifting the $p$ upwards and downwards. Namely, we show the conclusion of the statement by induction on $i$; for $i=p$, there is nothing to say. We will show how to induct downwards to $i\le p$ in detail, and inducting upwards is similar.

% 	To induct downwards, suppose the statement is true for $i+1$, and we show $i$, so fix a natural transformation
% 	\[\Phi_\bullet^{(i+1)}\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^i(G,\op{Hom}_\ZZ(X',-)),\]
% 	which we would like to know arises as a cup product. The main idea is to use $\Phi_\bullet^{(i+1)}$ in order to construct $\Phi_\bullet^{(i)}$. Well, for any $G$-module $A$, we note that the two $\ZZ$-split short exact sequences
% 	\begin{equation}
% 		\arraycolsep=1.4pt\begin{array}{ccccccccc}
% 			1 &\to& F(I_G\otimes_\ZZ A) &\to& F(\ZZ[G]\otimes_\ZZ A) &\to& FA &\to& 1 \\
% 			1 &\to& F'(I_G\otimes_\ZZ A) &\to& F'(\ZZ[G]\otimes_\ZZ A) &\to& F'A &\to& 1
% 		\end{array} \label{eq:usualhomshiftingses}
% 	\end{equation}
% 	induce $\delta$ morphisms
% 	\[\arraycolsep=1.4pt\begin{array}{ccccccccc}
% 		\delta_{tA}\colon& \widehat H^i(G,FA) &\to& \widehat H^{i+1}(G,F'(I_G\otimes_\ZZ A)) \\
% 		\delta_{tA}'\colon& \widehat H^i(G,F'A) &\to& \widehat H^{i+1}(G,F'(I_G\otimes_\ZZ A))
% 	\end{array}\]
% 	which are in fact isomorphisms because the modules $\op{Hom}_\ZZ(X,\ZZ[G]\otimes_\ZZ A)$ and $\op{Hom}_\ZZ(X,\ZZ[G]\otimes_\ZZ A)$ are induced by \autoref{lem:hompreservesinduced}. As such, we have the diagram
% 	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF5pKEcsXFxvcHtIb219X1xcWlooWCxBKSkiXSxbMSwwLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBBKSkiXSxbMCwxLCJcXHdpZGVoYXQgSF5pKEcsXFxvcHtIb219X1xcWlooWCcsQSkpIl0sWzEsMSwiXFx3aWRlaGF0IEhee2krMX0oRyxcXG9we0hvbX1fXFxaWihYJyxJX0dcXG90aW1lc19cXFpaIEEpKSJdLFswLDEsIlxcZGVsdGFfWCJdLFsxLDMsIlxcUGhpXnsoaSsxKX1fe0lfR1xcb3RpbWVzX1xcWlogQX0iXSxbMiwzLCJcXGRlbHRhX3tYJ30iXSxbMCwyLCIiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
% 	\[\begin{tikzcd}
% 		{\widehat H^i(G,FA)} & {\widehat H^{i+1}(G,F(I_G\otimes_\ZZ A))} \\
% 		{\widehat H^i(G,F'A)} & {\widehat H^{i+1}(G,F'(I_G\otimes_\ZZ A))}
% 		\arrow["{\delta_{tA}}", from=1-1, to=1-2]
% 		\arrow["{\Phi^{(i+1)}_{I_G\otimes_\ZZ A}}", from=1-2, to=2-2]
% 		\arrow["{\delta_{tA}'}", from=2-1, to=2-2]
% 		\arrow[dashed, from=1-1, to=2-1]
% 	\end{tikzcd}\]
% 	where the horizontal arrows are isomorphisms. Thus, we induce a morphism
% 	\[\Phi_A^{(i)}\coloneqq(\delta_{tA}')^{-1}\circ\Phi^{(i+1)}_{I_G\otimes_\ZZ A}\circ\delta_{tA}.\]
% 	We claim that $\Phi_\bullet^{(i)}$ assembles into a natural transformation $\widehat H^i(G,F-)\Rightarrow\widehat H^i(G,F'-)$. For this, we must check naturality. Suppose that we have a morphism $f\colon A\to B$. This gives rise to the following diagram. 
% 	% https://q.uiver.app/?q=WzAsOCxbMSwwLCJcXHdpZGVoYXQgSF5pKEcsXFxvcHtIb219X1xcWlooWCxBKSkiXSxbMywwLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBBKSkiXSxbMywyLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgnLElfR1xcb3RpbWVzX1xcWlogQSkpIl0sWzEsMiwiXFx3aWRlaGF0IEheaShHLFxcb3B7SG9tfV9cXFpaKFgnLEEpKSJdLFswLDEsIlxcd2lkZWhhdCBIXmkoRyxcXG9we0hvbX1fXFxaWihYLEIpKSJdLFsyLDEsIlxcd2lkZWhhdCBIXntpKzF9KEcsXFxvcHtIb219X1xcWlooWCxJX0dcXG90aW1lc19cXFpaIEIpKSJdLFswLDMsIlxcd2lkZWhhdCBIXmkoRyxcXG9we0hvbX1fXFxaWihYJyxCKSkiXSxbMiwzLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgnLElfR1xcb3RpbWVzX1xcWlogQikpIl0sWzAsMSwiXFxkZWx0YV97aEF9IiwwLHsibGFiZWxfcG9zaXRpb24iOjIwfV0sWzMsMiwiXFxkZWx0YV97aEF9JyIsMCx7ImxhYmVsX3Bvc2l0aW9uIjoyMH1dLFs0LDUsIlxcZGVsdGFfe2hCfSIsMSx7ImxhYmVsX3Bvc2l0aW9uIjoyMH1dLFs2LDcsIlxcZGVsdGFfe2hCfSciLDAseyJsYWJlbF9wb3NpdGlvbiI6MjB9XSxbMCwzLCJcXFBoaV9BXnsoaSl9IiwxLHsibGFiZWxfcG9zaXRpb24iOjIwLCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbNCw2LCJcXFBoaV9CXnsoaSl9IiwxLHsibGFiZWxfcG9zaXRpb24iOjIwLCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMCw0LCJmIiwxXSxbMSw1LCJmIiwxXSxbMiw3LCJmIiwxXSxbNSw3LCJcXFBoaV9CXnsoaSsxKX0iLDEseyJsYWJlbF9wb3NpdGlvbiI6MjB9XSxbMSwyLCJcXFBoaV9BXnsoaSsxKX0iLDEseyJsYWJlbF9wb3NpdGlvbiI6MjB9XSxbMyw2LCJmIiwxXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
% 	\[\begin{tikzcd}[column sep={3cm,between origins}]
% 		& {\widehat H^i(G,FA)} && {\widehat H^{i+1}(G,F(I_G\otimes_\ZZ A))} \\
% 		{\widehat H^i(G,FB)} && {\widehat H^{i+1}(G,F(I_G\otimes_\ZZ B))} \\
% 		& {\widehat H^i(G,F'A)} && {\widehat H^{i+1}(G,F'(I_G\otimes_\ZZ A))} \\
% 		{\widehat H^i(G,F'B)} && {\widehat H^{i+1}(G,F'(I_G\otimes_\ZZ B))}
% 		\arrow["{\delta_{tA}}"{description, pos=0.2}, from=1-2, to=1-4]
% 		\arrow["{\delta_{tA}'}"{description, pos=0.2}, from=3-2, to=3-4]
% 		\arrow["{\delta_{tB}}"{description, pos=0.2}, from=2-1, to=2-3]
% 		\arrow["{\delta_{tB}'}"{description, pos=0.2}, from=4-1, to=4-3]
% 		\arrow["{\Phi_A^{(i)}}"{description, pos=0.2}, dashed, from=1-2, to=3-2]
% 		\arrow["{\Phi_B^{(i)}}"{description, pos=0.2}, dashed, from=2-1, to=4-1]
% 		\arrow["Ff"{description}, from=1-2, to=2-1]
% 		\arrow["Ff"{description}, from=1-4, to=2-3]
% 		\arrow["F'f"{description}, from=3-4, to=4-3]
% 		\arrow["{\Phi_{I_G\otimes_\ZZ B}^{(i+1)}}"{description, pos=0.2}, from=2-3, to=4-3]
% 		\arrow["{\Phi_{I_G\otimes_\ZZ A}^{(i+1)}}"{description, pos=0.2}, from=1-4, to=3-4]
% 		\arrow["F'f"{description}, from=3-2, to=4-1]
% 	\end{tikzcd}\]
% 	We want to show that the left face commutes. For this, we note that all the horizontal arrows are isomorphisms (they're the $\delta$s from before), so it suffices to show that the rest of the cube commutes.
% 	\begin{itemize}
% 		\item The top face commutes by functoriality of $\delta$ morphsims applied to the following morphism of short exact sequences.
% 		% https://q.uiver.app/?q=WzAsMTAsWzAsMCwiMCJdLFsxLDAsIlxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBBKSJdLFsyLDAsIlxcb3B7SG9tfV9cXFpaKFgsXFxaWltHXVxcb3RpbWVzX1xcWlogQSkiXSxbMywwLCJcXG9we0hvbX1fXFxaWihYLEEpIl0sWzQsMCwiMCJdLFsxLDEsIlxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBCKSJdLFsyLDEsIlxcb3B7SG9tfV9cXFpaKFgsXFxaWltHXVxcb3RpbWVzX1xcWlogQikiXSxbMywxLCJcXG9we0hvbX1fXFxaWihYLEIpIl0sWzQsMSwiMCJdLFswLDEsIjAiXSxbMCwxXSxbOSw1XSxbMSwyXSxbMiwzXSxbMyw0XSxbNSw2XSxbNiw3XSxbNyw4XSxbMSw1LCJmIl0sWzIsNiwiZiJdLFszLDcsImYiXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
% 		\[\begin{tikzcd}
% 			0 & {F(I_G\otimes_\ZZ A)} & {F(\ZZ[G]\otimes_\ZZ A)} & {FA} & 0 \\
% 			0 & {F(I_G\otimes_\ZZ B)} & {F(\ZZ[G]\otimes_\ZZ B)} & {FB} & 0
% 			\arrow[from=1-1, to=1-2]
% 			\arrow[from=2-1, to=2-2]
% 			\arrow[from=1-2, to=1-3]
% 			\arrow[from=1-3, to=1-4]
% 			\arrow[from=1-4, to=1-5]
% 			\arrow[from=2-2, to=2-3]
% 			\arrow[from=2-3, to=2-4]
% 			\arrow[from=2-4, to=2-5]
% 			\arrow["Ff", from=1-2, to=2-2]
% 			\arrow["Ff", from=1-3, to=2-3]
% 			\arrow["Ff", from=1-4, to=2-4]
% 		\end{tikzcd}\]
% 		The bottom face commutes for the same reason, replacing $F$s with $F'$s in the above morphism of short exact sequences.
% 		\item The front and back faces commute by definition of the morphisms $\Phi_\bullet^{(i)}$.
% 		\item The right face commutes by naturality of $\Phi^{(i+1)}_\bullet$ applied to the induced morphism $f\colon I_G\otimes_\ZZ A\to I_G\otimes_\ZZ B$.
% 	\end{itemize}
% 	The above commutativity checks complete the proof that $\Phi_\bullet^{(i)}$ makes a natural transformation. To finish, we note that, if $\Phi_\bullet^{(i+1)}$ is a natural isomorphism, then $\Phi_\bullet^{(i)}$ is a natural isomorphism as well by its construction. This completes the induction downwards.

% 	We will not give detail for the induction upwards from $i-1$ to $i$, except to say that the short exact sequences \autoref{eq:usualhomshiftingses} are replaced with the following.
% 	\[\arraycolsep=1.4pt\begin{array}{ccccccccc}
% 		1 &\to& FA &\to& F(\op{Hom}_\ZZ(\ZZ[G],A)) &\to& F(\op{Hom}_\ZZ(I_G,A)) &\to& 1 \\
% 		1 &\to& F'A &\to& F'(\op{Hom}_\ZZ(\ZZ[G],A)) &\to& F'(\op{Hom}_\ZZ(I_G,A)) &\to& 1
% 	\end{array}\]
% 	The rest of the approach essentially goes through verbatim, constructing $\Phi_\bullet^{(i)}$ from a given $\Phi_\bullet^{(i-1)}$.
% \end{proof}
\begin{proof}
	This argument is by dimension-shifting the $s$ upwards and downwards. Namely, we show the conclusion of the statement by induction on $s$; for $s=0$, this is \autoref{lem:naturaltransiscupping}. We will show how to induct upwards to $s\ge0$ in detail, and inducting downwards is similar. For brevity, we set $F\coloneqq\op{Hom}_\ZZ(X,-)$ and $F'\coloneqq\op{Hom}_\ZZ(X',-)$.

	To induct upwards, suppose the statement is true for $s=i$, and we show $s=i+1$, so fix a natural transformation
	\[\Phi_\bullet^{(i+1)}\colon\widehat H^{i+1}(G,F-)\Rightarrow\widehat H^{p+i+1}(G,F'-),\]
	which we would like to know arises as $(x\cup-)$ for some $x\in\widehat H^p(G,\op{Hom}_\ZZ(X',X))$. The main idea is to use $\Phi_\bullet^{(i+1)}$ in order to construct $\Phi_\bullet^{(i)}$. Well, using \autoref{cor:cupup}, we have some $c\in\widehat H^1(G,I_G)$ given by $g\mapsto(g-1)$ yielding the following isomorphisms for any $G$-module $A$.
	% Well, for any $G$-module $A$, we note that the two $\ZZ$-split short exact sequences
	% \begin{equation}
	% 	\arraycolsep=1.4pt\begin{array}{ccccccccc}
	% 		1 &\to& F(I_G\otimes_\ZZ A) &\to& F(\ZZ[G]\otimes_\ZZ A) &\to& FA &\to& 1 \\
	% 		1 &\to& F'(I_G\otimes_\ZZ A) &\to& F'(\ZZ[G]\otimes_\ZZ A) &\to& F'A &\to& 1
	% 	\end{array} \label{eq:usualhomshiftingses}
	% \end{equation}
	% induce $\delta$ morphisms
	\[\arraycolsep=1.4pt\begin{array}{ccccccccc}
		(c\cup-)_d\colon& \widehat H^i(G,FA) &\to& \widehat H^{i+1}(G,F(I_G\otimes_\ZZ A)) \\
		(c\cup-)'_d\colon& \widehat H^{r+i}(G,F'A) &\to& \widehat H^{r+i+1}(G,F'(I_G\otimes_\ZZ A))
	\end{array}\]
	As such, we have the diagram
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF5pKEcsXFxvcHtIb219X1xcWlooWCxBKSkiXSxbMSwwLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBBKSkiXSxbMCwxLCJcXHdpZGVoYXQgSF5pKEcsXFxvcHtIb219X1xcWlooWCcsQSkpIl0sWzEsMSwiXFx3aWRlaGF0IEhee2krMX0oRyxcXG9we0hvbX1fXFxaWihYJyxJX0dcXG90aW1lc19cXFpaIEEpKSJdLFswLDEsIlxcZGVsdGFfWCJdLFsxLDMsIlxcUGhpXnsoaSsxKX1fe0lfR1xcb3RpbWVzX1xcWlogQX0iXSxbMiwzLCJcXGRlbHRhX3tYJ30iXSxbMCwyLCIiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\widehat H^i(G,FA)} & {\widehat H^{i+1}(G,F(I_G\otimes_\ZZ A))} \\
		{\widehat H^{r+i}(G,F'A)} & {\widehat H^{r+i+1}(G,F'(I_G\otimes_\ZZ A))}
		\arrow["{(c\cup-)_d}", from=1-1, to=1-2]
		\arrow["{\Phi^{(i+1)}_{I_G\otimes_\ZZ A}}", from=1-2, to=2-2]
		\arrow["{(c\cup-)'_d}", from=2-1, to=2-2]
		\arrow[dashed, from=1-1, to=2-1]
	\end{tikzcd}\]
	where the horizontal arrows are isomorphisms. Thus, we induce a morphism
	\[\Phi_A^{(i)}\coloneqq((c\cup-)'_d)^{-1}\circ\Phi^{(i+1)}_{I_G\otimes_\ZZ A}\circ(c\cup-)_d.\]
	Note that $\Phi_\bullet^{(i)}$ is the composition of natural transformations (the cup product is a natural transformation by construction) and therefore is a natural transformation.
	% We claim that $\Phi_\bullet^{(i)}$ assembles into a natural transformation $\widehat H^i(G,F-)\Rightarrow\widehat H^i(G,F'-)$. For this, we must check naturality. Suppose that we have a morphism $f\colon A\to B$. This gives rise to the following diagram.
	% % https://q.uiver.app/?q=WzAsOCxbMSwwLCJcXHdpZGVoYXQgSF5pKEcsXFxvcHtIb219X1xcWlooWCxBKSkiXSxbMywwLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBBKSkiXSxbMywyLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgnLElfR1xcb3RpbWVzX1xcWlogQSkpIl0sWzEsMiwiXFx3aWRlaGF0IEheaShHLFxcb3B7SG9tfV9cXFpaKFgnLEEpKSJdLFswLDEsIlxcd2lkZWhhdCBIXmkoRyxcXG9we0hvbX1fXFxaWihYLEIpKSJdLFsyLDEsIlxcd2lkZWhhdCBIXntpKzF9KEcsXFxvcHtIb219X1xcWlooWCxJX0dcXG90aW1lc19cXFpaIEIpKSJdLFswLDMsIlxcd2lkZWhhdCBIXmkoRyxcXG9we0hvbX1fXFxaWihYJyxCKSkiXSxbMiwzLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgnLElfR1xcb3RpbWVzX1xcWlogQikpIl0sWzAsMSwiXFxkZWx0YV97aEF9IiwwLHsibGFiZWxfcG9zaXRpb24iOjIwfV0sWzMsMiwiXFxkZWx0YV97aEF9JyIsMCx7ImxhYmVsX3Bvc2l0aW9uIjoyMH1dLFs0LDUsIlxcZGVsdGFfe2hCfSIsMSx7ImxhYmVsX3Bvc2l0aW9uIjoyMH1dLFs2LDcsIlxcZGVsdGFfe2hCfSciLDAseyJsYWJlbF9wb3NpdGlvbiI6MjB9XSxbMCwzLCJcXFBoaV9BXnsoaSl9IiwxLHsibGFiZWxfcG9zaXRpb24iOjIwLCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbNCw2LCJcXFBoaV9CXnsoaSl9IiwxLHsibGFiZWxfcG9zaXRpb24iOjIwLCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMCw0LCJmIiwxXSxbMSw1LCJmIiwxXSxbMiw3LCJmIiwxXSxbNSw3LCJcXFBoaV9CXnsoaSsxKX0iLDEseyJsYWJlbF9wb3NpdGlvbiI6MjB9XSxbMSwyLCJcXFBoaV9BXnsoaSsxKX0iLDEseyJsYWJlbF9wb3NpdGlvbiI6MjB9XSxbMyw2LCJmIiwxXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% \[\begin{tikzcd}[column sep={3cm,between origins}]
	% 	& {\widehat H^i(G,FA)} && {\widehat H^{i+1}(G,F(I_G\otimes_\ZZ A))} \\
	% 	{\widehat H^i(G,FB)} && {\widehat H^{i+1}(G,F(I_G\otimes_\ZZ B))} \\
	% 	& {\widehat H^i(G,F'A)} && {\widehat H^{i+1}(G,F'(I_G\otimes_\ZZ A))} \\
	% 	{\widehat H^i(G,F'B)} && {\widehat H^{i+1}(G,F'(I_G\otimes_\ZZ B))}
	% 	\arrow["{\delta_{tA}}"{description, pos=0.2}, from=1-2, to=1-4]
	% 	\arrow["{\delta_{tA}'}"{description, pos=0.2}, from=3-2, to=3-4]
	% 	\arrow["{\delta_{tB}}"{description, pos=0.2}, from=2-1, to=2-3]
	% 	\arrow["{\delta_{tB}'}"{description, pos=0.2}, from=4-1, to=4-3]
	% 	\arrow["{\Phi_A^{(i)}}"{description, pos=0.2}, dashed, from=1-2, to=3-2]
	% 	\arrow["{\Phi_B^{(i)}}"{description, pos=0.2}, dashed, from=2-1, to=4-1]
	% 	\arrow["Ff"{description}, from=1-2, to=2-1]
	% 	\arrow["Ff"{description}, from=1-4, to=2-3]
	% 	\arrow["F'f"{description}, from=3-4, to=4-3]
	% 	\arrow["{\Phi_{I_G\otimes_\ZZ B}^{(i+1)}}"{description, pos=0.2}, from=2-3, to=4-3]
	% 	\arrow["{\Phi_{I_G\otimes_\ZZ A}^{(i+1)}}"{description, pos=0.2}, from=1-4, to=3-4]
	% 	\arrow["F'f"{description}, from=3-2, to=4-1]
	% \end{tikzcd}\]
	% We want to show that the left face commutes. For this, we note that all the horizontal arrows are isomorphisms (they're the $\delta$s from before), so it suffices to show that the rest of the cube commutes.
	% \begin{itemize}
	% 	\item The top face commutes by functoriality of $\delta$ morphsims applied to the following morphism of short exact sequences.
	% 	% https://q.uiver.app/?q=WzAsMTAsWzAsMCwiMCJdLFsxLDAsIlxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBBKSJdLFsyLDAsIlxcb3B7SG9tfV9cXFpaKFgsXFxaWltHXVxcb3RpbWVzX1xcWlogQSkiXSxbMywwLCJcXG9we0hvbX1fXFxaWihYLEEpIl0sWzQsMCwiMCJdLFsxLDEsIlxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBCKSJdLFsyLDEsIlxcb3B7SG9tfV9cXFpaKFgsXFxaWltHXVxcb3RpbWVzX1xcWlogQikiXSxbMywxLCJcXG9we0hvbX1fXFxaWihYLEIpIl0sWzQsMSwiMCJdLFswLDEsIjAiXSxbMCwxXSxbOSw1XSxbMSwyXSxbMiwzXSxbMyw0XSxbNSw2XSxbNiw3XSxbNyw4XSxbMSw1LCJmIl0sWzIsNiwiZiJdLFszLDcsImYiXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% 	\[\begin{tikzcd}
	% 		0 & {F(I_G\otimes_\ZZ A)} & {F(\ZZ[G]\otimes_\ZZ A)} & {FA} & 0 \\
	% 		0 & {F(I_G\otimes_\ZZ B)} & {F(\ZZ[G]\otimes_\ZZ B)} & {FB} & 0
	% 		\arrow[from=1-1, to=1-2]
	% 		\arrow[from=2-1, to=2-2]
	% 		\arrow[from=1-2, to=1-3]
	% 		\arrow[from=1-3, to=1-4]
	% 		\arrow[from=1-4, to=1-5]
	% 		\arrow[from=2-2, to=2-3]
	% 		\arrow[from=2-3, to=2-4]
	% 		\arrow[from=2-4, to=2-5]
	% 		\arrow["Ff", from=1-2, to=2-2]
	% 		\arrow["Ff", from=1-3, to=2-3]
	% 		\arrow["Ff", from=1-4, to=2-4]
	% 	\end{tikzcd}\]
	% 	The bottom face commutes for the same reason, replacing $F$s with $F'$s in the above morphism of short exact sequences.
	% 	\item The front and back faces commute by definition of the morphisms $\Phi_\bullet^{(i)}$.
	% 	\item The right face commutes by naturality of $\Phi^{(i+1)}_\bullet$ applied to the induced morphism $f\colon I_G\otimes_\ZZ A\to I_G\otimes_\ZZ B$.
	% \end{itemize}
	% The above commutativity checks complete the proof that $\Phi_\bullet^{(i)}$ makes a natural transformation. To finish, we note that, if $\Phi_\bullet^{(i+1)}$ is a natural isomorphism, then $\Phi_\bullet^{(i)}$ is a natural isomorphism as well by its construction. This completes the induction downwards.

	Thus, the inductive hypothesis now tells us that $\Phi_\bullet^{(i)}=(x\cup-)$ for some $x\in\widehat H^p(G,\op{Hom}_\ZZ(X',X))$. We now need to turn this around on $\Phi_\bullet^{(i+1)}$, which essentially means we need to shift back in the other direction. As such, we use \autoref{cor:cupdown} to give the following isomorphisms for any $G$-module $A$.
	\[\arraycolsep=1.4pt\begin{array}{ccccccccc}
		(c\cup-)_u\colon&\widehat H^i(G,F(\op{Hom}_\ZZ(I_G,A)))&\to&\widehat H^{i+1}(G,FA) \\
		(c\cup-)_u'\colon&\widehat H^{r+i}(G,F(\op{Hom}_\ZZ(I_G,A)))&\to&\widehat H^{r+i+1}(G,FA)
	\end{array}\]
	Now, to deal with $\Phi_\bullet^{(i+1)}$, we claim that associativity and commutativity of cup products implies $\left((-1)^ix\cup-\right)$ can be used to make the right arrow in the diagram
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF5pKEcsXFxvcHtIb219X1xcWlooWCxcXG9we0hvbX1fXFxaWihJX0csQSkpKSJdLFsxLDAsIlxcd2lkZWhhdCBIXntpKzF9KEcsXFxvcHtIb219X1xcWlooWCxBKSkiXSxbMCwxLCJcXHdpZGVoYXQgSF5pKEcsXFxvcHtIb219X1xcWlooWCcsXFxvcHtIb219X1xcWlooSV9HLEEpKSkiXSxbMSwxLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgnLEEpKSJdLFswLDEsIihjXFxjdXAtKV91Il0sWzIsMywiKGNcXGN1cC0pX3UnIl0sWzAsMiwiKFxcdmFycGhpXFxjaXJjLSkiLDJdLFsxLDMsIiIsMSx7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6ImRhc2hlZCJ9fX1dXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\begin{equation}
		\begin{tikzcd}
			{\widehat H^i(G,F(\op{Hom}_\ZZ(I_G,A)))} & {\widehat H^{i+1}(G,FA)} \\
			{\widehat H^{r+i}(G,F'(\op{Hom}_\ZZ(I_G,A)))} & {\widehat H^{r+i+1}(G,F'A)}
			\arrow["{(c\cup-)_u}", from=1-1, to=1-2]
			\arrow["{(c\cup-)_u'}", from=2-1, to=2-2]
			\arrow["{x\cup-}"', from=1-1, to=2-1]
			\arrow[dashed, from=1-2, to=2-2]
		\end{tikzcd} \label{eq:shiftingcupup}
	\end{equation}
	commute. Indeed, applying \autoref{lem:cupassoc} to the square
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJJX0dcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooWCxcXG9we0hvbX1fXFxaWihJX0csQSkpXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgnLFgpIl0sWzAsMSwiSV9HXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgnLFxcb3B7SG9tfV9cXFpaKElfRyxBKSkiXSxbMSwwLCJcXG9we0hvbX1fXFxaWihYLEEpXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgnLFgpIl0sWzEsMSwiXFxvcHtIb219X1xcWlooWCcsQSkiXSxbMCwyXSxbMiwzXSxbMCwxXSxbMSwzXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{I_G\otimes_\ZZ\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A))\otimes_\ZZ\op{Hom}_\ZZ(X',X)} & {\op{Hom}_\ZZ(X,A)\otimes_\ZZ\op{Hom}_\ZZ(X',X)} \\
		{I_G\otimes_\ZZ\op{Hom}_\ZZ(X',\op{Hom}_\ZZ(I_G,A))} & {\op{Hom}_\ZZ(X',A)}
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-2, to=2-2]
		\arrow[from=1-1, to=2-1]
		\arrow[from=2-1, to=2-2]
	\end{tikzcd}\]
	shows that any $a\in\widehat H^i(G,F(\op{Hom}_\ZZ(I_G,A)))$ has
	\[c\cup(x\cup a)=(-1)^{ir}c\cup(a\cup x)=(-1)^{ir}(c\cup a)\cup x=(-1)^{ir+i(r+1)}x\cup(c\cup a)=(-1)^ix\cup(c\cup a),\]
	which is what we wanted.
	
	Now, this right arrow of \autoref{eq:shiftingcupup} is unique because the horizontal arrows are isomorphisms, so we will be done if we can show that we can place $\Phi_A^{(i+1)}$ in the right arrow to also make the diagram commute as well. For this, we draw the following very large diagram.
	% https://q.uiver.app/?q=WzAsNixbMCwwLCJcXHdpZGVoYXQgSF5pKEcsRihcXG9we0hvbX1fXFxaWihJX0csQSkpKSJdLFsxLDEsIlxcd2lkZWhhdCBIXntpKzF9KEcsRihJX0dcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooSV9HLEEpKSkiXSxbMiwwLCJcXHdpZGVoYXQgSF57aSsxfShHLEZBKSJdLFswLDMsIlxcd2lkZWhhdCBIXmkoRyxGJyhcXG9we0hvbX1fXFxaWihJX0csQSkpKSJdLFsxLDQsIlxcd2lkZWhhdCBIXntpKzF9KEcsRicoSV9HXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKElfRyxBKSkpIl0sWzIsMywiXFx3aWRlaGF0IEhee2krMX0oRyxGJ0EpIl0sWzAsMiwiKGNcXGN1cC0pX3UiLDEseyJsYWJlbF9wb3NpdGlvbiI6MjB9XSxbMCwxLCIoY1xcY3VwLSlfZCIsMV0sWzEsMiwiZiIsMV0sWzAsMywiKC1cXGNpcmNcXHZhcnBoaSkiLDEseyJsYWJlbF9wb3NpdGlvbiI6MzB9XSxbMSw0LCJcXFBoaV57KGkrMSl9X3tJX0dcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooSV9HLEEpfSIsMSx7ImxhYmVsX3Bvc2l0aW9uIjozMH1dLFsyLDUsIlxcUGhpXnsoaSsxKX1fQSIsMSx7ImxhYmVsX3Bvc2l0aW9uIjozMH1dLFszLDUsIihjXFxjdXAtKV91JyIsMSx7ImxhYmVsX3Bvc2l0aW9uIjoyMH1dLFszLDQsIihjXFxjdXAtKV9kJyIsMV0sWzQsNSwiZiIsMV1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\widehat H^i(G,F(\op{Hom}_\ZZ(I_G,A)))} && {\widehat H^{i+1}(G,FA)} \\
		& {\widehat H^{i+1}(G,F(I_G\otimes_\ZZ\op{Hom}_\ZZ(I_G,A)))} \\
		\\
		{\widehat H^{r+i}(G,F'(\op{Hom}_\ZZ(I_G,A)))} && {\widehat H^{r+i+1}(G,F'A)} \\
		& {\widehat H^{r+i+1}(G,F'(I_G\otimes_\ZZ\op{Hom}_\ZZ(I_G,A)))}
		\arrow["{(c\cup-)_u}"{description, pos=0.2}, from=1-1, to=1-3]
		\arrow["{(c\cup-)_d}"{description}, from=1-1, to=2-2]
		\arrow["f"{description}, from=2-2, to=1-3]
		\arrow["{x\cup-}"{description, pos=0.3}, from=1-1, to=4-1]
		\arrow["{\Phi^{(i+1)}_{I_G\otimes_\ZZ\op{Hom}_\ZZ(I_G,A)}}"{description, pos=0.3}, from=2-2, to=5-2]
		\arrow["{\Phi^{(i+1)}_A}"{description, pos=0.3}, from=1-3, to=4-3]
		\arrow["{(c\cup-)_u'}"{description, pos=0.2}, from=4-1, to=4-3]
		\arrow["{(c\cup-)_d'}"{description}, from=4-1, to=5-2]
		\arrow["f"{description}, from=5-2, to=4-3]
	\end{tikzcd}\]
	Here, the $f$ maps are induced by the evaluation map
	\[f\colon I_G\otimes_\ZZ\op{Hom}_\ZZ(I_G,A)\to A.\]
	We want the outer rectangle to commute, for which it suffices to show that each parallelogram and the small top and bottom triangles to commute.
	\begin{itemize}
		\item The left parallelogram commutes by definition of $\Phi_A^{(i)}$.
		\item The right parallelogram commutes by naturality of $\Phi^{(i+1)}_\bullet$.
		\item Showing that the bottom triangle commutes will be analogous to showing that the top triangle commutes, so we will only show the top. Unwinding \autoref{cor:cupup} and \autoref{cor:cupdown}, we see that this triangle is actually induced by the following diagram.
		% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF5pKEcsRihcXG9we0hvbX1fXFxaWihJX0csQSkpKSJdLFsxLDAsIlxcd2lkZWhhdCBIXmkoRyxJX0dcXG90aW1lc19cXFpaIEYoXFxvcHtIb219X1xcWlooSV9HLEEpKSkiXSxbMSwxLCJcXHdpZGVoYXQgSF5pKEcsRihJX0dcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooSV9HLEEpKSkiXSxbMiwwLCJcXHdpZGVoYXQgSF5pKEcsRkEpIl0sWzAsMSwiY1xcY3VwLSJdLFsyLDMsImYiLDJdLFsxLDIsIlxcZXRhX2QiLDJdLFsxLDMsIlxcZXRhX3UiXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
		\[\begin{tikzcd}
			{\widehat H^i(G,F(\op{Hom}_\ZZ(I_G,A)))} & {\widehat H^{i+1}(G,I_G\otimes_\ZZ F(\op{Hom}_\ZZ(I_G,A)))} & {\widehat H^{i+1}(G,FA)} \\
			& {\widehat H^{i+1}(G,F(I_G\otimes_\ZZ\op{Hom}_\ZZ(I_G,A)))}
			\arrow["{c\cup-}", from=1-1, to=1-2]
			\arrow["f"', from=2-2, to=1-3]
			\arrow["{\eta_d}"', from=1-2, to=2-2]
			\arrow["{\eta_u}", from=1-2, to=1-3]
		\end{tikzcd}\]
		Here, $\eta_u\colon I_G\otimes_\ZZ\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A))\to\op{Hom}_\ZZ(X,A)$ behaves as
		\[\eta_u\colon z\otimes f\mapsto\big(x\mapsto f(x)(z)\big),\]
		and $\eta_d\colon I_G\otimes_\ZZ\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A))\to \op{Hom}_\ZZ(X,I_G\otimes_\ZZ\op{Hom}_\ZZ(I_G,A))$ behaves as
		\[\eta_d\colon z\otimes f\mapsto\big(x\mapsto z\otimes f(x)\big).\]
		Now, to check our commutativity, it suffices to show that the triangle
		% https://q.uiver.app/?q=WzAsMyxbMCwwLCJJX0dcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooWCxcXG9we0hvbX1fXFxaWihJX0csQSkpIl0sWzAsMSwiXFxvcHtIb219X1xcWlooWCxJX0dcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooSV9HLEEpKSJdLFsxLDAsIlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMSwyLCJmIiwyXSxbMCwxLCJcXGV0YV9kIiwyXSxbMCwyLCJcXGV0YV91Il1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
		\[\begin{tikzcd}
			{I_G\otimes_\ZZ\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A))} & {\op{Hom}_\ZZ(X,A)} \\
			{\op{Hom}_\ZZ(X,I_G\otimes_\ZZ\op{Hom}_\ZZ(I_G,A))}
			\arrow["f"', from=2-1, to=1-2]
			\arrow["{\eta_d}"', from=1-1, to=2-1]
			\arrow["{\eta_u}", from=1-1, to=1-2]
		\end{tikzcd}\]
		commutes. Well, we can simply track through the diagram as follows.
		% https://q.uiver.app/?q=WzAsMyxbMCwwLCJ6XFxvdGltZXMgZiJdLFswLDEsIlxcYmlnKHhcXG1hcHN0byB6XFxvdGltZXMgZih4KVxcYmlnKSJdLFsxLDAsIlxcYmlnKHhcXG1hcHN0byBmKHgpKHopXFxiaWcpIl0sWzAsMiwiIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFswLDEsIiIsMCx7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbMSwyLCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
		\[\begin{tikzcd}
			{z\otimes f} & {\big(x\mapsto f(x)(z)\big)} \\
			{\big(x\mapsto z\otimes f(x)\big)}
			\arrow[maps to, from=1-1, to=1-2]
			\arrow[maps to, from=1-1, to=2-1]
			\arrow[maps to, from=2-1, to=1-2]
		\end{tikzcd}\]
	\end{itemize}
	The above commutativity checks finish the induction upwards.

	We will not give detail for the induction downwards from $i-1$ to $i$, except to say that we reverse the applications of \autoref{cor:cupup} and \autoref{cor:cupdown}. The rest of the approach essentially goes through verbatim, constructing $\Phi_\bullet^{(i)}$ from a given $\Phi_\bullet^{(i-1)}$, applying the inducting hypothesis to $\Phi_\bullet^{(i)}$, and then finishing by shifting back to $\Phi_\bullet^{(i-1)}$.
\end{proof}
\begin{remark}
	Essentially the same proof can show that, for any pair of shiftable functors $F,F'\colon\mathrm{Mod}_G\to\mathrm{Mod}_G$, a natural transformation (respectively, isomorphism)
	\[\Phi_\bullet^{(i)}\colon\widehat H^i(G,F-)\Rightarrow\widehat H^i(G,F'-),\]
	at $i=r$ induces natural transformations (respectively, isomorphisms) at all $i\in\ZZ$. Instead of using \autoref{cor:cupup} and \autoref{cor:cupdown}, we must instead dimension-shifting using the usual short exact sequences.
\end{remark}
\begin{cor}
	Let $G$ be a finite group, and let $X$ and $X'$ be $G$-modules. Then, given indices $s\in\ZZ$, any natural transformation
	\[\Phi_\bullet^{(s)}\colon\widehat H^q(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{s}(G,\op{Hom}_\ZZ(X',-)),\]
	is $\Phi_\bullet^{(s)}=(-\circ\varphi)$ for some $G$-module morphism $\varphi\colon X'\to X$.
\end{cor}
\begin{proof}
	\autoref{prop:allnaturaltransarecups} tells us that the natural transformation takes the form $([\varphi]\cup-)$ for some $G$-module morphism $\varphi\colon X'\to X$. Then $([\varphi]\cup-)$ is simply $(-\circ\varphi)$ by \autoref{lem:cupiscomp}.
\end{proof}

\subsection{Cohomological Equivalence}
It might be the case that ``many'' different shiftable functors give the same cohomology groups. Because we are mostly interested in the case of $\op{Hom}_\ZZ(X,-)$, we now have the tools to talk fairly concretely about what this means. We have the following definition.
\begin{definition}
	Let $G$ be a finite group. We say that two $G$-modules $X,X'$ are \textit{cohomologically equivalent} if and only if there exist morphisms $[\varphi]\in\widehat H^0(G,\op{Hom}_\ZZ(X',X))$ and $[\varphi']\in\widehat H^0(G,\op{Hom}_\ZZ(X,X'))$ such that
	\[[\varphi\circ\varphi']=[\id_X]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X))\qquad\text{and}\qquad[\varphi'\circ\varphi]=[\id_{X'}]\in\widehat H^0(G,\op{Hom}_\ZZ(X',X')).\]
\end{definition}
\begin{example} \label{ex:inducediszero}
	All induced modules $X$ are cohomologically equivalent to $0$. To see this, we set $\varphi\colon 0\to X$ and $\varphi'\colon X\to0$ equal to the zero maps (which are our only options). Then note that $\op{Hom}_\ZZ(X,X)$ is induced by \autoref{lem:hompreservesinduced} and $\op{Hom}_\ZZ(0,0)=0$, so
	\[\widehat H^0(G,\op{Hom}_\ZZ(X,X))=\widehat H^0(G,\op{Hom}_\ZZ(X',X'))=0,\]
	making the checks on $\varphi$ and $\varphi'$ both trivial.
\end{example}
More concretely, $X$ and $X'$ are cohomologically equivalent if and only if we have two $G$-module morphisms $\varphi\colon X'\to X$ and $\varphi'\colon X\to X'$ and two $\ZZ$-module morphisms $f\colon X\to X$ and $f'\colon X'\to X'$ such that
\[\varphi\circ\varphi'=\id_X+N_Gf\qquad\text{and}\qquad\varphi'\circ\varphi=\id_{X'}+N_Gf'.\]
As a quick sanity check that this is a reasonable notion of equivalence of modules, we have the following.
\begin{lemma} \label{lem:monoidequiv}
	Let $G$ be a finite group. If the $G$-modules $X$ and $X'$ are equivalent and $Y$ and $Y'$ are equivalent, then $X\oplus Y$ is equivalent to $X'\oplus Y'$.
\end{lemma}
\begin{proof}
	We are promised the morphisms
	\begin{itemize}
		\item $\varphi\colon X'\to X$ and $\varphi'\colon X\to X'$ (as morphisms of $G$-modules),
		\item $f\colon X\to X$ and $f'\colon X'\to X'$ (as morphisms of $\ZZ$-modules),
		\item $\psi\colon Y'\to Y$ and $\psi'\colon Y\to Y'$ (as morphisms of $G$-modules),
		\item $g\colon Y\to Y$ and $g'\colon Y'\to Y'$ (as morphisms of $\ZZ$-modules),
	\end{itemize}
	which are required to satisfy
	\begin{align*}
		\varphi\circ\varphi'={\id_X}+N_Gf\qquad&\text{and}\qquad\varphi'\circ\varphi={\id_{X'}}+N_Gf', \\
		\psi\circ\psi'={\id_Y}+N_Gg\qquad&\text{and}\qquad\psi'\circ\psi={\id_{Y'}}+N_Gg'.
	\end{align*}
	Summing everywhere, we get the $G$-module homomorphisms $\varphi\oplus\psi\colon X\oplus Y\to X'\oplus Y'$ and $\varphi'\oplus\psi'\colon X'\oplus Y'\to X\oplus Y$ satisfying
	\begin{align*}
		(\varphi\oplus\psi)\circ(\varphi'\oplus\psi') &= (\varphi\circ\varphi')\oplus(\psi\circ\psi') \\
		&= ({\id_X}+N_Gf)\oplus({\id_Y}+N_Gg) \\
		&= {\id_X}\oplus{\id_Y}+N_G(f\oplus g).
	\end{align*}
	The other check is analogous, switching primed and unprimed variables.
\end{proof}
We now show that this notion of equivalence correctly translates to shiftable functors.
\begin{proposition} \label{prop:cohomologicaldef}
	Let $G$ be a finite group, and let $X$ and $X'$ be $G$-modules. Then $X$ and $X'$ are cohomologically equivalent if and only if there is a natural isomorphism
	\[\Phi_\bullet\colon\widehat H^0(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^0(G,\op{Hom}_\ZZ(X',-)).\]
\end{proposition}
\begin{proof}
	In the forward direction, suppose $X$ and $X'$ are cohomologically equivalent so that we have $[\varphi]\in\widehat H^0(G,\op{Hom}_\ZZ(X',X))$ and $[\varphi']\in\widehat H^0(G,\op{Hom}_\ZZ(X,X'))$ such that
	\[[\varphi]\cup[\varphi']=[\varphi\circ\varphi']=[\id_X]\qquad\text{and}\qquad[\varphi']\cup[\varphi]=[\varphi'\circ\varphi]=[\id_{X'}],\]
	where we are using the canonical evaluation maps for the cup products. Now, we note that, for any $G$-module $A$, we have inverse morphisms
	\begin{equation}
		\arraycolsep=1.4pt\begin{array}{ccc}
			\widehat H^0(G,\op{Hom}_\ZZ(X,A)) &\simeq& \widehat H^0(G,\op{Hom}_\ZZ(X,A)) \\
			{[f]} &\mapsto& {[f\circ\varphi]} \\
			{[f'\circ\varphi']} & \mapsfrom & {[f']}.
		\end{array} \label{eq:makenaturaliso}
	\end{equation}
	Indeed, these are mutually inverse because
	\[[f\circ\varphi\circ\varphi']=[f]\cup[\varphi\circ\varphi']=[f]\circ[{\id_X}]=[f]\]
	and similar on the other side. To finish, we note that the isomorphisms \autoref{eq:makenaturaliso} assemble into a natural isomorphism by \autoref{lem:cuppingisnatural} and \autoref{lem:cupiscomp}.

	We now show the backwards direction. Suppose we have a natural isomorphism $\Phi_\bullet$. Then applying \autoref{lem:naturaltransiscupping} in both directions, we get $[\varphi]\in\widehat H^0(G,\op{Hom}_\ZZ(X',X))$ and $[\varphi']\in\widehat H^0(G,\op{Hom}_\ZZ(X,X'))$ such that the morphisms
	\[\arraycolsep=1.4pt\begin{array}{cccc}
		\Phi_\bullet\colon& \widehat H^0(G,\op{Hom}_\ZZ(X,-)) &\simeq& \widehat H^0(G,\op{Hom}_\ZZ(X,-)) \\
		&{[f]} &\mapsto& {[f\circ\varphi]} \\
		&{[f'\circ\varphi']} & \mapsfrom & {[f']}
	\end{array}\]
	are mutually inverse. In particular, we see that
	\[[\id_X]=[{\id_X}\circ\varphi\circ\varphi']=[\varphi\circ\varphi'],\]
	so $[\varphi\circ\varphi']=[\id_X]$. Swapping primed and unprimed variables, we see $[\varphi'\circ\varphi]=[\id_{X'}]$ as well.
\end{proof}
\begin{remark}
	The above result makes it fairly clear that cohomological equivalence actually makes an equivalence relation. In particular, we can invert and compose natural isomorphisms, which gives symmetry and transitivity of cohomological equivalence respectively.
\end{remark}
One use of this machinery is that we have pretty good tools to tell what is cohomologically equivalent to $0$.
\begin{cor} \label{cor:bettercohomequivzero}
	Let $G$ be a finite group, and let $X$ be a $G$-module. Then $X$ is cohomologically equivalent to $0$ if and only if $\widehat H^0(G,\op{Hom}_\ZZ(X,X))=0$.
\end{cor}
\begin{proof}
	On one hand, if $X$ is cohomologically equivalent to $0$, then \autoref{prop:cohomologicaldef} promises a natural isomorphism
	\[\Phi_\bullet\colon\widehat H^0(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^0(G,\op{Hom}_\ZZ(0,-))=0,\]
	so it follows $\widehat H^0(G,\op{Hom}_\ZZ(X,X))=0$ by plugging in $X$.

	On the other hand, if $\widehat H^0(G,\op{Hom}_\ZZ(X,X))=0$, then the $G$-module homomorphism ${\id_X}\colon X\to X$ must be equivalent to $0$ in this group. So let $\varphi\colon0\to X$ and $\varphi'\colon X\to0$ be the canonical zero morphisms so that
	\[[\varphi\circ\varphi']=[0]=[{\id_X}]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X))\]
	and
	\[[\varphi'\circ\varphi]=[0]=[{\id_0}]\in\widehat H^0(G,\op{Hom}_\ZZ(0,0)),\]
	which finishes.
\end{proof}
\begin{ex} \label{ex:ziexample}
	It is not in general true that two $G$-modules $X$ and $X'$ are cohomologically equivalent if and only if $\widehat H^0(G,\op{Hom}_\ZZ(X,X))\cong\widehat H^0(G,\op{Hom}_\ZZ(X',X'))$. Indeed, let $G=\langle\sigma\rangle\cong\ZZ/2\ZZ$ act on $X=\ZZ$ trivially and on $X'=\ZZ i$ by $\sigma\colon i\mapsto-i$. Then
	\[\op{Hom}_\ZZ(\ZZ,\ZZ)\cong\ZZ\cong\op{Hom}_\ZZ(\ZZ i,\ZZ i)\]
	as $G$-modules (!), but these modules are not cohomologically equivalent because
	\[\widehat H^0(G,\op{Hom}_\ZZ(\ZZ,\ZZ))\cong\ZZ/2\ZZ\not\cong0\cong\widehat H^0(G,\op{Hom}_\ZZ(\ZZ,\ZZ i)).\]
	Namely, $\op{Hom}_\ZZ(\ZZ,\ZZ i)=0$ as $G$-modules.
\end{ex}
\begin{cor} \label{cor:additiontozero}
	Let $G$ be a finite group, and let $A$ and $B$ be $G$-modules. Then, if $A\oplus B$ is cohomologically equivalent to $0$, then both $A$ and $B$ are cohomologically equivalent to $0$.
\end{cor}
\begin{proof}
	This is not too hard to see directly, but it falls immediately out of using \autoref{cor:bettercohomequivzero} and writing
	\begin{align*}
		0 &= \widehat H^0(G,\op{Hom}_\ZZ(A\oplus B,A\oplus B)) \\
		&\simeq \widehat H^0(G,\op{Hom}_\ZZ(A,A))\oplus\widehat H^0(G,\op{Hom}_\ZZ(A,B))\oplus{} \\
		&\qquad\widehat H^0(G,\op{Hom}_\ZZ(B,A))\oplus\widehat H^0(G,\op{Hom}_\ZZ(B,B)),
	\end{align*}
	from which $\widehat H^0(G,\op{Hom}_\ZZ(A,A))=\widehat H^0(G,\op{Hom}_\ZZ(B,B))=0$ is forced.
\end{proof}
\begin{example} \label{ex:projectiveiszero}
	By \autoref{ex:inducediszero}, free $\ZZ[G]$-modules $\ZZ[G]^S\simeq\ZZ[G]\otimes_\ZZ\ZZ^S$ for sets $S$ are cohomologically equivalent to $0$. It follows that all projective $\ZZ[G]$-modules are cohomologically equivalent to $0$ from \autoref{cor:additiontozero}.
\end{example}
Here is a quick partial converse to \autoref{ex:projectiveiszero}.
\begin{proposition}
	Let $G$ be a finite group. If $X$ is $\ZZ$-projective and cohomologically equivalent to $0$, then $X$ is $\ZZ[G]$-projective.
\end{proposition}
\begin{proof}
	It suffices to show that $\op{Hom}_{\ZZ[G]}(X,-)$ is exact. Well, given a short exact sequence
	\[0\to A\to B\to C\to 0\]
	of $G$-modules, the $\ZZ$-projectivity of $X$ implies that
	\[0\to\op{Hom}_\ZZ(X,A)\to\op{Hom}_\ZZ(X,B)\to\op{Hom}_\ZZ(X,C)\to0\]
	is also exact. Taking cohomology, we have the exact sequence
	\[0\to\op{Hom}_{\ZZ[G]}(X,A)\to\op{Hom}_{\ZZ[G]}(X,B)\to\op{Hom}_{\ZZ[G]}(X,C)\to H^1(G,\op{Hom}_\ZZ(X,A)),\]
	and $H^1(G,\op{Hom}_\ZZ(X,A))=0$ by \autoref{prop:cohomologicaldef}. So indeed, $\op{Hom}_{\ZZ[G]}(X,-)$ is exact.
\end{proof}
\begin{remark}
	Overall, it seems like an interesting question to pin down exactly which $G$-modules are cohomologically equivalent to $0$. It is possible to show that all such $X$ must be acyclic, but it seems currently out of reach to show that being acyclic is also sufficient.
\end{remark}
Anyway, the alternate definition for cohomological equivalence from \autoref{prop:cohomologicaldef} also provides us with a way to multiply.
\begin{cor} \label{cor:multequiv}
	Let $G$ be a finite group. If $X$ and $X'$ are cohomologically equivalent and $Y$ and $Y'$ are cohomologically equivalent, then $X\otimes_\ZZ X'$ is cohomologically equivalent to $Y\otimes_\ZZ Y'$.
\end{cor}
\begin{proof}
	We are granted natural isomorphisms as follows.
	\[\arraycolsep=1.4pt\begin{array}{cccc}
		\Phi_\bullet\colon &\widehat H^0(G,\op{Hom}_\ZZ(X,-))&\Rightarrow&\widehat H^0(G,\op{Hom}_\ZZ(X',-)) \\
		\Psi_\bullet\colon &\widehat H^0(G,\op{Hom}_\ZZ(Y,-))&\Rightarrow&\widehat H^0(G,\op{Hom}_\ZZ(Y',-))
	\end{array}\]
	Now, repeatedly using the hom--tensor adjunction, we can chain together natural isomorphisms
	\begin{align*}
		\widehat H^0(G,\op{Hom}_\ZZ(X\otimes_\ZZ Y,-)) &\simeq \widehat H^0(G,\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(Y,-))) \\
		&\hspace{-1.78em}\stackrel{\Phi\op{Hom}(Y,-)}\simeq \widehat H^0(G,\op{Hom}_\ZZ(X',\op{Hom}_\ZZ(Y,-))) \\
		&\simeq \widehat H^0(G,\op{Hom}_\ZZ(X'\otimes_\ZZ Y,-)) \\
		&\simeq \widehat H^0(G,\op{Hom}_\ZZ(Y\otimes_\ZZ X',-)) \\
		&\simeq \widehat H^0(G,\op{Hom}_\ZZ(Y,\op{Hom}_\ZZ( X',-))) \\
		&\hspace{-2.25em}\stackrel{\Psi\op{Hom}_\ZZ(X',-)}\simeq \widehat H^0(G,\op{Hom}_\ZZ(Y',\op{Hom}_\ZZ(X',-))) \\
		&\simeq \widehat H^0(G,\op{Hom}_\ZZ(Y'\otimes_\ZZ X',-)) \\
		&\simeq \widehat H^0(G,\op{Hom}_\ZZ(X'\otimes_\ZZ Y',-)),
	\end{align*}
	which is what we wanted.
\end{proof}
One might hope that we can get more information by using indices away from $0$, but in fact we cannot.
\begin{proposition} \label{prop:betterocohomdef}
	Let $G$ be a finite group, and let $X$ and $X'$ be $G$-modules. Then the following are equivalent.
	\begin{listalph}
		\item $X$ and $X'$ are cohomologically equivalent.
		\item For some $r\in\ZZ$, there is a natural isomorphism
		\[\Phi_\bullet^{(r)}\colon\widehat H^r(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^r(G,\op{Hom}_\ZZ(X',-)).\]
		\item There is a $G$-module homomorphism $\varphi\colon X'\to X$ such that the induced maps
		\[(-\circ\varphi)\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^i(G,\op{Hom}_\ZZ(X',-))\]
		are natural isomorphisms for all $i\in\ZZ$.
	\end{listalph}
\end{proposition}
\begin{proof}
	Note that (a) implies (b) by taking $r=0$ and applying \autoref{prop:cohomologicaldef}. Also, (c) implies (a) by taking $i=0$ and again applying \autoref{prop:cohomologicaldef}. Lastly, to show (b) implies (c), we note that \autoref{prop:allnaturaltransarecups} promises us $\varphi\colon X'\to X$ such that
	\[\Phi_\bullet^{(r)}=(-\circ\varphi).\]
	We would like to use \autoref{prop:dimshiftcupisos}. Let our shifting pair be $(\op{Hom}_\ZZ(X,-),\op{Hom}_\ZZ(X',-),\op{Hom}_\ZZ(X',X),\eta)$, where $\eta_\bullet$ is the canonical pre-composition map
	\[\eta_\bullet\colon\op{Hom}_\ZZ(X',X)\otimes_\ZZ\op{Hom}_\ZZ(X,-)\to\op{Hom}_\ZZ(X',-).\]
	Then we take $r=r$ and $s=0$ and $c=[\varphi]$ as above so that the cup-product natural transformation
	\[([\varphi]\cup-)\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^i(G,\op{Hom}_\ZZ(X',-))\]
	is simply induced by $(-\circ\varphi)$ for any $i\in\ZZ$ by \autoref{lem:cupiscomp}. So we are given that this is a natural isomorphism at $i=r$, so \autoref{prop:dimshiftcupisos} gives us this isomorphism at all $i\in\ZZ$, which proves (c).
	% Thus, (b) implies (c) is the interesting part. Observe that we already know from \autoref{lem:dimshiftnaturaltrans} that we have a natural isomorphism
	% \[\Phi^{(0)}_\bullet\colon\widehat H^0(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^0(G,\op{Hom}_\ZZ(X',-)).\]
	% Now, applying \autoref{lem:naturaltransiscupping}, we see that this must be induced by some $\varphi\colon X'\to X$, so we know that we have a natural isomorphism
	% \begin{equation}
	% 	(-\circ\varphi)\colon\widehat H^i(G,\op{Hom}_\ZZ(X,A))\to\widehat H^i(G,\op{Hom}_\ZZ(X',A)) \label{eq:cupshifting}
	% \end{equation}
	% is an isomorphism for all $G$-modules $A$ at $i=0$. To prove (c), we will shift this isomorphism up and down from $0$. To shift downwards, we suppose that we have an isomorphism always at $i$, and we show that we have an isomorphism always at $i-1$. Well, for any $G$-module $A$, we note the morphism of ($\ZZ$-split) short exact sequences
	% % https://q.uiver.app/?q=WzAsMTAsWzAsMSwiMCJdLFsxLDEsIlxcb3B7SG9tfV9cXFpaKFgnLElfR1xcb3RpbWVzX1xcWlogQSkiXSxbMiwxLCJcXG9we0hvbX1fXFxaWihYJyxcXFpaW0ddXFxvdGltZXNfXFxaWiBBKSJdLFszLDEsIlxcb3B7SG9tfV9cXFpaKFgnLEEpIl0sWzQsMSwiMCJdLFsxLDAsIlxcb3B7SG9tfV9cXFpaKFgsSV9HXFxvdGltZXNfXFxaWiBBKSJdLFsyLDAsIlxcb3B7SG9tfV9cXFpaKFgsXFxaWltHXVxcb3RpbWVzX1xcWlogQSkiXSxbMywwLCJcXG9we0hvbX1fXFxaWihYLEEpIl0sWzAsMCwiMCJdLFs0LDAsIjAiXSxbOCw1XSxbNSw2XSxbNiw3XSxbNyw5XSxbMCwxXSxbMSwyXSxbMiwzXSxbMyw0XSxbNSwxLCIoLVxcY2lyY1xcdmFycGhpKSIsMl0sWzYsMiwiKC1cXGNpcmNcXHZhcnBoaSkiLDJdLFs3LDMsIigtXFxjaXJjXFx2YXJwaGkpIiwyXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% \begin{equation}
	% 	\begin{tikzcd}[column sep=10pt]
	% 		0 & {\op{Hom}_\ZZ(X,I_G\otimes_\ZZ A)} & {\op{Hom}_\ZZ(X,\ZZ[G]\otimes_\ZZ A)} & {\op{Hom}_\ZZ(X,A)} & 0 \\
	% 		0 & {\op{Hom}_\ZZ(X',I_G\otimes_\ZZ A)} & {\op{Hom}_\ZZ(X',\ZZ[G]\otimes_\ZZ A)} & {\op{Hom}_\ZZ(X',A)} & 0
	% 		\arrow[from=1-1, to=1-2]
	% 		\arrow[from=1-2, to=1-3]
	% 		\arrow[from=1-3, to=1-4]
	% 		\arrow[from=1-4, to=1-5]
	% 		\arrow[from=2-1, to=2-2]
	% 		\arrow[from=2-2, to=2-3]
	% 		\arrow[from=2-3, to=2-4]
	% 		\arrow[from=2-4, to=2-5]
	% 		\arrow["{(-\circ\varphi)}"', from=1-2, to=2-2]
	% 		\arrow["{(-\circ\varphi)}"', from=1-3, to=2-3]
	% 		\arrow["{(-\circ\varphi)}"', from=1-4, to=2-4]
	% 	\end{tikzcd} \label{eq:somesesgoingdown}
	% \end{equation}
	% whose boundary morphisms induce the following commutative square.
	% % https://q.uiver.app/?q=WzAsNCxbMSwwLCJcXHdpZGVoYXQgSF57aS0xfShHLFxcb3B7SG9tfV9cXFpaKFgnLEEpKSJdLFswLDAsIlxcd2lkZWhhdCBIXntpLTF9KEcsXFxvcHtIb219X1xcWlooWCxBKSkiXSxbMCwxLCJcXHdpZGVoYXQgSF4wKEcsXFxvcHtIb219X1xcWlooWCxJX0dcXG90aW1lc19cXFpaIEEpIl0sWzEsMSwiXFx3aWRlaGF0IEheMChHLFxcb3B7SG9tfV9cXFpaKFgnLElfR1xcb3RpbWVzX1xcWlogQSkiXSxbMSwwLCJcXHZhcnBoaVxcY3VwLSJdLFsyLDMsIlxcdmFycGhpXFxjdXAtIl0sWzEsMiwiXFxkZWx0YSIsMl0sWzAsMywiXFxkZWx0YSIsMl1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% \[\begin{tikzcd}
	% 	{\widehat H^{i-1}(G,\op{Hom}_\ZZ(X,A))} & {\widehat H^{i-1}(G,\op{Hom}_\ZZ(X',A))} \\
	% 	{\widehat H^i(G,\op{Hom}_\ZZ(X,I_G\otimes_\ZZ A))} & {\widehat H^i(G,\op{Hom}_\ZZ(X',I_G\otimes_\ZZ A))}
	% 	\arrow["{(-\circ\varphi)}", from=1-1, to=1-2]
	% 	\arrow["{(-\circ\varphi)}", from=2-1, to=2-2]
	% 	\arrow["\delta"', from=1-1, to=2-1]
	% 	\arrow["\delta"', from=1-2, to=2-2]
	% \end{tikzcd}\]
	% In particular, the inductive hypothesis tells us that the bottom row is an isomorphism, and the fact that both middle terms of \autoref{eq:somesesgoingdown} are induced by \autoref{lem:hompreservesinduced} implies that the $\delta$s on either side are also isomorphisms. So the top row is an isomorphism, finishing.
	%
	% Similarly, to shift upwards, we suppose that \autoref{eq:cupshifting} is always an isomorphism at $i$, and we show that we have an isomorphism always at $i+1$. Well, for any $G$-module $A$, we note the ($\ZZ$-split) short exact sequences
	% % https://q.uiver.app/?q=WzAsMTAsWzAsMSwiMCJdLFsxLDEsIlxcb3B7SG9tfV9cXFpaKFgnLEEpIl0sWzIsMSwiXFxvcHtIb219X1xcWlooWCcsXFxvcHtIb219X1xcWlooXFxaWltHXSxBKSkiXSxbMywxLCJcXG9we0hvbX1fXFxaWihYJyxcXG9we0hvbX1fXFxaWihJX0csQSkpIl0sWzQsMSwiMCJdLFsxLDAsIlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMiwwLCJcXG9we0hvbX1fXFxaWihYLFxcb3B7SG9tfV9cXFpaKFxcWlpbR10sQSkpIl0sWzMsMCwiXFxvcHtIb219X1xcWlooWCxcXG9we0hvbX1fXFxaWihJX0csQSkpIl0sWzAsMCwiMCJdLFs0LDAsIjAiXSxbOCw1XSxbNSw2XSxbNiw3XSxbNyw5XSxbMCwxXSxbMSwyXSxbMiwzXSxbMyw0XSxbNSwxLCIoLVxcY2lyY1xcdmFycGhpKSIsMl0sWzYsMiwiKC1cXGNpcmNcXHZhcnBoaSkiLDJdLFs3LDMsIigtXFxjaXJjXFx2YXJwaGkpIiwyXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% \begin{equation}
	% 	\begin{tikzcd}[column sep=10pt]
	% 		0 & {\op{Hom}_\ZZ(X,A)} & {\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(\ZZ[G],A))} & {\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A))} & 0 \\
	% 		0 & {\op{Hom}_\ZZ(X',A)} & {\op{Hom}_\ZZ(X',\op{Hom}_\ZZ(\ZZ[G],A))} & {\op{Hom}_\ZZ(X',\op{Hom}_\ZZ(I_G,A))} & 0
	% 		\arrow[from=1-1, to=1-2]
	% 		\arrow[from=1-2, to=1-3]
	% 		\arrow[from=1-3, to=1-4]
	% 		\arrow[from=1-4, to=1-5]
	% 		\arrow[from=2-1, to=2-2]
	% 		\arrow[from=2-2, to=2-3]
	% 		\arrow[from=2-3, to=2-4]
	% 		\arrow[from=2-4, to=2-5]
	% 		\arrow["{(-\circ\varphi)}"', from=1-2, to=2-2]
	% 		\arrow["{(-\circ\varphi)}"', from=1-3, to=2-3]
	% 		\arrow["{(-\circ\varphi)}"', from=1-4, to=2-4]
	% 	\end{tikzcd} \label{eq:somesesgoingup}
	% \end{equation}
	% whose boundary morphisms induce the following commutative square.
	% % https://q.uiver.app/?q=WzAsNCxbMSwwLCJcXHdpZGVoYXQgSF57aX0oRyxcXG9we0hvbX1fXFxaWihYJyxcXG9we0hvbX1fXFxaWihJX0csQSkpKSJdLFswLDAsIlxcd2lkZWhhdCBIXntpfShHLFxcb3B7SG9tfV9cXFpaKFgsXFxvcHtIb219X1xcWlooSV9HLEEpKSkiXSxbMCwxLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMSwxLCJcXHdpZGVoYXQgSF57aSsxfShHLFxcb3B7SG9tfV9cXFpaKFgnLEEpIl0sWzEsMCwiXFx2YXJwaGlcXGN1cC0iXSxbMiwzLCJcXHZhcnBoaVxcY3VwLSJdLFsxLDIsIlxcZGVsdGEiLDJdLFswLDMsIlxcZGVsdGEiLDJdXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% \[\begin{tikzcd}
	% 	{\widehat H^{i}(G,\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(I_G,A)))} & {\widehat H^{i}(G,\op{Hom}_\ZZ(X',\op{Hom}_\ZZ(I_G,A)))} \\
	% 	{\widehat H^{i+1}(G,\op{Hom}_\ZZ(X,A))} & {\widehat H^{i+1}(G,\op{Hom}_\ZZ(X',A))}
	% 	\arrow["{(-\circ\varphi)}", from=1-1, to=1-2]
	% 	\arrow["{(-\circ\varphi)}", from=2-1, to=2-2]
	% 	\arrow["\delta"', from=1-1, to=2-1]
	% 	\arrow["\delta"', from=1-2, to=2-2]
	% \end{tikzcd}\]
	% This time around, the top row is an isomorphism by the inductive hypothesis, and the left and row arrows are isomorphisms because the middle terms of \autoref{eq:somesesgoingup} are induced by \autoref{lem:hompreservesinduced}. So the bottom row is an isomorphism as well, finishing.
\end{proof}

\subsection{Encoding Modules}
Lastly, we arrive at the application we care about: encoding cohomology. Cohomological equivalence is exactly what we need to talk about uniqueness.
\begin{prop} \label{prop:encodingmodules}
	Let $G$ be a finite group, and let $r,s\in\ZZ$ be indices. Then, if nonempty, the set of $G$-module $X$ with a natural isomorphism
	\[\Phi_\bullet\colon\widehat H^r(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{r+s}(G,-)\]
	make up exactly one cohomological equivalence class.
\end{prop}
\begin{proof}
	Fix some $G$-module $X$ with such a natural isomorphism
	\[\Psi_\bullet\colon\widehat H^r(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{r+s}(G,-).\]
	We would like to show that a $G$-module $X'$ has a natural isomorphism $\Phi_\bullet$ between the analogous functors if and only if $X$ and $X'$ are cohomologically equivalent.

	% Noting that the cup product is natural in both arguments (see, for example, \autoref{}), we see that the combination of \autoref{thm:yesitisacocycle} and \autoref{prop:alternativetupleclass} tells us that we have a natural isomorphism
	% \[\Psi_\bullet\colon\widehat H^0(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^2(G,-).\]
	% We now proceed with the proof.
	If $X$ and $X'$ are cohomologically equivalent, then we can compose the promised natural isomorphism of \autoref{prop:betterocohomdef} (c) with $\Psi_\bullet$, giving a natural isomorphism
	\[\widehat H^r(G,\op{Hom}_\ZZ(X',-))\Rightarrow\widehat H^r(G,\op{Hom}_\ZZ(X,-))\stackrel{\Psi_\bullet}\Rightarrow\widehat H^{r+s}(G,-).\]
	In the other direction, if we have a natural isomorphism
	\[\Phi_\bullet\colon\widehat H^r(G,\op{Hom}_\ZZ(X',-))\Rightarrow\widehat H^{r+s}(G,-),\]
	then we can compose with $\Psi_\bullet^{-1}$ to build a natural isomorphism
	\[\widehat H^r(G,\op{Hom}_\ZZ(X',-))\stackrel{\Phi_\bullet}\Rightarrow\widehat H^{r+s}(G,-)\stackrel{\Psi^{-1}_\bullet}\Rightarrow\widehat H^r(G,\op{Hom}_\ZZ(X,-)),\]
	from which it follows that $X$ and $X'$ are cohomologically equivalent by \autoref{prop:cohomologicaldef} (b).
\end{proof}
% \begin{remark}
% 	In fact, we can see that the natural isomorphism
% 	\[\Phi_\bullet\colon\widehat H^0(G,\op{Hom}_\ZZ(X',-))\Rightarrow\widehat H^2(G,-)\]
% 	must be a cup-product map with an element in $\widehat H^2(G,X')$. Namely, we note that $\Phi_\bullet$ is equal to the composite
% 	\[\widehat H^0(G,\op{Hom}_\ZZ(X',-))\stackrel{\Phi_\bullet}\Rightarrow\widehat H^2(G,-)\stackrel{\Psi^{-1}_\bullet}\Rightarrow\widehat H^0(G,\op{Hom}_\ZZ(X,-))\stackrel{\Psi_\bullet}\Rightarrow\widehat H^2(G,-).\]
% 	However, $\Psi_\bullet$ is a cup-product map with an element in $\widehat H^2(G,X)$ by its construction, and
% 	\[\widehat H^0(G,\op{Hom}_\ZZ(X',-))\stackrel{\Phi_\bullet}\Rightarrow\widehat H^2(G,-)\stackrel{\Psi^{-1}_\bullet}\Rightarrow\widehat H^0(G,\op{Hom}_\ZZ(X,-))\]
% 	is a cup-product map with an element in $\widehat H^0(G,\op{Hom}_\ZZ(X,X'))$ by \autoref{lem:naturaltransiscupping}. Composing our cup-product maps makes a cup-product map with an element in $\widehat H^2(G,X')$.
% \end{remark}
% \begin{example}
% 	Suppose that a $G$-module $X$ has a natural isomorphism
% 	\[\widehat H^0(\]
% 	If $M$ is any induced module, then we know $M$ is cohomologically equivalent to $0$. So \autoref{lem:monoidequiv} reassures us that $X\oplus M$ is cohomologically equivalent to $X\oplus0\simeq X$.
% \end{example}
\begin{example} \label{ex:igisencoding}
	Take $s\ge 0$. Dimension-shifting iteratively with the short exact sequence
	\[0\to I_G\otimes_\ZZ A\to\ZZ[G]\otimes_\ZZ A\to A\to0\]
	shows that
	\[\widehat H^{r+s}(G,A)\simeq\widehat H^r\left(G,\op{Hom}_\ZZ(I_G^{\otimes s},A)\right),\]
	and in fact these isomorphisms are natural by the functoriality of boundary morphisms. So the equivalence class of \autoref{prop:encodingmodules} is represented by $I_G^{\otimes s}$.
\end{example}
\begin{remark}
	We will show in \autoref{ex:allencoderesexist} that all of these equivalence classes are nonempty.
\end{remark}
\begin{example} \label{ex:notalltorsionfree}
	Not all $r$-encoding modules are $\ZZ$-torsion-free. For example, if $M$ is an $r$-encoding module, and $A$ is induced, then $M\oplus A$ is cohomologically equivalent to $M$, so $M\oplus A$ is an $r$-encoding module. However, not all induced modules $A$ are $\ZZ$-torsion-free.
\end{example}
% The above two examples should give a feeling for why this uniqueness problem is difficult.
In fact, akin to the classification of natural transformations from \autoref{prop:allnaturaltransarecups}, we can show that these encoding maps must be cup products.
% \begin{lemma}
% 	Let $G$ be a finite group, and let $p\ge0$ be an index. Then there exists some $x_p\in\widehat H^p\left(G,I_G^{\otimes p}\right)$ such that
% 	\[x_p\cup-\colon\widehat H^0\left(G,\op{Hom}_\ZZ(I_G^{\otimes p},-)\right)\Rightarrow H^p(G,-)\]
% 	is a natural isomorphism.
% \end{lemma}
% \begin{proof}
% 	We quickly remark that (akin to \autoref{}), by \autoref{} and functoriality of $\widehat H^p(G,-)$, any $x_p\in\widehat H^p(G,I_G^{\otimes p})$ will at least create a natural transformation. So the main point is to make the cup-product into an isomorphism. For $p=0$, we take $x_0\coloneqq[1]\in\widehat H^p(G,\ZZ)$ so that
% 	\[[1]\cup-\colon\widehat H^0(G,\op{Hom}_\ZZ(\ZZ,-))\Rightarrow\widehat H^0(G,-)\]
% 	is simply the map taking a $0$-cocycle $c$ to $[1]\cup c=c(1)$, which is the isomorphism $\op{Hom}_\ZZ(\ZZ,A)\simeq A$ for each $A$ anyway.

% 	We will also show $p=1$ by hand. The point here is that, for any $G$-module $A$, we already have (natural) isomorphisms
% 	\[\widehat H^0(G,\op{Hom}_\ZZ(I_G,A))\simeq\widehat H^1(G,A)\]
% 	by dimension-shifting, so we just have to track these through. Namely, we have the ($\ZZ$-split) short exact sequence
% 	\[0\to A\to\op{Hom}_\ZZ(\ZZ[G],A)\to\op{Hom}_\ZZ(I_G,A)\to 0,\]
% 	so given $[f]\in\widehat H^0(G,\op{Hom}_\ZZ(I_G,A))$ so that $f\in\op{Hom}_{\ZZ[G]}(I_G,A)$, this gets pulled back to the $0$-cochain $c\in\op{Hom}_\ZZ(\ZZ[G],A)$ defined by
% 	\[c\colon z\mapsto f(z-\varepsilon(z)).\]
% 	Pushing this down to $Z^1(G,\op{Hom}_\ZZ(\ZZ[G],A))$, we compute
% 	\begin{align*}
% 		(dc)(g)(z) &= (gc)(z)-c(z) \\
% 		&= g\cdot c\left(g^{-1}z\right) - c(z) \\
% 		&= g\cdot f\left(g^{-1}z-\varepsilon(g^{-1}z)\right) - f(z-\varepsilon(z)) \\
% 		&= f(z-g\varepsilon(z))-f(z-\varepsilon(z)) \\
% 		&= \varepsilon(z)\cdot f(1-g),
% 	\end{align*}
% 	so we pull back to the $1$-cochain $g\mapsto f(1-g)$ in $H^1(G,A)$. To see this as a cup product, we just note that running $A=I_G$ and $f=\id_{I_G}$ through this argument would reveal that $g\mapsto(1-g)$ is a $1$-cochain in $H^1(G,I_G)$, which we denote by $x_1$. Then returning to a general $G$-module $A$ with $[f]\in\widehat H^1(G,\op{Hom}_\ZZ(I_G,A))$, we see
% 	\[(x_1\cup[f])\colon g\mapsto(f\circ x_1)(g)=f(1-g)\]
% 	by construction of the cup product as evaluation.
% \end{proof}
\begin{cor} \label{prop:encodingsarecups}
	Let $G$ be a finite group, and let $r\in\ZZ$ be an index. Suppose we have a $G$-module $X$ and index $i\in\ZZ$ with a natural transformation
	\[\Phi_\bullet\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(G,-).\]
	Then there exists $[x]\in\widehat H^r(G,X)$ such that $\Phi_\bullet$ is the cup-product map $([x]\cup-)$.
\end{cor}
\begin{proof}
	The point is to set $X'=\ZZ$ in \autoref{prop:allnaturaltransarecups}. For technical reasons, we note that we have a natural isomorphism
	\[([1]\cup-)\colon\widehat H^{i+r}(G,\op{Hom}_\ZZ(\ZZ,-))\Rightarrow\widehat H^{i+r}(G,-)\]
	by checking at index $0$ and then using \autoref{prop:dimshiftcupisos}. Thus, $\Phi_\bullet$ will induce a natural transformation
	\[\widehat H^0(G,\op{Hom}_\ZZ(X,-))\stackrel{\Phi_\bullet}\Rightarrow\widehat H^{i+r}(G,-)\stackrel{([1]\cup-)^{-1}}\Rightarrow\widehat H^{i+r}(G,\op{Hom}_\ZZ(\ZZ,-)).\]
	By \autoref{prop:allnaturaltransarecups}, we are promised $[x]\in\widehat H^0(G,\op{Hom}_\ZZ(\ZZ,X))$ such that this composite is $([x]\cup-)$. It follows that $\Phi_\bullet$ is
	\[[1]\cup\big([x]\cup-\big)\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(G,-).\]
	Associating, this natural isomorphism is the same as $\big(([1]\cup[x])\cup-\big)$; indeed, fixing a $G$-module $A$ to plug in, we get the result by noting the commutativity of
	% https://q.uiver.app/?q=WzAsOCxbMCwwLCJcXFpaXFxvdGltZXNfXFxaWiBYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMSwwLCJcXFpaXFxvdGltZXNfXFxaWiBBIl0sWzAsMSwiWFxcb3RpbWVzX1xcWlpcXG9we0hvbX1fXFxaWihYLEEpIl0sWzEsMSwiQSJdLFsyLDAsInpcXG90aW1lcyB5XFxvdGltZXMgZiJdLFsyLDEsInp5XFxvdGltZXMgZiJdLFszLDEsImYoenkpIl0sWzMsMCwielxcb3RpbWVzIGYoeSkiXSxbMCwxXSxbMSwzXSxbMCwyXSxbMiwzXSxbNCw1LCIiLDIseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzUsNiwiIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFs0LDcsIiIsMCx7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbNyw2LCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\ZZ\otimes_\ZZ X\otimes_\ZZ\op{Hom}_\ZZ(X,A)} & {\ZZ\otimes_\ZZ A} & {z\otimes y\otimes f} & {z\otimes f(y)} \\
		{X\otimes_\ZZ\op{Hom}_\ZZ(X,A)} & A & {zy\otimes f} & {f(zy)}
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-2, to=2-2]
		\arrow[from=1-1, to=2-1]
		\arrow[from=2-1, to=2-2]
		\arrow[maps to, from=1-3, to=2-3]
		\arrow[maps to, from=2-3, to=2-4]
		\arrow[maps to, from=1-3, to=1-4]
		\arrow[maps to, from=1-4, to=2-4]
	\end{tikzcd}\]
	and passing through \autoref{lem:cupassoc}.
\end{proof}
\begin{example}
	For $r\ge0$, we can continue \autoref{ex:igisencoding} to note that standard dimension-shifting arguments give natural isomorphisms
	\[\widehat H^0\left(G,\op{Hom}_\ZZ(I_G^{\otimes r},-)\right)\Rightarrow\widehat H^r(G,-),\]
	so \autoref{prop:encodingsarecups} implies that these isomorphisms are cup products with an element of $\widehat H^r(G,I_G^{\otimes r})$. For example, when $r=0$, we have $[1]\in\widehat H^0(G,\ZZ)$; and when $r=1$, we have $g\mapsto(1-g)$ in $\widehat H^1(G,I_G)$. Observe that we could also see this by inductively dimension-shifting with \autoref{cor:cupdown}.
\end{example}
Because cup products are better-behaved than just general natural transformations, we get the following nice statement.
\begin{cor} \label{cor:betterencodingdef}
	Let $G$ be a finite group, and let $r\in\ZZ$ an index. Then an $r$-encoding module $X$ has $x\in\widehat H^r(G,X)$ such that
	\[(x\cup-)\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(G,-)\]
	is a natural isomorphism for all $i\in\ZZ$.
\end{cor}
\begin{proof}
	By definition of $X$, we know that there is some $i\in\ZZ$ such that we have a natural isomorphism
	\[\Phi_\bullet\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(G,-).\]
	Then \autoref{prop:encodingsarecups} tells us that this natural isomorphism arises as $(x\cup-)$ for some $x\in\widehat H^r(G,X)$.
	
	To finish, we extend $(x\cup-)$ being a natural isomorphism from a single $i$ to all $i\in\ZZ$ by using \autoref{prop:dimshiftcupisos}. Indeed, take $F=\op{Hom}_\ZZ(X,-)$ and $F'=\mathrm{id}$ and $X=X$ and $\eta\colon X\otimes_\ZZ\op{Hom}_\ZZ(X,-)\Rightarrow\mathrm{id}$ to be the canonical evaluation maps. This finishes.
\end{proof}
% thank you https://math.stackexchange.com/a/44503/869257
\begin{remark} \label{rem:neednaturality}
	Taking $X=\ZZ$ above, we are asserting that, if $G$ is a group such that all $G$-modules admit period-$r$ cohomology which is natural in some sense at a single index $i$, then this periodicity extends to all indices and arises from a cup product with an element of $\widehat H^r(G,\ZZ)$.
	
	Observe that the naturality in the isomorphisms is important: letting $G\coloneqq\ZZ/p\ZZ$ act on $A\coloneqq\ZZ/p\ZZ$ trivially,
	\[\widehat H^{-1}(G,A)=\frac{\ZZ/p\ZZ}{0}\simeq\widehat H^0(G,A),\]
	but this does not extend to all $G$-modules. For example,
	\[\widehat H^{-1}(G,\ZZ)=0\not\cong\frac{\ZZ}{p\ZZ}=\widehat H^0(G,\ZZ).\]
\end{remark}
The element defined in \autoref{cor:betterencodingdef} is so special that we will give it a name.
\begin{definition}
	Let $G$ be a finite group and $X$ an $r$-encoding module. An element $x\in\widehat H^r(G,X)$ as constructed in \autoref{cor:betterencodingdef} is the \textit{encoding element}.
\end{definition}
It will turn out that encoding elements are unique, though they will be almost unique.

\subsection{Encoding Is Unique}
Fix an $r$-encoding module $X$. As a brief intermission, we will show that there is essentially one way to do the encoding
\[\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(G,-).\]
Namely, we know from \autoref{prop:encodingsarecups}, that this natural isomorphism must come from a cup-product with an element $x\in\widehat H^r(G,X)$, so we might wonder how unique this element $x$ is. The answer to this, roughly speaking, will be that $\widehat H^r(G,X)$ is cyclic of order $\#G$ generated by $x$. In the process, we will be able to compute all the cohomology groups $\widehat H^i(G,X)$.

Anyway, the main idea will be to use the following duality result.
\begin{prop}[{\cite[Corollary~XII.6.5]{cartan-eilenberg}}] \label{prop:ceduality}
	Let $G$ be a finite group and $A$ be any $G$-module. Then the cup-product pairing induces an isomorphism
	\[\widehat H^{i-1}(G,\op{Hom}_\ZZ(A,\QQ/\ZZ))\to\op{Hom}_\ZZ\left(\widehat H^{-i}(G,A),\widehat H^{-1}(G,\QQ/\ZZ)\right)\]
	for all $i\in\ZZ$. Indeed, this is a duality upon embedding $\widehat H^{-1}(G,\QQ/\ZZ)$ into $\QQ/\ZZ$.
\end{prop}
% In particular, we will use the following form.
% \begin{cor} \label{cor:betterceduality}
% 	Let $G$ be a finite group and $A$ be a finitely generated $G$-module. Then the cup-product pairing induces an isomorphism
% 	\[\widehat H^{i-1}(G,A)\to\op{Hom}_\ZZ\left(\widehat H^{-i}(G,\op{Hom}_\ZZ(A,\QQ/\ZZ)),\widehat H^{-1}(G,\QQ/\ZZ)\right)\]
% 	for all $i\in\ZZ$.
% \end{cor}
% \begin{proof}
% 	Given a $G$-module $M$, set for brevity $M^*\coloneqq\op{Hom}_\ZZ(M,\QQ/\ZZ)$. Note that the canonical map
% 	\[\varphi\colon A\to A^{**}\]
% 	taking $a\in A$ to $\varphi(a)\colon f\mapsto f(a)$ is a $G$-module morphism as well as an isomorphism of finitely generated abelian groups and hence an isomorphism of $G$-modules. Thus, using \autoref{prop:ceduality}, we can track the isomorphisms
% 	\[\widehat H^{i-1}(G,A)\simeq\widehat H^{i-1}(G,A^{**})\to\op{Hom}_\ZZ\left(\widehat H^{-i}(G,A^*),\widehat H^{-1}(G,\QQ/\ZZ)\right)\]
% 	as sending $a\in\widehat H^{i-1}(G,A)$ to $a^*\mapsto a\cup a^*$. Indeed, this is a matter of tracking through the following diagram.
% 	% https://q.uiver.app/?q=WzAsNixbMCwwLCJcXHdpZGVoYXQgSF57aS0xfShHLEEpXFxvdGltZXNfXFxaWlxcd2lkZWhhdCBIXmkoRyxBXlxcbG9yKSJdLFswLDEsIlxcd2lkZWhhdCBIXntpLTF9KEcsQV57XFxsb3JcXGxvcn0pXFxvdGltZXNfXFxaWlxcd2lkZWhhdCBIXmkoRyxBXlxcbG9yKSJdLFsxLDAsIlxcd2lkZWhhdCBIXnstMX0oRyxBXFxvdGltZXNfXFxaWiBBXlxcbG9yKSJdLFsxLDEsIlxcd2lkZWhhdCBIXnstMX0oRyxBXntcXGxvclxcbG9yfVxcb3RpbWVzX1xcWlogQV5cXGxvcikiXSxbMiwwLCJcXHdpZGVoYXQgSF57LTF9KEcsXFxRUS9cXFpaKSJdLFsyLDEsIlxcd2lkZWhhdCBIXnstMX0oRyxcXFFRL1xcWlopIl0sWzAsMSwiXFx2YXJwaGlcXG90aW1lc3tcXGlkfSIsMl0sWzAsMl0sWzEsM10sWzIsMywiXFx2YXJwaGlcXG90aW1lc3tcXGlkfSIsMl0sWzIsNF0sWzMsNV0sWzQsNSwiIiwwLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
% 	\[\begin{tikzcd}
% 		{\widehat H^{i-1}(G,A)\otimes_\ZZ\widehat H^i(G,A^*)} & {\widehat H^{-1}(G,A\otimes_\ZZ A^*)} & {\widehat H^{-1}(G,\QQ/\ZZ)} \\
% 		{\widehat H^{i-1}(G,A^{**})\otimes_\ZZ\widehat H^i(G,A^*)} & {\widehat H^{-1}(G,A^{**}\otimes_\ZZ A^*)} & {\widehat H^{-1}(G,\QQ/\ZZ)}
% 		\arrow["{\varphi\otimes{\id}}"', from=1-1, to=2-1]
% 		\arrow[from=1-1, to=1-2]
% 		\arrow[from=2-1, to=2-2]
% 		\arrow["{\varphi\otimes{\id}}"', from=1-2, to=2-2]
% 		\arrow[from=1-2, to=1-3]
% 		\arrow[from=2-2, to=2-3]
% 		\arrow[Rightarrow, no head, from=1-3, to=2-3]
% 	\end{tikzcd}\]
% 	The left square commutes by naturality of cup products and commutes, and the right square commutes because the square
% 	% https://q.uiver.app/?q=WzAsOCxbMCwwLCJBXFxvdGltZXNfXFxaWiBBXlxcbG9yIl0sWzAsMSwiQV57XFxsb3JcXGxvcn1cXG90aW1lc19cXFpaIEFeXFxsb3IiXSxbMSwwLCJcXFFRL1xcWloiXSxbMSwxLCJcXFFRL1xcWloiXSxbMiwwLCJhXFxvdGltZXMgYV5cXGxvciJdLFsyLDEsIihmXFxtYXBzdG8gZihhKSlcXG90aW1lcyBhXlxcbG9yIl0sWzMsMCwiYV5cXGxvcihhKSJdLFszLDEsImFeXFxsb3IoYSkiXSxbMCwxLCJcXHZhcnBoaVxcb3RpbWVze1xcaWR9IiwyXSxbMCwyXSxbMSwzXSxbMiwzXSxbNCw2LCIiLDIseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzYsNywiIiwyLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbNCw1LCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzUsNywiIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
% 	\[\begin{tikzcd}
% 		{A\otimes_\ZZ A^*} & {\QQ/\ZZ} & {a\otimes a^*} & {a^*(a)} \\
% 		{A^{**}\otimes_\ZZ A^*} & {\QQ/\ZZ} & {(f\mapsto f(a))\otimes a^*} & {a^*(a)}
% 		\arrow["{\varphi\otimes{\id}}"', from=1-1, to=2-1]
% 		\arrow[from=1-1, to=1-2]
% 		\arrow[from=2-1, to=2-2]
% 		\arrow[Rightarrow, no head, from=1-2, to=2-2]
% 		\arrow[maps to, from=1-3, to=1-4]
% 		\arrow[Rightarrow, no head, from=1-4, to=2-4]
% 		\arrow[maps to, from=1-3, to=2-3]
% 		\arrow[maps to, from=2-3, to=2-4]
% 	\end{tikzcd}\]
% 	commutes.
% \end{proof}
And here is our computation.
\begin{cor} \label{cor:hpxcomputation}
	Let $G$ be a finite group and $X$ an $r$-encoding module. Picking up an encoding element $x\in\widehat H^r(G,X)$, $\widehat H^r(G,X)$ is cyclic of order $\#G$ generated by $x$.
\end{cor}
\begin{proof}
	For brevity, set $n\coloneqq\#G$. By \autoref{cor:betterencodingdef}, we have the isomorphism
	\[x\cup-\colon\widehat H^{-p-1}(G,\op{Hom}_\ZZ(X,\QQ/\ZZ))\to\widehat H^{-1}(G,\QQ/\ZZ)=\textstyle\frac1n\ZZ/\ZZ.\]
	In particular, $\widehat H^{-p-1}(G,\op{Hom}_\ZZ(X,\ZZ))\simeq\ZZ/n\ZZ$, generated by some element $x^\lor$ such that $x\cup x^\lor=[1/n]$.

	Now, we apply \autoref{prop:ceduality} to say that the cup-product pairing induces an isomorphism
	\[{\textstyle\frac1n\ZZ/n\ZZ}\simeq\widehat H^{-p-1}(G,\op{Hom}_\ZZ(X,\QQ/\ZZ))\to\op{Hom}_\ZZ\left(\widehat H^p(G,X),\widehat H^{-1}(G,\QQ/\ZZ)\right)\simeq\op{Hom}_\ZZ\left(\widehat H^p(G,X),\textstyle\frac1n\ZZ/\ZZ\right).\]
	Because $\widehat H^p(G,X)$ is $n$-torsion, homomorphisms $\widehat H^2(G,X)\to\QQ/\ZZ$ must have image in $\frac1n\ZZ/\ZZ$, so in fact the rightmost group is the dual of $\widehat H^p(G,X)$. Because an abelian group is isomorphic to its dual, we see that $\widehat H^p(G,X)$ is in fact cyclic of order $n$.

	It remains to show that $x$ is a generator; for this, we show that $x$ has order at least $n$, which will be enough because $H^2(G,X)$ is cyclic of order $n$. Well, if we have $k\in\ZZ$ such that $kx=0$, then
	\[[k/n]=k\big(x\cup x^\lor\big)=kx\cup x^\lor=[0]\cup x^\lor=[0]\]
	in $\widehat H^{-1}(G,\QQ/\ZZ)\simeq\frac1n\ZZ/\ZZ$, so $n\mid k$. This finishes.
\end{proof}
\begin{remark}
	Conversely, if $x\in\widehat H^r(G,X)$ is any generator, then
	\[(x\cup-)\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(G,-)\]
	is a natural isomorphism. Indeed, certainly some generator $x_0\in\widehat H^p(G,X)$ conjured from \autoref{cor:betterencodingdef} suffices, but then $x=kx_0$ for some $k\in(\ZZ/\#G\ZZ)^\times$, so we have the equality
	\[(x\cup-)=\big((kx_0)\cup-\big)=k(x_0\cup-)\]
	of natural transformations. But multiplication by $k$ is a natural isomorphism $\widehat H^\bullet(G,-)\Rightarrow\widehat H^\bullet(G,-)$ because these cohomology groups are $\#G$-torsion, so we conclude $(x\cup-)=k(x_0\cup-)$ is a natural isomorphism.
\end{remark}
And here is our uniqueness result.
\begin{cor}
	Let $G$ be a finite group, and let $X$ be a finitely generated $r$-encoding module. Then, given $i\in\ZZ$ and two natural isomorphisms
	\[\Phi_\bullet,\Phi_\bullet'\colon\widehat H^i(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(G,-),\]
	there exists a unique $k\in(\ZZ/\#G\ZZ)^\times$ such that $\Phi_\bullet'=k\Phi_\bullet$.
\end{cor}
\begin{proof}
	Note that we are allowed to interpret $k\pmod n$ because these cohomology groups are $\#G$-torsion, so $\#G\cdot\Phi_\bullet=0$.

	Anyway, by \autoref{prop:encodingsarecups}, we know that there are $x,x'\in\widehat H^r(G,X)$ such that
	\[\Phi_\bullet=(x\cup-)\qquad\text{and}\qquad\Phi_\bullet'=(x'\cup-).\]
	However, by \autoref{cor:hpxcomputation}, we see that $\widehat H^r(G,X)$ is cyclic generated by $x$ of order $\#G$, so we can write $x'=kx$ for a unique $k\in\ZZ/\#G\ZZ$.

	It remains to show that $\Phi_\bullet'=k\Phi_\bullet$. Well, for any $G$-module $A$ and $c\in\widehat H^i(G,\op{Hom}_\ZZ(X,A))$, we write
	\[\Phi_A'(c)=x'\cup c=kx\cup c=k(x\cup c)=k\Phi_A(c).\]
	It follows that $\Phi_\bullet'=k\Phi_\bullet$.
\end{proof}

\subsection{The Dual Element}
In the theory of periodic cohomology (e.g., see \cite[Section~XII.11]{cartan-eilenberg}), it is helpful to phrase the theory in terms of having some elements $x\in\widehat H^r(G,\ZZ)$ and $y\in\widehat H^{-r}(G,\ZZ)$ such that
\[x\cup y=[1]\in\widehat H^0(G,\ZZ).\]
In contrast, given an $r$-encoding module $X$, we cannot hope to have $x\in\widehat H^r(G,X)$ and $y\in\widehat H^{-r}(G,X)$ with $x\cup y\in\widehat H^0(G,\ZZ)$ because there is no obvious map $X\otimes_\ZZ X\to\ZZ$. To remedy this, we observe that this is a canonical map
\[X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)\to\ZZ.\]
This idea gives the following result.
% Let $X$ be an $r$-encoding module, and conjure $x\in\widehat H^p(G,X)$ from \autoref{cor:betterencodingdef}. Then note that our proof of \autoref{cor:hpxcomputation} found $x^\lor\in\widehat H^{-p-1}(G,\op{Hom}_\ZZ(X,\QQ/\ZZ))$ such that
% \[x\cup x^\lor=[1/n]\in\widehat H^{-1}(G,\QQ/\ZZ).\]
% This is fairly close to saying that the operation of $x\cup-$ can be inverted with the correct $x^\lor\cup-$ operation (and maybe a sign), but cupping with $[1/n]$ would then not necessarily by the identity transformation.
%
% In particular, we would like to actually be in $\widehat H^0(G,\ZZ)$, whose cup products are well-behaved. As such, we have the following.
\begin{prop} \label{prop:intdualelement}
	Let $G$ be a finite group, and let $X$ be a $G$-module and $r\in\ZZ$ be an index. The following are equivalent.
	\begin{enumerate}[label=(\alph*)]
		\item $X$ is an $r$-encoding module.
		\item There are $x\in\widehat H^r(G,X)$ and $x^\lor\in\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))$ such that
		\[x\cup x^\lor=[1]\in\widehat H^0(G,\ZZ)\qquad\text{and}\qquad x^\lor\cup x=[{\id_X}]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X)).\]
	\end{enumerate}
\end{prop}
\begin{proof}
	For brevity, set $n\coloneqq\#G$.
	
	We start by showing (a) implies (b). By \autoref{cor:betterencodingdef}, we can find an encoding element $x\in\widehat H^r(G,X)$ yielding the isomorphism
	\[(x\cup-)\colon\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))\to\widehat H^0(G,\ZZ)=\ZZ/n\ZZ.\]
	As such, we can find a unique $x^\lor\in\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))$ such that $x\cup x^\lor=[1]$. It remains to show that $x^\lor\cup x=[{\id_X}]$.
	
	Note that $(x\cup-)$ and $(x^\lor\cup-)$ induce morphisms
	\[\arraycolsep=1.4pt\begin{array}{rccc}
		(x\cup-)\colon& \widehat H^0(G,\op{Hom}_\ZZ(X,X)) &\to& \widehat H^r(G,X) \\
		(x^\lor\cup-)\colon& \widehat H^r(G,X) &\to& \widehat H^0(G,\op{Hom}_\ZZ(X,X))
	\end{array}\]
	We claim that these are inverse. Because $(x\cup-)$ is already an isomorphism, it suffices to show that we have an inverse on one side. Well, $\widehat H^r(G,X)$ is cyclic generated by $x$ by \autoref{cor:hpxcomputation}, so it suffices to note that any $kx\in\widehat H^r(G,X)$ has
	\[\big((x\cup-)\circ(x^\lor\cup-)\big)(kx)=x\cup(x^\lor\cup kx)\stackrel*=(x\cup x^\lor)\cup kx=[1]\cup kx=kx.\]
	Notably, $\stackrel*=$ has used \autoref{lem:cupassoc}, noting that the square
	% https://q.uiver.app/?q=WzAsOCxbMCwwLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsXFxaWilcXG90aW1lc19cXFpaIFgiXSxbMCwxLCJcXFpaXFxvdGltZXNfXFxaWiBYIl0sWzEsMSwiWCJdLFsxLDAsIlhcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooWCxYKSJdLFsyLDAsInhfMVxcb3RpbWVzIGZcXG90aW1lcyB4XzIiXSxbMiwxLCJmKHhfMSlcXG90aW1lcyB4XzIiXSxbMywxLCJmKHhfMSl4XzIiXSxbMywwLCJ4XzFcXG90aW1lcyh5XFxtYXBzdG8gZih5KXhfMikiXSxbMCwxXSxbMCwzXSxbMywyXSxbMSwyXSxbNCw1LCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzQsNywiIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFs3LDYsIiIsMix7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbNSw2LCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ X} & {X\otimes_\ZZ\op{Hom}_\ZZ(X,X)} & {x_1\otimes f\otimes x_2} & {x_1\otimes(y\mapsto f(y)x_2)} \\
		{\ZZ\otimes_\ZZ X} & X & {f(x_1)\otimes x_2} & {f(x_1)x_2}
		\arrow[from=1-1, to=2-1]
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-2, to=2-2]
		\arrow[from=2-1, to=2-2]
		\arrow[maps to, from=1-3, to=2-3]
		\arrow[maps to, from=1-3, to=1-4]
		\arrow[maps to, from=1-4, to=2-4]
		\arrow[maps to, from=2-3, to=2-4]
	\end{tikzcd}\]
	commutes. Anyway, we now see that we have inverse morphisms, so
	\[x\cup[{\id_X}]=\id_X(x)=x\]
	implies that $x^\lor\cup x=[{\id_X}]$, finishing.

	We now show (b) implies (a). Let $i\in\ZZ$ be any index. The main point is that
	\[\arraycolsep=1.4pt\begin{array}{rccc}
		(x\cup-)\colon& \widehat H^i(G,\op{Hom}_\ZZ(X,-)) &\Rightarrow& \widehat H^{i+r}(G,-) \\
		(x^\lor\cup-)\colon& \widehat H^{i+r}(G,-) &\Rightarrow& \widehat H^i(G,\op{Hom}_\ZZ(X,-))
	\end{array}\]
	ought to be inverse natural transformations. More formally, we want to show $(x\cup-)$ is a natural isomorphism, for which we note naturality follows from \autoref{lem:cuppingisnatural}.

	Thus, given a $G$-module $A$, it remains to show that its component morphisms
	\[(x\cup-)\colon \widehat H^i(G,\op{Hom}_\ZZ(X,A))\to\widehat H^{i+r}(G,A).\]
	In fact, we claim that the corresponding map
	\[(x^\lor\cup-)\colon\widehat H^{i+r}(G,A)\to\widehat H^i(G,\op{Hom}_\ZZ(X,A))\]
	is the inverse morphism. We have two checks.
	\begin{itemize}
		\item In one direction, we note that any $a\in\widehat H^{i+r}(G,A)$ has
		\[\big((x\cup-)\circ(x^\lor\cup-)\big)(a)=x\cup (x^\lor\cup a)\stackrel*=(x\cup x^\lor)\cup a=[1]\cup a=a\]
		where $\stackrel*=$ holds by using \autoref{lem:cupassoc} on the following commuting square.
		% https://q.uiver.app/?q=WzAsOCxbMCwwLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsXFxaWilcXG90aW1lc19cXFpaIEEiXSxbMCwxLCJcXFpaXFxvdGltZXNfXFxaWiBBIl0sWzEsMSwiQSJdLFsxLDAsIlhcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooWCxBKSJdLFsyLDAsInlcXG90aW1lcyBmXFxvdGltZXMgYSJdLFsyLDEsImYoeSlcXG90aW1lcyBhIl0sWzMsMSwiZih5KWEiXSxbMywwLCJ5XFxvdGltZXMoeV8wXFxtYXBzdG8gZih5XzApYSkiXSxbMCwxXSxbMCwzXSxbMywyXSxbMSwyXSxbNCw1LCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzQsNywiIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFs3LDYsIiIsMix7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbNSw2LCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
		\[\begin{tikzcd}
			{X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ A} & {X\otimes_\ZZ\op{Hom}_\ZZ(X,A)} & {y\otimes f\otimes b} & {y\otimes(y_0\mapsto f(y_0)b)} \\
			{\ZZ\otimes_\ZZ A} & A & {f(y)\otimes b} & {f(y)b}
			\arrow[from=1-1, to=2-1]
			\arrow[from=1-1, to=1-2]
			\arrow[from=1-2, to=2-2]
			\arrow[from=2-1, to=2-2]
			\arrow[maps to, from=1-3, to=2-3]
			\arrow[maps to, from=1-3, to=1-4]
			\arrow[maps to, from=1-4, to=2-4]
			\arrow[maps to, from=2-3, to=2-4]
		\end{tikzcd}\]
		\item In the other direction, we note that $a^\lor\in\widehat H^i(G,\op{Hom}_\ZZ(X,A))$ will have
		\[\big((x^\lor\cup-)\circ(x\cup-)\big)(a^\lor)=x^\lor\cup (x\cup a)\stackrel*=(x^\lor\cup x)\cup a=[\id_X]\cup a=\id_X(a)=a,\]
		where $\stackrel*=$ holds by using \autoref{lem:cupassoc} on the following commuting square.
		% https://q.uiver.app/?q=WzAsOCxbMCwwLCJcXG9we0hvbX1fXFxaWihYLFxcWlopXFxvdGltZXNfXFxaWiBYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMCwxLCJcXG9we0hvbX1fXFxaWihYLFgpXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMSwxLCJcXG9we0hvbX1fXFxaWihYLEEpIl0sWzEsMCwiXFxvcHtIb219X1xcWlooWCxcXFpaKVxcb3RpbWVzX1xcWlogQSJdLFsyLDAsImZcXG90aW1lcyB5XFxvdGltZXMgZyJdLFszLDAsImZcXG90aW1lcyBnKHkpIl0sWzMsMSwiXFxiaWcoeV8wXFxtYXBzdG8gZih5XzApZyh5KVxcYmlnKSJdLFsyLDEsIih5XzBcXG1hcHN0byBmKHlfMCl5KVxcb3RpbWVzIGciXSxbMCwxXSxbMCwzXSxbMywyXSxbMSwyXSxbNCw3XSxbNCw1XSxbNSw2XSxbNyw2XV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
		\[\begin{tikzcd}[{column sep=7pt}]
			{\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ X\otimes_\ZZ\op{Hom}_\ZZ(X,A)} & {\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ A} & {f\otimes y\otimes g} & {f\otimes g(y)} \\
			{\op{Hom}_\ZZ(X,X)\otimes_\ZZ\op{Hom}_\ZZ(X,A)} & {\op{Hom}_\ZZ(X,A)} & {(y_0\mapsto f(y_0)y)\otimes g} & {\big(y_0\mapsto f(y_0)g(y)\big)}
			\arrow[from=1-1, to=2-1]
			\arrow[from=1-1, to=1-2]
			\arrow[from=1-2, to=2-2]
			\arrow[from=2-1, to=2-2]
			\arrow[from=1-3, to=2-3]
			\arrow[from=1-3, to=1-4]
			\arrow[from=1-4, to=2-4]
			\arrow[from=2-3, to=2-4]
		\end{tikzcd}\]
	\end{itemize}
	This finishes the proof.
\end{proof}
We quickly note that the proof of \autoref{prop:intdualelement} actually managed to conjure the inverse natural transformation to $(x\cup-)$.
\begin{cor} \label{cor:cuppingisinverse}
	Let $G$ be a finite group, and let $X$ be an $r$-encoding module. Constructing $x\in\widehat H^r(G,X)$ and $x^\lor\in\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))$ from \autoref{prop:intdualelement}, the natural transformations
	\[\arraycolsep=1.4pt\begin{array}{rccc}
		(x\cup-)\colon& \widehat H^i(G,\op{Hom}_\ZZ(X,-)) &\to& \widehat H^{i+r}(G,-) \\
		(x^\lor\cup-)\colon& \widehat H^{i+r}(G,-) &\to& \widehat H^i(G,\op{Hom}_\ZZ(X,-))
	\end{array}\]
	are inverse for each $i\in\ZZ$.
\end{cor}
\begin{proof}
	In the proof, we showed that, given a $G$-module $A$, the morphisms
	\[(x^\lor\cup-)\colon\widehat H^{i+r}(G,A) \to \widehat H^i(G,\op{Hom}_\ZZ(X,A))\]
	provide the inverses for $(x\cup-)$. This is what we wanted.
	% The case of $i=0$ follows directly from the proof of \autoref{prop:intdualelement}. The general case follows by literally shifting all the indices in the proof of \autoref{prop:intdualelement} away from $i=0$ to a general $i\in\ZZ$; nothing in the logic changes.
\end{proof}
As such, we will give the element $x^\lor$ a name.
\begin{definition}
	Let $G$ be a finite group and $X$ an $r$-encoding module. Element $x^\lor\in\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))$ as constructed in \autoref{prop:intdualelement} are \textit{dual elements}.
\end{definition}
Here is another amusing corollary we get from this.
\begin{cor} \label{cor:encodingsubgroups}
	Let $G$ be a finite group, and let $X$ be an $r$-encoding module with encoding element $x\in\widehat H^r(G,X)$. Then, for any subgroup $H\subseteq G$, $X$ is an $r$-encoding $H$-module so that any index $i\in\ZZ$ has the natural isomorphism
	\[(\op{Res}x\cup-)\colon\widehat H^i(H,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{i+r}(H,-).\]
\end{cor}
\begin{proof}
	The point is that restriction commutes with cup products, so we may use \autoref{prop:intdualelement}. Indeed, we are given $x\in\widehat H^r(G,X)$ and $x^\lor\in\widehat H^{-r}(G,\op{Hom}_\ZZ(X,X))$ such that
	\[x\cup x^\lor=[1]\in\widehat H^0(G,\ZZ)\qquad\text{and}\qquad x^\lor\cup x=[{\id_X}]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X)).\]
	Applying restriction to $H$ everywhere, we see
	\begin{align*}
		\op{Res}x\cup\op{Res}x^\lor &= \op{Res}(x\cup x^\lor) \\
		&= \op{Res}([1]) \\
		&= [1]\in\widehat H^0(H,\ZZ),
	\end{align*}
	and
	\begin{align*}
		\op{Res}x^\lor\cup\op{Res}x &= \op{Res}(x^\lor\cup x) \\
		&= \op{Res}([{\id_X}]) \\
		&= [{\id_X}]\in\widehat H^0(H,\op{Hom}_\ZZ(X,X)),
	\end{align*}
	which is enough by \autoref{prop:intdualelement} to show that $X$ is an $r$-encoding $H$-module. The remarks from \autoref{cor:cuppingisinverse} explain why the needed isomorphism is given by $(\op{Res}x\cup-)$.
\end{proof}
% \begin{remark}
% 	The constraint that $p$ be even is not too strict. Namely, if $X$ is a $p$-encoding module, then we have natural isomorphisms
% 	\[\widehat H^i(G,\op{Hom}_\ZZ(X\otimes_\ZZ X,-))\simeq\widehat H^i(G,\op{Hom}_\ZZ(X,\op{Hom}_\ZZ(X,-)))\simeq\widehat H^{i+p}(G,\op{Hom}_\ZZ(X,-))\simeq\widehat H^{i+2p}(G,-),\]
% 	so $X\otimes_\ZZ X$ is a $2p$-encoding module.
% \end{remark}
\begin{remark}
	Essentially the same proof should hold for inflation.
\end{remark}
\begin{example}
	It is not true that, if $X$ is an $r$-encoding $G_p$-module for all Sylow $p$-subgroups $G_p\subseteq G$, then $X$ is an $r$-encoding $G$-module. Indeed, take $X=\ZZ$ and $G=S_3$: all Sylow $p$-subgroups of $S_3$ are cyclic, so $\ZZ$ is a $2$-encoding module for all these subgroups. However, $S_3$ is not cyclic, so
	\[\widehat H^{-2}(G,\op{Hom}_\ZZ(X,\ZZ))\simeq\widehat H^{-2}(G,\ZZ)\simeq S_3/[S_3,S_3]\not\cong\ZZ/6\ZZ=\widehat H^0(G,\ZZ).\]
\end{example}

\subsection{Encoding by Tensoring}
It turns out that we can also encode ``on the other side,'' in the following sense.
\begin{theorem} \label{thm:tensorencode}
	Let $G$ be a finite group, and let $X$ be an $r$-encoding module with encoding element $x\in\widehat H^r(G,X)$. Then the cup products
	\[(-\cup x)\colon\widehat H^i(G,-)\Rightarrow\widehat H^{i+r}(G,-\otimes_\ZZ X)\]
	assemble into a natural isomorphism for any $i\in\ZZ$.
\end{theorem}
\begin{proof}
	That we have a natural transformation follows from the naturality of cup products. Thus, it suffices to pick up a $G$-module $A$ and show that the component morphisms
	\[(-\cup x)\colon\widehat H^i(G,A)\to\widehat H^{i+r}(G,A\otimes_\ZZ X)\]
	is an isomorphism. For this, we pick up a dual element $x^\lor\in\widehat H^{i+r}(G,\op{Hom}_\ZZ(X,\ZZ))$ so that
	\[x\cup x^\lor=[1]\in\widehat H^0(G,\ZZ)\qquad\text{and}\qquad x^\lor\cup x=[{\id_X}]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X)).\]
	As such, we claim that the morphisms
	\[\arraycolsep=1.4pt\begin{array}{rccc}
		(-\cup x)\colon& \widehat H^i(G,A) &\to& \widehat H^{i+r}(G,A\otimes_\ZZ X) \\
		(-\cup x^\lor)\colon& \widehat H^{i+r}(G,A\otimes_\ZZ X) &\to& \widehat H^i(G,A)
	\end{array}\]
	are inverse, which will finish; here $(-\cup x^\lor)$ is using the following evaluation map.
	\[\arraycolsep=1.4pt\begin{array}{clclccc}
		(A&\otimes_\ZZ& X)&\otimes_\ZZ&\op{Hom}_\ZZ(X,\ZZ) &\to& A \\
		b &\otimes& y &\otimes& f &\mapsto& f(y)b
	\end{array}\]
	We have now checks for our morphisms to be inverse.
	\begin{itemize}
		\item On one hand, pick up $a\in\widehat H^i(G,A)$. Then we can use \autoref{lem:cupassoc} on the commuting square
		% https://q.uiver.app/?q=WzAsOCxbMCwwLCJBXFxvdGltZXNfXFxaWiBYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsXFxaWikiXSxbMSwxLCJBIl0sWzEsMCwiQVxcb3RpbWVzX1xcWlpcXFpaIl0sWzAsMSwiQVxcb3RpbWVzX1xcWlogWFxcb3RpbWVzX1xcWlpcXG9we0hvbX1fXFxaWihYLFxcWlopIl0sWzIsMCwiYlxcb3RpbWVzIHlcXG90aW1lcyBmIl0sWzIsMSwiYlxcb3RpbWVzIHlcXG90aW1lcyBmIl0sWzMsMSwiZih5KWIiXSxbMywwLCJiXFxvdGltZXMgZih5KSJdLFswLDMsIiIsMix7ImxldmVsIjoyLCJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJub25lIn19fV0sWzMsMV0sWzIsMV0sWzAsMl0sWzQsNSwiIiwwLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbNSw2LCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzQsNywiIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFs3LDYsIiIsMix7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
		\[\begin{tikzcd}
			{A\otimes_\ZZ X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)} & {A\otimes_\ZZ\ZZ} & {b\otimes y\otimes f} & {b\otimes f(y)} \\
			{A\otimes_\ZZ X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)} & A & {b\otimes y\otimes f} & {f(y)b}
			\arrow[Rightarrow, no head, from=1-1, to=2-1]
			\arrow[from=2-1, to=2-2]
			\arrow[from=1-2, to=2-2]
			\arrow[from=1-1, to=1-2]
			\arrow[Rightarrow, no head, from=1-3, to=2-3]
			\arrow[maps to, from=2-3, to=2-4]
			\arrow[maps to, from=1-3, to=1-4]
			\arrow[maps to, from=1-4, to=2-4]
		\end{tikzcd}\]
		to evaluate
		\[\big((-\cup x^\lor)\circ(-\cup x)\big)(a)=(a\cup x)\cup x^\lor=a\cup(x\cup x^\lor)=a\cup[1]=a.\]
		\item On the other hand, pick up $a^\lor\in\widehat H^{i+r}(G,A\otimes_\ZZ X)$. Then we can use \autoref{lem:cupassoc} on the commuting square
		% https://q.uiver.app/?q=WzAsOCxbMCwwLCIoQVxcb3RpbWVzX1xcWlogWClcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooWCxcXFpaKVxcb3RpbWVzX1xcWlogWCJdLFswLDEsIihBXFxvdGltZXNfXFxaWiBYKVxcb3RpbWVzX1xcWlpcXG9we0hvbX1fXFxaWihYLFgpIl0sWzEsMSwiQVxcb3RpbWVzX1xcWlogWCJdLFsxLDAsIkFcXG90aW1lc19cXFpaIFgiXSxbMiwwLCJiXFxvdGltZXMgeVxcb3RpbWVzIGZcXG90aW1lcyB5JyJdLFsyLDEsImJcXG90aW1lcyB5XFxvdGltZXMoeV8wXFxtYXBzdG8gZih5XzApeScpIl0sWzMsMCwiZih5KWJcXG90aW1lcyB5JyJdLFszLDEsImJcXG90aW1lcyBmKHkpeSciXSxbMCwxXSxbMSwyXSxbMCwzXSxbMywyLCIiLDIseyJsZXZlbCI6Miwic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFs0LDUsIiIsMix7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbNSw3LCIiLDIseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzQsNiwiIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFs2LDcsIiIsMCx7ImxldmVsIjoyLCJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJub25lIn19fV1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
		\[\begin{tikzcd}
			{(A\otimes_\ZZ X)\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ X} & {A\otimes_\ZZ X} & {b\otimes y\otimes f\otimes y'} & {f(y)b\otimes y'} \\
			{(A\otimes_\ZZ X)\otimes_\ZZ\op{Hom}_\ZZ(X,X)} & {A\otimes_\ZZ X} & {b\otimes y\otimes(y_0\mapsto f(y_0)y')} & {b\otimes f(y)y'}
			\arrow[from=1-1, to=2-1]
			\arrow[from=2-1, to=2-2]
			\arrow[from=1-1, to=1-2]
			\arrow[Rightarrow, no head, from=1-2, to=2-2]
			\arrow[maps to, from=1-3, to=2-3]
			\arrow[maps to, from=2-3, to=2-4]
			\arrow[maps to, from=1-3, to=1-4]
			\arrow[Rightarrow, no head, from=1-4, to=2-4]
		\end{tikzcd}\]
		to evaluate
		\[\big((-\cup x)\circ(-\cup x^\lor)\big)(a)=(a\cup x^\lor)\cup x=a^\lor\cup(x^\lor\cup x)=a^\lor\cup[{\id_X}]=a^\lor.\]
	\end{itemize}
	The above checks complete the proof.
\end{proof}
\begin{remark} \label{rem:bighandwave}
	One could rebuild the theory we have in the previous sections, in particular showing that all natural isomorphisms of the form
	\[\widehat H^i(G,-\otimes_\ZZ A)\Rightarrow\widehat H^{i+r}(G,-\otimes_\ZZ B)\]
	are cup products from an element of $\widehat H^r(G,\op{Hom}_\ZZ(A,B))$. Thus, for some $G$-module $X$, natural isomorphisms
	\[\widehat H^i(G,-)\Rightarrow\widehat H^{i+r}(G,-\otimes_\ZZ X)\]
	promise $x\in\widehat H^r(G,X)$ (from using $A=\ZZ$ and $B=X$ with $i=0$) and $x^\lor\in\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))$ (from using $A=X$ and $B=\ZZ$ with $i=-r$) which we can evaluate to have
	\[x\cup x^\lor=[1]\in\widehat H^0(G,\ZZ)\qquad\text{and}\qquad x^\lor\cup x=[{\id_X}]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X)).\]
	Namely, $X$ is an $r$-encoding module!
\end{remark}
\begin{cor}
	Let $G$ be a finite group, and let $X$ be an $r$-encoding module with encoding element $x\in\widehat H^r(G,X)$. Then the cup products
	\[(-\cup x)\colon\widehat H^i(G,\ZZ)\to\widehat H^{i+r}(G,X)\]
	are isomorphisms for all $i\in\ZZ$.
\end{cor}
\begin{proof}
	Plug in $\ZZ$ into \autoref{thm:tensorencode}.
\end{proof}

\subsection{Torsion-Free Encoding}
In the theory of periodic cohomology, one can show that it is enough to check the single cohomology group
\[\widehat H^r(G,\ZZ)\cong\ZZ/\#G\ZZ\]
for some index $r\in\ZZ$ to get $r$-periodic cohomology. We might hope that something similar is true for our $r$-encoding modules.
% \autoref{prop:ceduality} was able to provide us with some duality for $\widehat H^p(G,X)$, which enabled us to prove that $\widehat H^p(G,X)\simeq\ZZ/\#G\ZZ$. However, we saw in \autoref{prop:intdualelement}, that somehow the correct dual element is supposed to live in $\widehat H^{-p}(G,\op{Hom}_\ZZ(X,\ZZ))$.
%
% Thus, we might hope that if we can go find $x\in\widehat H^p(G,X)$ and its dual element $x^\lor\in\widehat H^p(G,\op{Hom}_\ZZ(X,\ZZ))$, then we could actually recover the fact that $X$ is a $p$-encoding module.
To this end, we pick up the following ``integral'' duality statement.
\begin{proposition} \label{prop:abstractintegralduality}
	Let $G$ be a finite group, and let $X$ be a $\ZZ$-free $G$-module. Then the cup-product pairing induces an isomorphism
	\[\widehat H^i(G,\op{Hom}_\ZZ(X,\ZZ))\to\op{Hom}_\ZZ\left(\widehat H^{-i}(G,X),\widehat H^0(G,\ZZ)\right)\]
	for all $i\in\ZZ$. Indeed, this is a duality upon identifying $\widehat H^0(G,\ZZ)$ with $\frac1{\#G}\ZZ/\ZZ\subseteq\QQ/\ZZ$.
\end{proposition}
\begin{proof}
	This proof is analogous to \cite[Theorem~XII.6.6]{cartan-eilenberg}. The key to the proof is the short exact sequence
	\begin{equation}
		0\to\ZZ\to\QQ\to\QQ/\ZZ\to0. \label{eq:divisibleses}
	\end{equation}
	The main point is that $X$ being $\ZZ$-free implies that $X$ is projective (as an abelian group), so we can apply $\op{Hom}_\ZZ(X,-)$ to get out the short exact sequence
	\begin{equation}
		0\to\op{Hom}_\ZZ(X,\ZZ)\to\op{Hom}_\ZZ(X,\QQ)\to\op{Hom}_\ZZ(X,\QQ/\ZZ)\to0. \label{eq:homdivisibleses}
	\end{equation}
	Now, note that the multiplication-by-$n$ endomorphism on $\op{Hom}_\ZZ(X,\QQ)$ is an isomorphism (namely, $\QQ$ is a divisible abelian group), so the same will be true of $\widehat H^i(G,\op{Hom}_\ZZ(X,\QQ))$ for any $i\in\ZZ$. However, these cohomology groups must be $\#G$-torsion, so in fact $\widehat H^i(G,\op{Hom}_\ZZ(X,\QQ))=0$ for all $i\in\ZZ$.

	Similarly, we note that we can hit \autoref{eq:homdivisibleses} with the functor $-\otimes_\ZZ X$ to get another short exact sequence
	\begin{equation}
		0\to\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ X\to\op{Hom}_\ZZ(X,\QQ)\otimes_\ZZ X\to\op{Hom}_\ZZ(X,\QQ/\ZZ)\otimes_\ZZ X\to0. \label{eq:tensorhomdivisibleses}
	\end{equation}
	Notably, this is exact because $X$ is $\ZZ$-free and hence flat as a $\ZZ$-module. Now, $\op{Hom}_\ZZ(X,\QQ)\otimes_\ZZ X$ is still a divisible abelian group, so again $\widehat H^i(G,\op{Hom}_\ZZ(X,\QQ))=0$ for all $i\in\ZZ$.

	The rest of the proof is tracking boundary morphisms around. Fix some $i\in\ZZ$. Note \autoref{eq:divisibleses} and \autoref{eq:homdivisibleses} and \autoref{eq:tensorhomdivisibleses} induce boundary isomorphisms
	\[\arraycolsep=1.4pt\begin{array}{rccc}
		\delta \colon& \widehat H^{-1}(G,\QQ/\ZZ) &\to& \widehat H^0(G,\ZZ) \\
		\delta_h \colon& \widehat H^{i-1}(G,\op{Hom}_\ZZ(X,\QQ/\ZZ))&\to&\widehat H^i(G,\op{Hom}_\ZZ(X,\ZZ)) \\
		\delta_t \colon& \widehat H^{-1}(G,\op{Hom}_\ZZ(\QQ/\ZZ)\otimes_\ZZ X)&\to&\widehat H^0(G,\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ X).
	\end{array}\]
	We also note that we have a morphism of short exact sequences
	% https://q.uiver.app/?q=WzAsMTAsWzAsMCwiMCJdLFsxLDAsIlxcb3B7SG9tfV9cXFpaKFgsXFxaWilcXG90aW1lc19cXFpaIFgiXSxbMiwwLCJcXG9we0hvbX1fXFxaWihYLFxcUVEpXFxvdGltZXNfXFxaWiBYIl0sWzMsMCwiXFxvcHtIb219X1xcWlooWCxcXFFRL1xcWlopXFxvdGltZXNfXFxaWiBYIl0sWzAsMSwiMCJdLFs0LDAsIjAiXSxbNCwxLCIwIl0sWzEsMSwiXFxaWiJdLFsyLDEsIlxcUVEiXSxbMywxLCJcXFFRL1xcWloiXSxbMCwxXSxbMSwyXSxbMiwzXSxbMyw1XSxbNCw3XSxbNyw4XSxbOCw5XSxbOSw2XSxbMSw3LCJcXGV0YV9cXFpaIiwyXSxbMiw4LCJcXGV0YV9cXFFRIiwyXSxbMyw5LCJcXGV0YV97XFxRUS9cXFpafSIsMl1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		0 & {\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ X} & {\op{Hom}_\ZZ(X,\QQ)\otimes_\ZZ X} & {\op{Hom}_\ZZ(X,\QQ/\ZZ)\otimes_\ZZ X} & 0 \\
		0 & \ZZ & \QQ & {\QQ/\ZZ} & 0
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-2, to=1-3]
		\arrow[from=1-3, to=1-4]
		\arrow[from=1-4, to=1-5]
		\arrow[from=2-1, to=2-2]
		\arrow[from=2-2, to=2-3]
		\arrow[from=2-3, to=2-4]
		\arrow[from=2-4, to=2-5]
		\arrow["{\eta_\ZZ}"', from=1-2, to=2-2]
		\arrow["{\eta_\QQ}"', from=1-3, to=2-3]
		\arrow["{\eta_{\QQ/\ZZ}}"', from=1-4, to=2-4]
	\end{tikzcd}\]
	where the $\eta_\bullet$ are evaluation maps.
	% For peace of mind, we can check that the squares commute by the following lemma.
	% \begin{lemma} \label{lem:evcommutes}
	% 	Let $G$ be a group and $A,B,C$ be $G$-modules with a $G$-module homomorphism $\varphi\colon B\to C$. Then the diagram
	% 	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJBXFxvdGltZXNfXFxaWlxcb3B7SG9tfShBLEIpIl0sWzEsMCwiQVxcb3RpbWVzX1xcWlooQSxDKSJdLFswLDEsIkIiXSxbMSwxLCJDIl0sWzAsMSwiXFx2YXJwaGkiXSxbMiwzLCJcXHZhcnBoaSJdLFswLDJdLFsxLDNdXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% 	\[\begin{tikzcd}
	% 		{A\otimes_\ZZ\op{Hom}_\ZZ(A,B)} & {A\otimes_\ZZ\op{Hom}_\ZZ(A,C)} \\
	% 		B & C
	% 		\arrow["\varphi", from=1-1, to=1-2]
	% 		\arrow["\varphi", from=2-1, to=2-2]
	% 		\arrow[from=1-1, to=2-1]
	% 		\arrow[from=1-2, to=2-2]
	% 	\end{tikzcd}\]
	% 	commutes, where the vertical homomorphisms are evaluation.
	% \end{lemma}
	% \begin{proof}
	% 	We simply pick up some $a\otimes f\in A\otimes_\ZZ\op{Hom}_\ZZ(A,B)$ and track through
	% 	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJhXFxvdGltZXMgZiJdLFsxLDAsImFcXG90aW1lc1xcdmFycGhpXFxjaXJjIGYiXSxbMCwxLCJmKGEpIl0sWzEsMSwiXFx2YXJwaGkoZihhKSkiXSxbMCwxLCJcXHZhcnBoaSIsMCx7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbMiwzLCJcXHZhcnBoaSIsMCx7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbMCwyLCIiLDEseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzEsMywiIiwxLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	% 	\[\begin{tikzcd}
	% 		{a\otimes f} & {a\otimes\varphi\circ f} \\
	% 		{f(a)} & {\varphi(f(a))}
	% 		\arrow["\varphi", maps to, from=1-1, to=1-2]
	% 		\arrow["\varphi", maps to, from=2-1, to=2-2]
	% 		\arrow[maps to, from=1-1, to=2-1]
	% 		\arrow[maps to, from=1-2, to=2-2]
	% 	\end{tikzcd}\]
	% 	which finishes the proof.
	% \end{proof}
	Now, \autoref{prop:ceduality} tells us that
	\[\arraycolsep=1.4pt\begin{array}{ccc}
		\widehat H^{i-1}(G,\op{Hom}_\ZZ(X,\QQ/\ZZ)) &\to& \op{Hom}_\ZZ\left(\widehat H^{-i}(G,X),\widehat H^{-1}(G,\QQ/\ZZ)\right) \\
		a &\mapsto& (b\mapsto\eta_{\QQ/\ZZ}(a\cup b))
	\end{array}\]
	is an isomorphism. Composing this with various other isomorphisms, we can build the isomorphism
	\[\arraycolsep=1.4pt\begin{array}{ccccccc}
		\widehat H^i(G,X^\lor) &\to& \widehat H^{i-1}(G,X^*) &\to& \op{Hom}\left(\widehat H^{-i}(G,X),\widehat H^{-1}(G,\QQ/\ZZ)\right) &\to& \op{Hom}\left(\widehat H^{-i}(G,X),\widehat H^0(G,\QQ/\ZZ)\right)  \\
		a &\mapsto& \delta_h^{-1}a &\mapsto& \left(b\mapsto\eta_{\QQ/\ZZ}(\delta_h^{-1}a\cup b)\right) &\mapsto& \left(b\mapsto\delta\eta_{\QQ/\ZZ}(\delta_h^{-1}a\cup b)\right)
	\end{array}\]
	where $X^\lor\coloneqq\op{Hom}_\ZZ(X,\ZZ)$ and $X^*\coloneqq\op{Hom}_\ZZ(X,\QQ/\ZZ)$, for brevity. This gives an isomorphism between the desired objects, but to prove the result we need to show that the above map is $a\mapsto(b\mapsto\eta_\ZZ(a\cup b))$. Well, given $a\in\widehat H^i(G,\op{Hom}_\ZZ(X,\ZZ))$ and $b\in\widehat H^{-i}(G,X)$, properties of the boundary morphisms tells us
	\begin{align*}
		\delta\eta_{\QQ/\ZZ}\left(\delta_h^{-1}a\cup b\right) &= \eta_\ZZ\delta_t\left(\delta_h^{-1}a\cup b\right) \\
		&= \eta_\ZZ\left(\delta_h\delta_h^{-1}a\cup b\right) \\
		&= \eta_\ZZ(a\cup b),
	\end{align*}
	which is what we wanted.
\end{proof}
\begin{remark}
	The hypothesis that $X$ be $\ZZ$-free is necessary: the statement is false for $X=\ZZ/\#G\ZZ$ and $i=0$, for example.
\end{remark}
And here is our result.
\begin{prop} \label{prop:finitecohomcheck}
	Let $G$ be a finite group, and let $X$ be a $\ZZ$-free $G$-module. The following are equivalent.
	\begin{listalph}
		\item $X$ is an $r$-encoding module.
		\item $\widehat H^r(G,X)\cong\ZZ/\#G\ZZ$ and $\widehat H^0(G,\op{Hom}_\ZZ(X,X))\cong\ZZ/\#G\ZZ$.
		\item $\widehat H^r(G,X)\cong\ZZ/\#G\ZZ$ and $\widehat H^0(G,\op{Hom}_\ZZ(X,X))$ is cyclic.
	\end{listalph}
\end{prop}
\begin{proof}
	For brevity, set $n\coloneqq\#G$. That (a) implies (b) is not hard: \autoref{cor:hpxcomputation} tells us that $\widehat H^r(G,X)\cong\ZZ/n\ZZ$, and then being an $r$-encoding module promises an isomorphism
	\[\widehat H^0(G,\op{Hom}_\ZZ(X,X))\simeq\widehat H^r(G,X)\cong\ZZ/n\ZZ.\]
	Continuing, we see that (b) implies (c) easily. Thus, the interesting direction is showing that (c) implies (a).
	
	For this, we use \autoref{prop:abstractintegralduality} and \autoref{prop:intdualelement}. We are given $x\in\widehat H^r(G,X)$ of order $n$, so we note that there is a morphism
	\[\widehat H^r(G,X)\simeq\ZZ/n\ZZ=\widehat H^0(G,\ZZ)\]
	sending $x$ to $[1]$. Thus, \autoref{prop:abstractintegralduality} grants $x^\lor\in\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))$ such that
	\[x\cup x^\lor=[1]\in\widehat H^0(G,\ZZ).\]
	It remains to check that $x^\lor\cup x=[{\id_X}]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X))$. This is more difficult.

	For this, we will show that
	\begin{equation}
		(x\cup-)\colon\widehat H^0(G,\op{Hom}_\ZZ(X,X))\to\widehat H^r(G,X) \label{eq:babycuptoupgrade}
	\end{equation}
	is injective while showing that $x^\lor\cup x$ and ${\id_X}$ have the same image under $(x\cup-)$.
	
	Indeed, on one hand, let $A$ be a $G$-module (which we will set to be $X$ shortly), and we claim that the composite
	\[\widehat H^r(G,A)\stackrel{x^\lor\cup-}\to\widehat H^0(G,\op{Hom}_\ZZ(X,A))\stackrel{x\cup-}\to\widehat H^r(G,A)\]
	is the identity. Then the commutativity of the diagram
	% https://q.uiver.app/?q=WzAsOCxbMCwwLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsXFxaWilcXG90aW1lc19cXFpaIEEiXSxbMSwwLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMCwxLCJcXFpaXFxvdGltZXNfXFxaWiBBIl0sWzEsMSwiQSJdLFsyLDAsInhfMFxcb3RpbWVzIGZcXG90aW1lcyBhXzAiXSxbMywwLCJ4XzBcXG90aW1lc1xcYmlnKHlcXG1hcHN0byBmKHkpYV8wXFxiaWcpIl0sWzIsMSwiZih4XzApXFxvdGltZXMgYV8wIl0sWzMsMSwiZih4XzApYV8wIl0sWzAsMl0sWzIsM10sWzAsMV0sWzEsM10sWzQsNiwiIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFs2LDcsIiIsMix7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbNCw1LCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzUsNywiIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ A} & {X\otimes_\ZZ\op{Hom}_\ZZ(X,A)} & {x_0\otimes f\otimes a_0} & {x_0\otimes\big(y\mapsto f(y)a_0\big)} \\
		{\ZZ\otimes_\ZZ A} & A & {f(x_0)\otimes a_0} & {f(x_0)a_0}
		\arrow[from=1-1, to=2-1]
		\arrow[from=2-1, to=2-2]
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-2, to=2-2]
		\arrow[maps to, from=1-3, to=2-3]
		\arrow[maps to, from=2-3, to=2-4]
		\arrow[maps to, from=1-3, to=1-4]
		\arrow[maps to, from=1-4, to=2-4]
	\end{tikzcd}\]
	allows us to compute, for any $a\in\widehat H^p(G,A)$,
	\begin{equation}
		x\cup x^\lor\cup a=[1]\cup a=a, \label{eq:oneside}
	\end{equation}
	as desired.
	
	Now, taking $A=X$, we note
	\begin{equation}
		x\cup[{\id_X}]=x\in\widehat H^r(G,X). \label{eq:twoside}
	\end{equation}
	So we will be done once we show that \autoref{eq:babycuptoupgrade}is injective. Well, note $[{\id_X}]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X))$ has order $n$: if $k[{\id_X}]=0$, then $0=k(x\cup[{\id_X}])=kx$, so $n\mid k$. Because $\widehat H^0(G,\op{Hom}_\ZZ(X,X))$ is cyclic (by hypothesis!) and $n$-torsion, we conclude that in fact $\widehat H^0(G,\op{Hom}_\ZZ(X,X))$ is cyclic of order $n$ generated by $[{\id_X}]$. Thus, we note that there is a unique isomorphism
	\[\widehat H^0(G,\op{Hom}_\ZZ(X,X))\cong\ZZ/n\ZZ\cong\widehat H^r(G,X)\]
	sending $[{\id_X}]$ to $1$ to $x$, so this isomorphism must be $(x\cup-)$ by \autoref{eq:twoside}; in particular, $(x\cup-)$ is injective.
	
	Finishing up, comparing the injectivity of $(x\cup-)$ with \autoref{eq:oneside} and \autoref{eq:twoside} forces us to conclude that $x^\lor\cup x=[{\id_X}]$. This finishes.
\end{proof}
\begin{example}
	The $\ZZ$-free condition is necessary. As in \autoref{rem:neednaturality}, let $G\coloneqq\ZZ/p\ZZ$ act on $X\coloneqq\ZZ/p\ZZ$ trivially. Then
	\[\widehat H^0(G,\op{Hom}_\ZZ(X,X))\simeq\widehat H^0(G,X)\cong\widehat H^{-1}(G,X)=\ZZ/p\ZZ.\]
	However, $X$ is not a $(-1)$-encoding module because
	\[\widehat H^1(G,\op{Hom}_\ZZ(X,\ZZ))\simeq\widehat H^1(G,0)=0\not\cong\ZZ/p\ZZ=\widehat H^0(G,\ZZ).\]
\end{example}
\begin{remark}
	As we will discuss later in \autoref{rem:almosttorsionfree}, the requirement that $X$ be $\ZZ$-free is not too serious.
\end{remark}
\begin{example}
	To see that $\widehat H^0(G,\op{Hom}_\ZZ(X,X))$ being cyclic is necessary, we use the example from \autoref{ex:ziexample}. Let $G=\langle\sigma\rangle\simeq\ZZ/2\ZZ$ act on $X\coloneqq\ZZ[i]=\ZZ\oplus\ZZ i$ by conjugation. Then
	\[\widehat H^0(G,X)\simeq\widehat H^0(G,\ZZ)\oplus\widehat H^0(G,\ZZ i)\simeq\ZZ/2\ZZ,\]
	but
	\begin{align*}
		\widehat H^0(G,\op{Hom}_\ZZ(X,X)) &\simeq \widehat H^0(G,\op{Hom}_\ZZ(\ZZ,\ZZ))\oplus\widehat H^0(G,\op{Hom}_\ZZ(\ZZ,\ZZ i)) \\
		&\qquad\oplus\widehat H^0(G,\op{Hom}_\ZZ(\ZZ i,\ZZ))\oplus\widehat H^0(G,\op{Hom}_\ZZ(\ZZ i,\ZZ i))
	\end{align*}
	comes out to $\ZZ/2\ZZ\oplus0\oplus0\oplus\ZZ/2\ZZ$. Thus,
	\[\widehat H^0(G,\op{Hom}_\ZZ(X,X))\not\cong\widehat H^0(G,X),\]
	so $X$ is not a $0$-encoding module even though $X$ is $\ZZ$-free and $\widehat H^0(G,X)\cong\ZZ/\#G\ZZ$.
\end{example}
In some sense, the issue with the above example is that we could decompose our $G$-module into $A\oplus B$ when in fact there is no reason to talk about these sorts of $G$-modules as encoding modules.
\begin{cor} \label{cor:indecomposable}
	Let $G$ be a finite $p$-group. If $A\oplus B$ is a finitely generated $\ZZ$-free $r$-encoding module, then one of $A$ or $B$ is an $r$-encoding module and the other is cohomologically equivalent to $0$.
\end{cor}
\begin{proof}
	This follows quickly from the check in \autoref{prop:finitecohomcheck}. On one hand,
	\begin{align*}
		\widehat H^0(G,\op{Hom}_\ZZ(A\oplus B,A\oplus B)) &\simeq \widehat H^0(G,\op{Hom}_\ZZ(A,A))\oplus\widehat H^0(G,\op{Hom}_\ZZ(A,B)) \\
		&\qquad\oplus\widehat H^0(G,\op{Hom}_\ZZ(B,A))\oplus\widehat H^0(G,\op{Hom}_\ZZ(B,B))
	\end{align*}
	tells us that both $\widehat H^0(G,\op{Hom}_\ZZ(A,A))$ and $\widehat H^0(G,\op{Hom}_\ZZ(B,B))$ are both cyclic because $\widehat H^0(G,\op{Hom}_\ZZ(A\oplus B,A\oplus B))$ is.

	On the other hand, we note
	\[\widehat H^r(G,A)\oplus\widehat H^r(G,B)\simeq\widehat H^r(G,A\oplus B)\cong\ZZ/\#G\ZZ,\]
	so we are forced to have $\widehat H^r(G,A)\cong\ZZ/\#G\ZZ$ or $\widehat H^r(G,B)\cong\ZZ/\#G\ZZ$ because $G$ is a finite $p$-group.

	Thus, one of $A$ or $B$ is an $r$-encoding module; without loss of generality, say that $A$ is. It remains to show that $B$ is cohomologically equivalent to $0$. Well, we have
	\[\widehat H^0(G,\op{Hom}_\ZZ(A,A))\cong\widehat H^r(G,A)=\ZZ/\#G\ZZ\]
	because $A$ is an $r$-encoding module, so the embedding
	\[\underbrace{\widehat H^0(G,\op{Hom}_\ZZ(A,A))}_{\ZZ/\#G\ZZ}\oplus\widehat H^0(G,\op{Hom}_\ZZ(B,B))\subseteq\underbrace{\widehat H^0(G,\op{Hom}_\ZZ(A\oplus B,A\oplus B))}_{\ZZ/\#G\ZZ}\]
	forces $\widehat H^0(G,\op{Hom}_\ZZ(B,B))=0$. As such, \autoref{cor:bettercohomequivzero} finishes.
\end{proof}
\begin{remark}
	It is conceivable that \autoref{cor:indecomposable} is true without requiring $A\oplus B$ to be $\ZZ$-free nor $G$ to be a $p$-group.
\end{remark}

\subsection{New Encoding Modules From Old}
The goal of this section is to build encoding modules up from smaller ones.
\begin{proposition}
	Let $G$ be a finite group. Given an $r$-encoding module $A$ and an $s$-encoding module $B$, the $G$-module $A\otimes_\ZZ B$ is an $(r+s)$-encoding module.
\end{proposition}
\begin{proof}
	By \autoref{cor:betterencodingdef}, we have natural isomorphisms
	\[\widehat H^0(G,\op{Hom}_\ZZ(A,-))\simeq\widehat H^r(G,-)\qquad\text{and}\qquad\widehat H^r(G,\op{Hom}_\ZZ(B,-))\simeq\widehat H^{r+s}(G,-).\]
	Whiskering, we have a natural isomorphism
	\begin{align*}
		\widehat H^0(G,\op{Hom}_\ZZ(A\otimes_\ZZ B,-)) &\simeq \widehat H^r(G,\op{Hom}_\ZZ(A,\op{Hom}_\ZZ(B,-))) \\
		&\simeq \widehat H^r(G,\op{Hom}_\ZZ(B,-)) \\
		&\simeq \widehat H^{r+s}(G,-),
	\end{align*}
	which is what we wanted.
\end{proof}
\begin{remark}
	With some care, it is possible to use \autoref{cor:multequiv} to show this result. The difficulty in realizing this approach lies in the fact that $r$ and $s$ need not both be nonnegative.
\end{remark}
\begin{proposition} \label{prop:dualmodule}
	Let $G$ be a finite group, and let $X$ be an $r$-encoding module. Then $\op{Hom}_\ZZ(X,\ZZ)$ is a $(-r)$-encoding module.
\end{proposition}
\begin{proof}
	We use \autoref{prop:intdualelement}. For brevity, we set $X^\lor\coloneqq\op{Hom}_\ZZ(X,\ZZ)$ and $X^{\lor\lor}\coloneqq\op{Hom}_\ZZ(X^\lor,\ZZ)$. Observe that there is a (canonical) map $\varphi\colon X\to X^{\lor\lor}$ by
	\[\varphi\colon f\mapsto f\circ\varphi.\]
	By \autoref{prop:intdualelement}, we may find $x\in\widehat H^r(G,X)$ and $x^\lor\in\widehat H^{-r}(G,X^\lor)$ such that
	\[x\cup x^\lor=[1]\in\widehat H^0(G,\ZZ)\qquad\text{and}\qquad x^\lor\cup x=[{\id_X}]\in\widehat H^0(G,\op{Hom}_\ZZ(X,X)).\]
	As such, we set $y\coloneqq x^\lor$ and $y^\lor\coloneqq(-1)^r\varphi(x)$. The commutative diagram
	% https://q.uiver.app/?q=WzAsOCxbMCwwLCJYXFxvdGltZXNfXFxaWiBYXioiXSxbMSwwLCJcXFpaIl0sWzAsMSwiWF57Kip9XFxvdGltZXNfXFxaWiBYXioiXSxbMSwxLCJcXFpaIl0sWzIsMCwieFxcb3RpbWVzIGYiXSxbMiwxLCIoZ1xcbWFwc3RvIGcoeCkpXFxvdGltZXMgZiJdLFszLDAsImYoeCkiXSxbMywxLCJmKHgpIl0sWzEsMywiIiwwLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMCwxXSxbMiwzXSxbMCwyLCJcXHZhcnBoaVxcb3RpbWVze1xcaWR9IiwyXSxbNCw2LCIiLDIseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzQsNSwiIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFs1LDcsIiIsMCx7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbNiw3LCIiLDIseyJsZXZlbCI6Miwic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{X\otimes_\ZZ X^\lor} & \ZZ & {x\otimes f} & {f(x)} \\
		{X^{\lor\lor}\otimes_\ZZ X^\lor} & \ZZ & {(g\mapsto g(x))\otimes f} & {f(x)}
		\arrow[Rightarrow, no head, from=1-2, to=2-2]
		\arrow[from=1-1, to=1-2]
		\arrow[from=2-1, to=2-2]
		\arrow["{\varphi\otimes{\id}}"', from=1-1, to=2-1]
		\arrow[maps to, from=1-3, to=1-4]
		\arrow[maps to, from=1-3, to=2-3]
		\arrow[maps to, from=2-3, to=2-4]
		\arrow[Rightarrow, no head, from=1-4, to=2-4]
	\end{tikzcd}\]
	tells us that we may evaluate
	\[\varphi(x)\cup x^\lor=x\cup x^\lor=[1]\in\widehat H^0(G,\ZZ),\]
	so $y\cup y^\lor=[1]\in\widehat H^0(G,\ZZ)$ after being careful with signs.

	On the other hand, we set $A=B=X$ for clarity and define $\psi\colon\op{Hom}_\ZZ(A,B)\to\op{Hom}_\ZZ(B^*,A^*)$ by
	\[\psi(f)\colon g\mapsto(g\circ f),\]
	yielding the commutative diagram
	% https://q.uiver.app/?q=WzAsOCxbMCwwLCJBXipcXG90aW1lc19cXFpaIEIiXSxbMSwwLCJcXG9we0hvbX1fXFxaWihBLEIpIl0sWzAsMSwiQV4qXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKEJeKixcXFpaKSJdLFsxLDEsIlxcb3B7SG9tfV9cXFpaKEJeKixBXiopIl0sWzIsMCwiZlxcb3RpbWVzIGIiXSxbMywwLCJcXGJpZyhhXFxtYXBzdG8gZihhKWJcXGJpZykiXSxbMiwxLCJmXFxvdGltZXNcXGJpZyhnXFxtYXBzdG8gZyhiKVxcYmlnKSJdLFszLDEsIlxcYmlnKGdcXG1hcHN0byBnKGIpZlxcYmlnKSJdLFsxLDMsIlxccHNpIl0sWzAsMV0sWzAsMiwie1xcaWR9XFxvdGltZXNcXHZhcnBoaSIsMl0sWzIsM10sWzQsNiwiIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFs2LDcsIiIsMCx7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbNSw3LCIiLDIseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzQsNSwiIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{A^\lor\otimes_\ZZ B} & {\op{Hom}_\ZZ(A,B)} & {f\otimes b} & {\big(a\mapsto f(a)b\big)} \\
		{A^\lor\otimes_\ZZ\op{Hom}_\ZZ(B^\lor,\ZZ)} & {\op{Hom}_\ZZ(B^\lor,A^\lor)} & {f\otimes\big(g\mapsto g(b)\big)} & {\big(g\mapsto g(b)f\big)}
		\arrow["\psi", from=1-2, to=2-2]
		\arrow[from=1-1, to=1-2]
		\arrow["{{\id}\otimes\varphi}"', from=1-1, to=2-1]
		\arrow[from=2-1, to=2-2]
		\arrow[maps to, from=1-3, to=2-3]
		\arrow[maps to, from=2-3, to=2-4]
		\arrow[maps to, from=1-4, to=2-4]
		\arrow[maps to, from=1-3, to=1-4]
	\end{tikzcd}\]
	which tells us that we may evaluate
	\[x^\lor\cup\varphi(x)=\psi(x^\lor\cup x)=\psi([\id_X])=[\id_{X^\lor}]\in\widehat H^0(G,\op{Hom}_\ZZ(X^\lor,X^\lor)),\]
	so $y^\lor\cup y=[{\id_{X^\lor}}]$ after being careful with signs. This completes the proof.
\end{proof}
\begin{example} \label{ex:allencoderesexist}
	\autoref{ex:igisencoding} established that $I_G^{\otimes r}$ is an $r$-encoding module for $r\ge0$. As such, $\op{Hom}_\ZZ\left(I_G^{\otimes r},\ZZ\right)$ is a $(-r)$-encoding module for $-r\le0$. Thus, we have established existence for $r$-encoding modules for all $r\in\ZZ$.
\end{example}
\begin{cor} \label{cor:getfreeencoder}
	Let $G$ be a finite group, and let $X$ be a finitely generated $r$-encoding module. Letting $X_t$ denote the $\ZZ$-torsion subgroup of $X$, we have that $X_t$ is a $G$-submodule of $X$, and $X/X_t$ is an $r$-encoding module.
\end{cor}
\begin{proof}
	To see that $X_t$ is a $G$-submodule, we note that any $x\in X_t$ has some $k\in\ZZ$ such that $kx=0$, so any $g\in G$ will have
	\[k\cdot gx=g(kx)=g\cdot0=0.\]
	Thus, $X_t\subseteq X$ is preserved by $G$.

	It remains to show that $X_f\coloneqq X/X_t$ is an $r$-encoding module. To begin, we claim that
	\begin{equation}
		\op{Hom}_\ZZ(\op{Hom}_\ZZ(X,\ZZ),\ZZ)\cong\op{Hom}_\ZZ(\op{Hom}_\ZZ(X_f,\ZZ),\ZZ) \label{eq:isodoubledual}
	\end{equation}
	as $G$-modules; by \autoref{prop:dualmodule}, this will imply that $\op{Hom}_\ZZ(\op{Hom}_\ZZ(X_f,\ZZ),\ZZ)$ is an $r$-encoding module. To see this, we note that the short exact sequence
	\[0\to X_t\to X\to X_f\to 0\]
	becomes the left exact sequence
	\[0\to\op{Hom}_\ZZ(X_f,\ZZ)\to\op{Hom}_\ZZ(X,\ZZ)\to\op{Hom}_\ZZ(X_t,\ZZ).\]
	However, $\op{Hom}_\ZZ(X_t,\ZZ)=0$ because $X_t$ is $\ZZ$-torsion, so the above left exact sequence witnesses the isomorphism $\op{Hom}_\ZZ(X_f,\ZZ)\cong\op{Hom}_\ZZ(X,\ZZ)$. Applying $\op{Hom}_\ZZ(-,\ZZ)$ again yields \autoref{eq:isodoubledual}.

	To finish, we note that
	\[\varphi\colon X_f\to\op{Hom}_\ZZ(\op{Hom}_\ZZ(X_f,\ZZ),\ZZ)\]
	by $x\mapsto(f\mapsto f(x))$ is a $G$-module morphism and isomorphism of abelian groups because $X_f$ is torsion-free and finitely generated. Thus, $\varphi$ is an isomorphism of $G$-modules, implying that $X_f$ is an $r$-encoding module.
\end{proof}
\begin{remark} \label{rem:almosttorsionfree}
	Even though \autoref{ex:notalltorsionfree} asserts that not all $p$-encoding modules $X$ are $\ZZ$-torsion-free, \autoref{cor:getfreeencoder} explains that we can canonically obtain a $\ZZ$-torsion-free $p$-encoding module from $X$ in the form of $\op{Hom}_\ZZ(\op{Hom}_\ZZ(X,\ZZ),\ZZ)\cong X/X_t$.
\end{remark}
\begin{proposition} \label{prop:encodingses}
	Let $G$ be a finite group, and let
	\[0\to X'\to M\to X\to 0\]
	be a $\ZZ$-split short exact sequence such that $M$ is an induced $G$-module. Then $X$ is an $r$-encoding module if and only if $X'$ is an $(r+1)$-encoding module.
\end{proposition}
\begin{proof}
	Given a $G$-module $A$, we recall that $\op{Hom}_\ZZ(-,A)$ is a shiftable functor by \autoref{lem:contravariantshiftable}, so $\op{Hom}_\ZZ(M,A)$ is induced. Now, because the short exact sequence is $\ZZ$-split, we have the short exact sequence
	\[0\to\op{Hom}_\ZZ(X,A)\to\op{Hom}_\ZZ(M,A)\to\op{Hom}_\ZZ(X',A)\to0\]
	which gives the isomorphism
	\[\delta_A\colon\widehat H^0(G,\op{Hom}_\ZZ(X',A))\to\widehat H^1(G,\op{Hom}_\ZZ(X,A))\]
	because $\op{Hom}_\ZZ(M,A)$ is induced. In fact, the $\delta_A$ make a natural isomorphism $\delta_\bullet\colon\widehat H^0(G,\op{Hom}_\ZZ(X',-))\Rightarrow\widehat H^1(G,\op{Hom}_\ZZ(X,-))$: given a $G$-module morphism $f\colon A\to B$, the morphism of short exact sequences
	% https://q.uiver.app/?q=WzAsMTAsWzAsMCwiMCJdLFsxLDAsIlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMiwwLCJcXG9we0hvbX1fXFxaWihNLEEpIl0sWzMsMCwiXFxvcHtIb219X1xcWlooWCcsQSkiXSxbNCwwLCIwIl0sWzEsMSwiXFxvcHtIb219X1xcWlooWCxCKSJdLFsyLDEsIlxcb3B7SG9tfV9cXFpaKE0sQikiXSxbMywxLCJcXG9we0hvbX1fXFxaWihYJyxCKSJdLFs0LDEsIjAiXSxbMCwxLCIwIl0sWzAsMV0sWzEsMl0sWzIsM10sWzMsNF0sWzksNV0sWzUsNl0sWzYsN10sWzcsOF0sWzEsNSwiZiIsMl0sWzIsNiwiZiIsMl0sWzMsNywiZiIsMl1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		0 & {\op{Hom}_\ZZ(X,A)} & {\op{Hom}_\ZZ(M,A)} & {\op{Hom}_\ZZ(X',A)} & 0 \\
		0 & {\op{Hom}_\ZZ(X,B)} & {\op{Hom}_\ZZ(M,B)} & {\op{Hom}_\ZZ(X',B)} & 0
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-2, to=1-3]
		\arrow[from=1-3, to=1-4]
		\arrow[from=1-4, to=1-5]
		\arrow[from=2-1, to=2-2]
		\arrow[from=2-2, to=2-3]
		\arrow[from=2-3, to=2-4]
		\arrow[from=2-4, to=2-5]
		\arrow["f"', from=1-2, to=2-2]
		\arrow["f"', from=1-3, to=2-3]
		\arrow["f"', from=1-4, to=2-4]
	\end{tikzcd}\]
	induces the desired commuting square, as follows.
	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF4wKEcsXFxvcHtIb219X1xcWlooWCcsQSkpIl0sWzEsMCwiXFx3aWRlaGF0IEheMShHLFxcb3B7SG9tfV9cXFpaKFgsQSkpIl0sWzAsMSwiXFx3aWRlaGF0IEheMChHLFxcb3B7SG9tfV9cXFpaKFgnLEIpKSJdLFsxLDEsIlxcd2lkZWhhdCBIXjEoRyxcXG9we0hvbX1fXFxaWihYLEEpKSJdLFswLDEsIlxcZGVsdGFfQSJdLFsyLDMsIlxcZGVsdGFfQiJdLFswLDIsImYiLDJdLFsxLDMsImYiLDJdXQ==&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{\widehat H^0(G,\op{Hom}_\ZZ(X',A))} & {\widehat H^1(G,\op{Hom}_\ZZ(X,A))} \\
		{\widehat H^0(G,\op{Hom}_\ZZ(X',B))} & {\widehat H^1(G,\op{Hom}_\ZZ(X,B))}
		\arrow["{\delta_A}", from=1-1, to=1-2]
		\arrow["{\delta_B}", from=2-1, to=2-2]
		\arrow["f"', from=1-1, to=2-1]
		\arrow["f"', from=1-2, to=2-2]
	\end{tikzcd}\]
	We now proceed with the proof. In one direction, if $X$ is an $r$-encoding module, then \autoref{cor:betterencodingdef} promises us a natural isomorphism
	\[\Phi_\bullet\colon\widehat H^1(G,\op{Hom}_\ZZ(X,-))\Rightarrow\widehat H^{r+1}(G,-),\]
	so the composite
	\[\widehat H^0(G,\op{Hom}_\ZZ(X',-))\stackrel{\delta_\bullet}\Rightarrow\widehat H^1(G,\op{Hom}_\ZZ(X,-))\stackrel{\Phi_\bullet}\Rightarrow\widehat H^{r+1}(G,-)\]
	shows that $X'$ is a $(r+1)$-encoding module. The other direction is analogous, concatenating with $\delta_\bullet^{-1}$.
\end{proof}
\begin{example}
	Fix a finite group $G$ generated by $S\coloneqq\langle\sigma_1,\ldots,\sigma_n\rangle$, and let $M\coloneqq\ZZ[G]^{\#S}$ have basis $\{e_i\}_{i=1}^m$. Then there is a projection $\pi\colon\ZZ[G]^{\#G}\onto I_G$ by sending $e_i\mapsto(\sigma_i-1)$, giving the short exact sequence
	\[0\to\ker\pi\to\ZZ[G]^{\#S}\to I_G\to0.\]
	This short exact sequence is $\ZZ$-split because $I_G$ is $\ZZ$-free. Because $\ZZ[G]^{\#S}\cong\ZZ[G]\otimes_\ZZ\ZZ^{\#S}$ is induced and $I_G$ is a $1$-encoding module, we conclude that $\ker\pi$ is a $2$-encoding module by \autoref{prop:encodingses}.
\end{example}
By this point, we have a wide array of ways of making $p$-encoding modules, so we call it quits here.

\subsection{A Perfect Pairing}
We close this section with a hint of Artin reciprocity. The main goal of this subsection is to prove the following result.
\begin{theorem} \label{thm:abstractperfectpairing}
	Let $G$ be a finite group, and let $X$ and $A$ be $G$-modules and $r\in\ZZ$ be an index. Then, if there exists an element $c\in H^r(G,X)$ such that the cup-product maps
	\[\arraycolsep=1.4pt\begin{array}{cccc}
		(c\cup-)\colon&\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))&\to&\widehat H^0(G,\ZZ) \\
		(c\cup-)\colon&\widehat H^0(G,\op{Hom}_\ZZ(X,A))&\to&\widehat H^{r}(G,A)
	\end{array}\]
	are isomorphisms, then the cup-product pairing induces an isomorphism
	\[\widehat H^r(G,A)\to\op{Hom}_\ZZ\left(\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ)),\widehat H^0(G,\op{Hom}_\ZZ(X,A))\right).\]
\end{theorem}
% The main step in the proof is the following lemma.
% \begin{lemma}
% 	Let $G$ be a finite group, and let $X$ and $A$ be $G$-modules. Pick up another $G$-module $A$. Then, given any $i\in\ZZ$ and $c\in\widehat H^p(G,X)$ and $u\in\widehat H^p(G,A)$, the following diagram commutes, where all arrows are cup-product maps.
% 	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJcXHdpZGVoYXQgSF57aS0yfShHLFxcb3B7SG9tfV9cXFpaKFgsXFxaWikpIl0sWzEsMCwiXFx3aWRlaGF0IEheaShHLFxcb3B7SG9tfV9cXFpaKFgsQSkpIl0sWzAsMSwiXFx3aWRlaGF0IEheaShHLFxcWlopIl0sWzEsMSwiXFx3aWRlaGF0IEhee2krMn0oRyxBKSJdLFswLDEsIi1cXGN1cCB1Il0sWzAsMiwiY1xcY3VwLSIsMl0sWzIsMywiLVxcY3VwIHUiLDJdLFsxLDMsImNcXGN1cC0iXV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
% 	\[\begin{tikzcd}
% 		{\widehat H^{i-p}(G,\op{Hom}_\ZZ(X,\ZZ))} & {\widehat H^i(G,\op{Hom}_\ZZ(X,A))} \\
% 		{\widehat H^i(G,\ZZ)} & {\widehat H^{i+p}(G,A)}
% 		\arrow["{-\cup u}", from=1-1, to=1-2]
% 		\arrow["{c\cup-}"', from=1-1, to=2-1]
% 		\arrow["{-\cup u}"', from=2-1, to=2-2]
% 		\arrow["{c\cup-}", from=1-2, to=2-2]
% 	\end{tikzcd}\]
% \end{lemma}
% \begin{proof}
% 	Formally, our cup-product maps are induced by the following ``evaluation morphisms.''
% 	\begin{itemize}
% 		\item For the left arrow, we have $\eta_L\colon X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)\to\ZZ$ by evaluation.
% 		\item For the top arrow, we have $\eta_T\colon\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ A\to\op{Hom}_\ZZ(X,A)$ by $f\otimes a\mapsto(x\mapsto f(x)a)$.
% 		\item For the bottom arrow, we have $\eta_B\colon\ZZ\otimes_\ZZ A\to A$ by $k\otimes a\mapsto ka$.
% 		\item For the right arrow, we have $\eta_R\colon X\otimes_\ZZ\op{Hom}_\ZZ(X,A)\to A$ by evaluation.
% 	\end{itemize}
% 	In particular, these maps are defined so that the following diagram commutes.
% 	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsXFxaWilcXG90aW1lc19cXFpaIEEiXSxbMSwwLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMCwxLCJcXFpaXFxvdGltZXNfXFxaWiBBIl0sWzEsMSwiQSJdLFswLDEsIlxcZXRhX1QiXSxbMCwyLCJcXGV0YV9MIiwyXSxbMSwzLCJcXGV0YV9SIl0sWzIsMywiXFxldGFfQiIsMl1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
% 	\begin{equation}
% 		\begin{tikzcd}
% 			{X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ A} & {X\otimes_\ZZ\op{Hom}_\ZZ(X,A)} \\
% 			{\ZZ\otimes_\ZZ A} & A
% 			\arrow["{\eta_T}", from=1-1, to=1-2]
% 			\arrow["{\eta_L}"', from=1-1, to=2-1]
% 			\arrow["{\eta_R}", from=1-2, to=2-2]
% 			\arrow["{\eta_B}"', from=2-1, to=2-2]
% 		\end{tikzcd} \label{eq:innermorphismcoherence}
% 	\end{equation}
% 	Indeed, we can just compute along the following diagram.
% 	% https://q.uiver.app/?q=WzAsNCxbMCwwLCJ4XFxvdGltZXMgZlxcb3RpbWVzIGEiXSxbMSwwLCJ4XFxvdGltZXMoeCdcXG1hcHN0byBmKHgnKWEpIl0sWzAsMSwiZih4KVxcb3RpbWVzIGEiXSxbMSwxLCJmKHgpYSJdLFswLDEsIlxcZXRhX1QiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzAsMiwiXFxldGFfTCIsMix7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbMSwzLCJcXGV0YV9SIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFsyLDMsIlxcZXRhX0IiLDIseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV1d&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
% 	\[\begin{tikzcd}
% 		{x\otimes f\otimes a} & {x\otimes(x'\mapsto f(x')a)} \\
% 		{f(x)\otimes a} & {f(x)a}
% 		\arrow["{\eta_T}", maps to, from=1-1, to=1-2]
% 		\arrow["{\eta_L}"', maps to, from=1-1, to=2-1]
% 		\arrow["{\eta_R}", maps to, from=1-2, to=2-2]
% 		\arrow["{\eta_B}"', maps to, from=2-1, to=2-2]
% 	\end{tikzcd}\]
% 	Now, the core of the proof is in drawing the following very large diagram.
% 	% https://q.uiver.app/?q=WzAsOSxbMCwwLCJcXHdpZGVoYXQgSF57aS0yfShHLFxcb3B7SG9tfV9cXFpaKFgsXFxaWikpIl0sWzEsMCwiXFx3aWRlaGF0IEheaShHLFxcb3B7SG9tfV9cXFpaKFgsXFxaWilcXG90aW1lc19cXFpaIEEpIl0sWzIsMCwiXFx3aWRlaGF0IEheaShHLFxcb3B7SG9tfV9cXFpaKFgsQSkpIl0sWzAsMSwiXFx3aWRlaGF0IEheaShHLFhcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooWCxcXFpaKSkiXSxbMSwxLCJcXHdpZGVoYXQgSF57aSsyfShHLFhcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooWCxcXFpaKVxcb3RpbWVzX1xcWlogQSkiXSxbMiwxLCJcXHdpZGVoYXQgSF57aSsyfShHLFhcXG90aW1lc19cXFpaXFxvcHtIb219X1xcWlooWCxBKSkiXSxbMiwyLCJcXHdpZGVoYXQgSF57aSsyfShHLEEpIl0sWzAsMiwiXFx3aWRlaGF0IEheaShHLFxcWlopIl0sWzEsMiwiXFx3aWRlaGF0IEheMihHLFhcXG90aW1lc19cXFpaIEEpIl0sWzAsMSwiLVxcY3VwIHUiXSxbMyw0LCItXFxjdXAgdSJdLFs3LDgsIi1cXGN1cCB1Il0sWzAsMywiY1xcY3VwIC0iLDJdLFsxLDQsImNcXGN1cCAtIiwyXSxbMiw1LCJjXFxjdXAgLSIsMl0sWzEsMiwiXFxldGFfVCJdLFs0LDUsIlxcZXRhX1QiXSxbOCw2LCJcXGV0YV9CIl0sWzMsNywiXFxldGFfTCIsMl0sWzQsOCwiXFxldGFfTCIsMl0sWzUsNiwiXFxldGFfUiIsMl0sWzEyLDEzLCIoMSkiLDMseyJzaG9ydGVuIjp7InNvdXJjZSI6MjAsInRhcmdldCI6MjB9LCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJub25lIn0sImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMTMsMTQsIigyKSIsMyx7InNob3J0ZW4iOnsic291cmNlIjoyMCwidGFyZ2V0IjoyMH0sInN0eWxlIjp7ImJvZHkiOnsibmFtZSI6Im5vbmUifSwiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFsxOCwxOSwiKDMpIiwzLHsic2hvcnRlbiI6eyJzb3VyY2UiOjIwLCJ0YXJnZXQiOjIwfSwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoibm9uZSJ9LCJoZWFkIjp7Im5hbWUiOiJub25lIn19fV0sWzE5LDIwLCIoNCkiLDMseyJzaG9ydGVuIjp7InNvdXJjZSI6MjAsInRhcmdldCI6MjB9LCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJub25lIn0sImhlYWQiOnsibmFtZSI6Im5vbmUifX19XV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
% 	\[\begin{tikzcd}
% 		{\widehat H^{i-p}(G,\op{Hom}_\ZZ(X,\ZZ))} & {\widehat H^i(G,\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ A)} & {\widehat H^i(G,\op{Hom}_\ZZ(X,A))} \\
% 		{\widehat H^i(G,X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ))} & {\widehat H^{i+p}(G,X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ A)} & {\widehat H^{i+p}(G,X\otimes_\ZZ\op{Hom}_\ZZ(X,A))} \\
% 		{\widehat H^i(G,\ZZ)} & {\widehat H^{i+p}(G,X\otimes_\ZZ A)} & {\widehat H^{i+p}(G,A)}
% 		\arrow["{-\cup u}", from=1-1, to=1-2]
% 		\arrow["{-\cup u}", from=2-1, to=2-2]
% 		\arrow["{-\cup u}", from=3-1, to=3-2]
% 		\arrow[""{name=0, anchor=center, inner sep=0}, "{c\cup -}"', from=1-1, to=2-1]
% 		\arrow[""{name=1, anchor=center, inner sep=0}, "{c\cup -}"', from=1-2, to=2-2]
% 		\arrow[""{name=2, anchor=center, inner sep=0}, "{c\cup -}"', from=1-3, to=2-3]
% 		\arrow["{\eta_T}", from=1-2, to=1-3]
% 		\arrow["{\eta_T}", from=2-2, to=2-3]
% 		\arrow["{\eta_B}", from=3-2, to=3-3]
% 		\arrow[""{name=3, anchor=center, inner sep=0}, "{\eta_L}"', from=2-1, to=3-1]
% 		\arrow[""{name=4, anchor=center, inner sep=0}, "{\eta_L}"', from=2-2, to=3-2]
% 		\arrow[""{name=5, anchor=center, inner sep=0}, "{\eta_R}"', from=2-3, to=3-3]
% 		\arrow["{(1)}"{marking}, Rightarrow, draw=none, from=0, to=1]
% 		\arrow["{(2)}"{marking}, Rightarrow, draw=none, from=1, to=2]
% 		\arrow["{(3)}"{marking}, Rightarrow, draw=none, from=3, to=4]
% 		\arrow["{(4)}"{marking}, Rightarrow, draw=none, from=4, to=5]
% 	\end{tikzcd}\]
% 	We are being asked to show that the outer square commutes; we will show that each inner square commutes, which will be enough.
% 	\begin{enumerate}[label=(\arabic*)]
% 		\item This square commutes by the associativity of the cup product.
% 		\item This square commutes by functoriality of cup products.
% 		\item This square commutes by functoriality of cup products.
% 		\item This square commutes by functoriality of $\widehat H^{i+p}(G,-)$ applied to \autoref{eq:innermorphismcoherence}.
% 	\end{enumerate}
% 	The above checks complete the proof.
% \end{proof}
% We may now proceed directly with \autoref{thm:abstractperfectpairing}.
\begin{proof}
	Applying \autoref{lem:cupassoc} to the commutative square
	% https://q.uiver.app/?q=WzAsOCxbMCwwLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsXFxaWilcXG90aW1lc19cXFpaIEEiXSxbMSwwLCJYXFxvdGltZXNfXFxaWlxcb3B7SG9tfV9cXFpaKFgsQSkiXSxbMCwxLCJcXFpaXFxvdGltZXNfXFxaWiBBIl0sWzEsMSwiQSJdLFsyLDAsInhcXG90aW1lcyBmXFxvdGltZXMgYSJdLFszLDAsInhcXG90aW1lcyh5XFxtYXBzdG8gZih5KWEpIl0sWzIsMSwiZih4KVxcb3RpbWVzIGEiXSxbMywxLCJmKHgpYSJdLFswLDFdLFswLDJdLFsxLDNdLFsyLDNdLFs0LDUsIiIsMCx7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XSxbNSw3LCIiLDAseyJzdHlsZSI6eyJ0YWlsIjp7Im5hbWUiOiJtYXBzIHRvIn19fV0sWzQsNiwiIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoibWFwcyB0byJ9fX1dLFs2LDcsIiIsMix7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Im1hcHMgdG8ifX19XV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
	\[\begin{tikzcd}
		{X\otimes_\ZZ\op{Hom}_\ZZ(X,\ZZ)\otimes_\ZZ A} & {X\otimes_\ZZ\op{Hom}_\ZZ(X,A)} & {x\otimes f\otimes a} & {x\otimes(y\mapsto f(y)a)} \\
		{\ZZ\otimes_\ZZ A} & A & {f(x)\otimes a} & {f(x)a}
		\arrow[from=1-1, to=1-2]
		\arrow[from=1-1, to=2-1]
		\arrow[from=1-2, to=2-2]
		\arrow[from=2-1, to=2-2]
		\arrow[maps to, from=1-3, to=1-4]
		\arrow[maps to, from=1-4, to=2-4]
		\arrow[maps to, from=1-3, to=2-3]
		\arrow[maps to, from=2-3, to=2-4]
	\end{tikzcd}\]
	we are able to conclude that any $u\in H^p(G,A)$ makes the diagram
	\[\begin{tikzcd}
		{\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))} & {\widehat H^0(G,\op{Hom}_\ZZ(X,A))} \\
		{\widehat H^0(G,\ZZ)} & {\widehat H^{r}(G,A)}
		\arrow["{-\cup u}", from=1-1, to=1-2]
		\arrow["{c\cup-}"', from=1-1, to=2-1]
		\arrow["{-\cup u}"', from=2-1, to=2-2]
		\arrow["{c\cup-}", from=1-2, to=2-2]
	\end{tikzcd}\]
	commute. Now, by hypothesis, the left and right arrows are isomorphisms, so the commutativity means that showing
	\[\arraycolsep=1.4pt\begin{array}{ccc}
		\widehat H^r(G,A) &\to& \op{Hom}_\ZZ\left(\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ)),\widehat H^0(G,\op{Hom}_\ZZ(X,A))\right) \\
		u &\mapsto& (a\mapsto (a\cup u))
	\end{array}\]
	is an isomorphism is the same as showing that
	\[\arraycolsep=1.4pt\begin{array}{ccc}
		\widehat H^r(G,A) &\to& \op{Hom}_\ZZ\left(\widehat H^0(G,\ZZ),\widehat H^r(G,A)\right) \\
		u &\mapsto& (k\mapsto (k\cup u))
	\end{array}\]
	is an isomorphism.
	
	Setting $n\coloneqq\#G$, we see $\widehat H^0(G,\ZZ)=\ZZ/n\ZZ$, and the cup product we are looking at sends $k\in\ZZ/n\ZZ$ and $u\in\widehat H^2(G,A)$ to $k\cup u=ku$ by how the isomorphism $\ZZ\otimes_\ZZ A\simeq A$ behaves. Thus, we are showing that
	\[\arraycolsep=1.4pt\begin{array}{ccc}
		\widehat H^p(G,A) &\to& \op{Hom}_\ZZ\left(\ZZ/n\ZZ,\widehat H^r(G,A)\right) \\
		u &\mapsto& (k\mapsto ku)
	\end{array}\]
	is an isomorphism.
	
	However, $\widehat H^r(G,A)$ is $n$-torsion, so in fact maps $\ZZ\to\widehat H^p(G,A)$ automatically have $n\ZZ$ in their kernel and hence reduce to maps $\ZZ/n\ZZ\to\widehat H^r(G,A)$. Conversely, any map $\ZZ/n\ZZ\to\widehat H^p(G,A)$ can be extended by $\ZZ\onto\ZZ/n\ZZ$ to a map $\ZZ\to\widehat H^r(G,A)$, so we have a natural isomorphism
	\[\arraycolsep=1.4pt\begin{array}{ccc}
		\op{Hom}_\ZZ\left(\ZZ/n\ZZ,\widehat H^r(G,A)\right) &\simeq& \op{Hom}_\ZZ\left(\ZZ,\widehat H^r(G,A)\right) \\
		f &\mapsto& (k\mapsto f([k])) \\
		([k]\mapsto f(k)) &\mapsfrom& f.
	\end{array}\]
	In particular, it suffices to show that
	\[\arraycolsep=1.4pt\begin{array}{ccc}
		\widehat H^r(G,A) &\to& \op{Hom}_\ZZ\left(\ZZ,\widehat H^r(G,A)\right) \\
		u &\mapsto& (k\mapsto ku)
	\end{array}\]
	is an isomorphism. But this is a standard fact about the functor $\op{Hom}_\ZZ$, so we are done.
\end{proof}
We now synthesize this with the theory we have been building.
\begin{cor}
	Let $G$ be a finite group, and let $X$ be an $r$-encoding module. Then, given a $G$-module $A$, the cup-product pairing induces an isomorphism
	\[\widehat H^r(G,A)\to\op{Hom}_\ZZ\left(\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ)),\widehat H^0(G,\op{Hom}_\ZZ(X,A))\right).\]
\end{cor}
\begin{proof}
	We apply \autoref{thm:abstractperfectpairing} to our case; we take $c$ to be the $x$ of \autoref{prop:encodingsarecups}. The cup-product maps in question are isomorphisms by \autoref{cor:betterencodingdef}. Thus, \autoref{thm:abstractperfectpairing} kicks in, completing the proof.
\end{proof}
\begin{remark}
	The other side of the pairing
	\[\widehat H^{-r}(G,\op{Hom}_\ZZ(X,\ZZ))\to\op{Hom}_\ZZ\left(\widehat H^r(G,A),\widehat H^0(G,\op{Hom}_\ZZ(X,A))\right)\]
	need not be an isomorphism; for example, take $A=0$.
\end{remark}
\begin{remark} \label{rem:artinreciptaste}
	When $X$ is a $\ZZ$-free $2$-encoding module, we can think about $\op{Hom}_\ZZ(X,-)$ as a torus $T$. For example, if $L/K$ is an extension of local fields, and the torus $T$ splits over $L$, then the above statement says that the Artin reciprocity map
	\[\widehat H^{-2}(L/K,X_*(T))\to\widehat H^0(L/K,TL)\]
	uniquely determines $u_{L/K}\in\widehat H^2(L/K,L^\times)$. It is conceivable that a sufficiently concrete description of this reciprocity map might then be able to describe $u_{L/K}$.
\end{remark}