In this section, we will use the notions but not the exact notation as in the set-up. Instead, we will build a ``tower set-up'' below. Our goal is to be able to force some compatibility among the data in the tuples of \autoref{cor:fundtriple} in towers. This is particularly simple in the case where we fix some unramified extension and allow our ramification to ascend in a tower.

As such, fix a base field $K$ and unramified extension $K_m$, and we also fix a tower of totally ramified extensions
\[K\coloneqq K_{\pi,0}\subseteq K_{\pi,1}\subseteq K_{\pi,2}\subseteq\cdots.\]
For example, we might choose Lubin--Tate extensions for this purpose. For brevity, we set
\[K_\pi\coloneqq\bigcup_{i\ge0}K_{\pi,i}\]
to be the (very large) composite totally ramified extension. Now, for each $i\ge0$, we define $L_i\coloneqq K_mK_{\pi,i}$ for each and $M_i$ to be the unramified extension of degree $[L_i:K]$ over $K$; notably, $[K_m:K]\mid[L_i:K]$, so $K_m\subseteq M_i$ for each $i\ge0$. Here is our diagram.
% https://q.uiver.app/?q=WzAsMTUsWzMsNSwiSyJdLFs0LDQsIktfbSJdLFs1LDMsIk1fMSJdLFsyLDQsIktfe1xccGksMX0iXSxbMSwzLCJLX3tcXHBpLDJ9Il0sWzAsMiwiXFxkZG90cyJdLFszLDMsIkxfMSJdLFsyLDIsIkxfMiJdLFs2LDIsIlxcaWRkb3RzIl0sWzQsMiwiTV8xTF8xIl0sWzMsMSwiTV8xTF8yIl0sWzUsMSwiXFxpZGRvdHMiXSxbMSwxLCJcXGRkb3RzIl0sWzIsMCwiXFxkZG90cyJdLFs0LDAsIlxcaWRkb3RzIl0sWzAsMywiIiwwLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFszLDQsIiIsMCx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbNCw1LCIiLDAseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJub25lIn19fV0sWzAsMSwiIiwyLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFsxLDIsIiIsMix7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMiw4LCIiLDIseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJub25lIn19fV0sWzEsNiwiIiwyLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFsyLDksIiIsMix7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbNiw5LCIiLDEseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJub25lIn19fV0sWzksMTEsIiIsMSx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbNiw3LCIiLDEseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJub25lIn19fV0sWzksMTAsIiIsMSx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMTAsMTQsIiIsMSx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMTAsMTMsIiIsMSx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbNywxMiwiIiwxLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFs0LDcsIiIsMSx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbNywxMCwiIiwxLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFszLDYsIiIsMCx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XV0=&macro_url=https%3A%2F%2Fraw.githubusercontent.com%2FdFoiler%2Fnotes%2Fmaster%2Fnir.tex
\[\begin{tikzcd}[column sep={1cm,between origins}, row sep={1cm,between origins}]
	&& \ddots && \iddots \\
	& \ddots && {M_1L_2} && \iddots \\
	\ddots && {L_2} && {M_1L_1} && \iddots \\
	& {K_{\pi,2}} && {L_1} && {M_1} \\
	&& {K_{\pi,1}} && {K_m} \\
	&&& K
	\arrow[no head, from=6-4, to=5-3]
	\arrow[no head, from=5-3, to=4-2]
	\arrow[no head, from=4-2, to=3-1]
	\arrow[no head, from=6-4, to=5-5]
	\arrow[no head, from=5-5, to=4-6]
	\arrow[no head, from=4-6, to=3-7]
	\arrow[no head, from=5-5, to=4-4]
	\arrow[no head, from=4-6, to=3-5]
	\arrow[no head, from=4-4, to=3-5]
	\arrow[no head, from=3-5, to=2-6]
	\arrow[no head, from=4-4, to=3-3]
	\arrow[no head, from=3-5, to=2-4]
	\arrow[no head, from=2-4, to=1-5]
	\arrow[no head, from=2-4, to=1-3]
	\arrow[no head, from=3-3, to=2-2]
	\arrow[no head, from=4-2, to=3-3]
	\arrow[no head, from=3-3, to=2-4]
	\arrow[no head, from=5-3, to=4-4]
\end{tikzcd}\]
Arrows going up and to the left are unramified; arrows going up and to the right are (totally) ramified. Now, we are interested in constructing a ``compatible'' system of tuples representing fundamental classes for the ascending chain of extensions $L_1/K$, $L_2/K$, $L_3/K$, etc.

For coherence reasons, we will also place a few assumptions on our Galois groups. Namely, we will assume that
\[\op{Gal}(K_\pi/K)=\bigoplus_{i=1}^m\overline{\langle\tau_i\rangle}\]
is a direct sum of finitely many procyclic groups. For example, if we are using Lubin--Tate extensions, and we are in characteristic $0$, then this is automatic. Additionally, we will assume that our quotients are
\[\op{Gal}(K_{\pi,i}/K)=\bigoplus_{i=1}^m\langle\tau_i|_{K_i}\rangle\]
for each $i\ge0$. This requirement, though strong, is essentially the only way we could hope for compatibility among our tuples---namely, it tells us that each $L_i/K$ has Galois group generated by the same elements (up to restriction) and hence have more or less the same requirements to yield a fundamental tuple. As an example, this requirement is satisfied when $K=\QQ_p$ and $K_i=\QQ_p(\zeta_{p^i})$; in fact, $m\in\{1,2\}$ in this case.

The main focus of the construction is to construct compatible $\gamma$ elements, but the notion of compatibility will in fact extend. As such, we will codify this into the following definition.
\begin{definition}
	Fix everything as above. Then a sequence $\{x_i\}_{i=0}^\infty$ of elements $x_i\in M_iL_i$ is \textit{compatible in towers} if and only if
	\[\op N_{M_{i+1}L_{i+1}/M_iL_{i+1}}(x_{i+1})=x_i.\]
\end{definition}
This definition is written down sequentially so that verifying its existence is easy.
\begin{lemma}
	Fix a uniformizer $\pi_K\in K$. There is a sequence $\{\gamma_i\}_{i=0}^\infty$ of elements compatible in towers such that $\gamma_0\in M_0L_0=K_m$ is $\gamma_0=\pi_K$.
\end{lemma}
\begin{proof}
	This comes down to a norm argument and an induction. Extend a valuation $v_K\colon K\to\ZZ$ to all fields above. Suppose we have constructed $\gamma_i$ such that $\gamma_i$ is a uniformizer of $M_iL_i$. We claim that we can construct $\gamma_{i+1}$ to also be a uniformizer of $M_{i+1}L_{i+1}$ and with
	\[\op N_{M_{i+1}L_{i+1}/M_iL_{i+1}}(\gamma_{i+1})=\gamma_i.\]
	This claim will finish the proof inductively.
	
	Now, observe that the extension $M_iL_{i+1}/M_iL_i$ is a totally ramified extension, so if we let $\varpi$ denote a uniformizer of $M_iL_{i+1}$, we have
	\begin{equation}
		v\left(\varpi^{[M_iL_{i+1}:M_iL_i]}\right)=v(\gamma_i). \label{eq:totramtowervaluation}
	\end{equation}
	Continuing, $M_{i+1}L_{i+1}/M_iL_{i+1}$ is an unramified extension, so in fact $\varpi$ continues to be a uniformizer up in $M_{i+1}L_{i+1}$. As such, we see that it suffices to construct $u\in M_{i+1}L_{i+1}$ such that
	\[\op N_{M_{i+1}L_{i+1}/M_iL_{i+1}}(u)=\frac{\gamma_i}{\op N_{M_{i+1}L_{i+1}/M_iL_{i+1}}(\varpi)}.\]
	But the right-hand side is a unit because it has valuation $0$ from \autoref{eq:totramtowervaluation}, so we can construct a unit $u$ for the left-hand side as well because the norm map surjects from units to units in unramified extensions. In total, $\gamma_{i+1}\coloneqq u\varpi$ is the element we are looking for.
\end{proof}
However, the definition of compatibility does not actually tell us that each of these $\gamma_i$ will behave the way that we need them to as required by \autoref{cor:fundtriple}. The compatibility is also a little unnatural because it only moves one step at a time. To fix both of these issues, we have the following.
\begin{lemma}
	Suppose that the sequence $\{x_i\}_{i=0}^\infty$ is compatible in towers. Then for any nonnegative integers $p\ge q$, we have
	\[\op N_{M_pL_p/M_qL_p}(x_p)=x_q.\]
\end{lemma}
\begin{proof}
	This will require us to actually describe the Galois groups involved. Set $\sigma_K\in\op{Gal}(K^{\op{unr}}/K)$ to the Frobenius automorphism on $K$, but extend $\sigma_K$ to all $K^{\op{ab}}$ by acting trivially on totally ramified extensions. Additionally, for brevity we set
	\[f\coloneqq[K_m:K]\qquad\text{and}\qquad e_i\coloneqq[K_{\pi,i}:K]\]
	for each $i\ge0$. Now, the extension $M_pL_p/M_qL_p$ is unramified and hence has Galois group generated by its Frobenius element. The Frobenius element of $M_qL_p$ is equal to the Frobenius element of $M_q$ because the extension $M_jL_i/M_j$ is totally ramified, and because $M_q/K$ is unramified, we may compute the Frobenius element of $M_q$ as
	\[\sigma_K^{[M_q:K]},\]
	where $[M_q:K]=[L_q:K]=[L_q:K_{\pi,q}]\cdot[K_{\pi,q}:K]=[K_m:K]\cdot[K_{\pi,q}:K]=fe_q$. As for the order of $\op{Gal}(M_pL_p/M_qL_p)$, we first compute, for any $i\ge0$,
	\[[M_iL_i:L_i]=\frac{[M_iL_i:K]}{[L_i:K]}=\frac{[M_iL_i:M_i]\cdot[M_i:K]}{[L_i:K]}=[M_iL_i:M_i]=[K_{\pi,i}:K]=e_i,\]
	so the degree we want is $e_p/e_q$. Thus,
	\[\op N_{M_pL_p/M_qL_p}(x_p)=\prod_{i=0}^{e_p/e_q-1}\sigma_K^{fe_qi}(x_p).\]
	Now, we show that this equals $x_q$ by induction on $p$. When $p=q$, there is nothing to say. Then, supposing we have the equality at $p$, we write
	\begin{align*}
		\op N_{M_{p+1}L_{p+1}/M_qL_{p+1}}(x_{p+1}) &= \prod_{i=0}^{e_{p+1}/e_q-1}\sigma_K^{fe_qi}(x_{p+1}) \\
		&= \prod_{b=0}^{e_p/e_q-1}\prod_{a=0}^{e_{p+1}/e_p-1}\sigma_K^{fe_q(a(e_p/e_q)+b)}(x_{p+1}) \\
		&= \prod_{b=0}^{e_p/e_q-1}\sigma_K^{fe_qb}\Bigg(\prod_{a=0}^{e_{p+1}/e_p-1}\sigma_K^{fe_pa}(x_{p+1})\Bigg) \\
		&= \prod_{b=0}^{e_p/e_q-1}\sigma_K^{fe_qb}\Bigg(\prod_{a=0}^{e_{p+1}/e_p-1}\sigma_K^{fe_pa}(x_{p+1})\Bigg).
	\end{align*}
	Doing the same Galois theory, we see $\op{Gal}(M_{p+1}L_{p+1}/M_pL_{p+1})$ is cyclic generated by $\sigma_K^{fe_p}$ of order $e_{p+1}/e_p$, so the inner term is $\op N_{M_{p+1}L_{p+1}/M_pL_{p+1}}(x_{p+1})$, which we know to be $x_p$. Now, $x_p\in M_pL_p$, so in fact the entire product collapses to
	\[\op N_{M_{p+1}L_{p+1}/M_qL_{p+1}}(x_{p+1})=\op N_{M_pL_p/M_qL_p}(x_p)=x_q,\]
	which is what we wanted. This completes the proof.
\end{proof}
In particular, our sequence $\{\gamma_i\}_{i=0}^\infty$ compatible in towers with $\gamma_0=0$ will have
\[\op N_{M_iL_i/L_i}(\gamma_i)=\op N_{M_iL_i/M_0L_i}(\gamma_i)=\gamma_0=\pi_K\]
for each $i\ge0$, so these $\gamma_i\in M_iL_i$ do in fact satisfy the needed requirement of \autoref{cor:fundtriple}.

Thus, we have described how to construct our $\gamma$ terms in the tower, from which the rest of the fundamental tuple follows. However, we do remark that it is possible to choose the $\eta$ terms to be compatible in towers as well.
\begin{lemma}
	Fix everything as above. Further, fix some $\sigma\in\op{Gal}\big(\bigcup_{i\ge0}L_i/K\big)$. Then there exists a sequence $\{\eta_i\}_{i=0}^\infty$ compatible in towers such that
	\begin{equation}
		\frac{\eta_i}{\sigma_K^f(\eta_i)}=\frac{\sigma(\gamma_i)}{\gamma_i} \label{eq:etaequation}
	\end{equation}
	for each $i\ge0$.
\end{lemma}
\begin{proof}
	Well, to begin we have $\gamma_0=\pi_K$, which is fixed by $\sigma$, so the right-hand side is $1$, meaning that we might as well take $\eta_0=1$. We now claim that, given $\eta_i$ satisfying \autoref{eq:etaequation} which is a unit, we can construct $\eta_{i+1}$ with
	\[\op N_{M_{i+1}L_{i+1}/M_iL_{i+1}}(\eta_{i+1})=\eta_i\]
	also satisfying \autoref{eq:etaequation} (for $i+1$) which is a unit. For brevity, set ${\op N}\coloneqq\op N_{M_{i+1}L_{i+1}/M_iL_{i+1}}$. To begin, we note that $\eta_i$ is a unit in $M_iL_{i+1}$ as well, so because $M_{i+1}L_{i+1}/M_iL_{i+1}$ is unramified, we may simply guess any $\eta\in M_{i+1}L_{i+1}$ such that
	\[\op N(\eta)=\eta_i.\]
	We now need to correct for \autoref{eq:etaequation}. Well, we start by noting we're pretty close because
	\begin{align*}
		\op N\Bigg(\frac{\eta}{\sigma_K^f(\eta)}\bigg/\frac{\sigma(\gamma_{i+1})}{\gamma_{i+1}}\Bigg) &= \frac{\op N\eta}{\sigma_K^f(\op N\eta)}\bigg/\frac{\sigma(\op N\gamma_{i+1})}{\op N\gamma_{i+1}} \\
		&= \frac{\eta_i}{\sigma_K^f(\eta_i)}\bigg/\frac{\sigma(\gamma_{i})}{\gamma_{i}} \\
		&= 1.
	\end{align*}
	Now, $M_{i+1}L_{i+1}/M_iL_{i+1}$ is unramified and hence cyclic, and we know that its Galois group is generated by $\sigma_K^{fe_i}$ as computed earlier, so Hilbert's theorem 90 allows us to find some $u\in M_{i+1}L_{i+1}$ such that
	\[\frac{\eta}{\sigma_K^f(\eta)}\bigg/\frac{\sigma(\gamma_{i+1})}{\gamma_{i+1}}=\frac u{\sigma_K^{fe_i}u}.\]
	Quickly, note that we may multiply $u$ by any element in $M_iL_{i+1}$ without adjusting the equality. Thus, taking $\varpi$ to be a uniformizer of $M_iL_{i+1}$, we note that we can divide out $u$ by some number of $\varpi$s to force $u$ to be a unit because the extension $M_{i+1}L_{i+1}/M_iL_{i+1}$ is unramified, making $\varpi$ also a uniformizer of $M_{i+1}L_{i+1}$. This is all to say that we may assume that $u$ is a unit.

	Now, we note that
	\[\frac u{\sigma_K^{fe_i}u}=\prod_{k=0}^{e_i-1}\frac{\sigma_K^{fk}u}{\sigma_K^{f(k+1)}u}=\underbrace{\Bigg(\prod_{k=0}^{e_i-1}\sigma_K^{fk}u\Bigg)}_{v\coloneqq}/\sigma_K^f\Bigg(\prod_{k=0}^{e_i-1}\sigma_K^{fk}u\Bigg)=\frac{v}{\sigma_K^fv}.\]
	Because $u$ is a unit, $v$ is as well. In total, we see that
	\[\frac{\eta}{\sigma_K^f(\eta)}\bigg/\frac{\sigma(\gamma_{i+1})}{\gamma_{i+1}}=\frac u{\sigma_K^{fe_i}u}=\frac{v}{\sigma_K^fv}\]
	now implies that
	\[\frac{\eta/v}{\sigma_K^f(\eta/v)}=\frac{\sigma(\gamma_{i+1})}{\gamma_{i+1}}.\]
	Thus, we set $\eta_{i+1}\coloneqq\eta/v$, which we know to be a unit because both $\eta$ and $v$ are. This completes the inductive step and hence the proof.
\end{proof}
As such, we define $\{\eta_{\sigma,i}\}_{i=0}^\infty$ for each $\sigma\in\op{Gal}\big(\bigcup_{i\ge0}L_i/K\big)$ as constructed above, and we know these to be compatible in towers.

To finish our discussion, we note that because the expressions for the $\alpha_i$ and $\beta_{ij}$ are multiplicative and because norms commute with automorphisms in abelian extensions, choosing the $\gamma$s and $\eta$s to be compatible in towers will imply that the entire fundamental tuples will be (pointwise) compatible in towers.

As an example, we write this compatibility out for $\alpha_0$; the rest of the terms are similar. We define
\[\alpha_{0,i}\coloneqq\gamma_i\cdot\prod_{k=0}^{f-1}\sigma_K^k(\eta_{\sigma_K,i})\]
in accordance with \autoref{cor:fundtriple}. To check that this is compatible in towers, we set ${\op N}\coloneqq\op N_{M_{i+1}L_{i+1}/M_iL_{i+1}}$ for some index $i$ and compute
\begin{align*}
	\op N(\alpha_{0,i+1}) &= \op N\Bigg(\gamma_{i+1}\cdot\prod_{k=0}^{f-1}\sigma_K^k(\eta_{\sigma_K,i+1})\Bigg) \\
	&= \op N\gamma_{i+1}\cdot\prod_{k=0}^{f-1}\sigma_K^k(\op N\eta_{\sigma_K,i+1}) \\
	&= \gamma_i\cdot\prod_{k=0}^{f-1}\sigma_K^k(\eta_{\sigma_K,i}) \\
	&= \alpha_{0,i},
\end{align*}
which is what we wanted.